---
title: "GEPD Geospatial Admin Linkaged"
author: "Brian Stacy"
date: "11/5/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(sf)
sf::sf_use_s2(FALSE)
library(rnaturalearth)
library(rnaturalearthdata)
library(ggthemes)
library(patchwork)

#cnt_map <- ne_countries(country="Peru", scale = "medium", returnclass = "sf", type='map_units')


#set directory to bring in data
country <-'PER'
country_name <- "Peru"
year <- '2019'

#directories
project_folder  <- "C:/Users/wb469649/WBG/HEDGE Files - HEDGE Documents/GEPD-Confidential/CNT/"
confidential_folder <- file.path(paste(project_folder,country,paste(country,year,"GEPD", sep="_"),paste(country,year,"GEPD_v01_RAW", sep="_"),"Data/confidential/", sep="/"))
save_folder <- file.path(paste(project_folder,country,paste(country,year,"GEPD", sep="_"),paste(country,year,"GEPD_v01_RAW", sep="_"),"Data/anonymized/", sep="/"))

# load the world bank admin boundaries
load("C:/Users/wb469649/WBG/HEDGE Files - HEDGE Documents/GEPD-Confidential/General/WB_admin_boundaries.Rdata")

# load the public officials data
load(file.path(confidential_folder, "/Public_Officials/public_officials_indicators_data.RData"))

# load the school data
load(file.path(confidential_folder, "/School/school_survey_data.RData"))


keyfile <- read_csv(paste0(confidential_folder, "/School/EPDash_linkfile_hashed.csv"))

#get list of indicators

    sch_ind_list<-c('student_knowledge', 'math_student_knowledge', 'literacy_student_knowledge', 'student_proficient','student_proficient_nogiraffe',  'literacy_student_proficient_nogiraffe', 'literacy_student_proficient', 'math_student_proficient', 'student_proficient_70',  'student_proficient_75',
                'student_attendance',
                'presence_rate',  'absence_rate', 'sch_absence_rate', 
                'content_proficiency', 'literacy_content_proficiency', 'math_content_proficiency', 'content_proficiency_70', 'content_proficiency_75', 'content_knowledge', 'math_content_knowledge', 'literacy_content_knowledge', 'grammar', 'cloze',  'read_passage', 'arithmetic_number_relations', 'geometry', 'interpret_data',
                'teach_score','classroom_culture','instruction','socio_emotional_skills',
                'teach_prof','classroom_culture_prof','instruction_prof','socio_emotional_skills_prof', 'timeontask1',
                'ecd_student_knowledge', 'ecd_math_student_knowledge', 'ecd_literacy_student_knowledge', 'ecd_exec_student_knowledge', 'ecd_soc_student_knowledge',
                'ecd_student_proficiency', 'ecd_math_student_proficiency', 'ecd_literacy_student_proficiency', 'ecd_exec_student_proficiency', 'ecd_soc_student_proficiency',
                'inputs', 'blackboard_functional', 'pens_etc','textbooks', 'share_desk', 'used_ict', 'access_ict',
                'infrastructure','drinking_water', 'functioning_toilet', 'internet', 'class_electricity','disability_accessibility',
                'operational_management', 'vignette_1',  'vignette_2', 
                'intrinsic_motivation', 'acceptable_absent', 'students_deserve_attention', 'growth_mindset', 'motivation_teaching',
                'instructional_leadership', 'classroom_observed', 'classroom_observed_recent', 'discussed_observation', 'feedback_observation', 'lesson_plan_w_feedback',
                'principal_knowledge_score', 'add_triple_digit_pknw', 'multiply_double_digit_pknw', 'complete_sentence_pknw', 'experience_pknw', 'textbooks_pknw', 'blackboard_pknw',
                'principal_management', 'sch_goals_exist','sch_goals_clear','sch_goals_relevant','sch_goals_measured',
                'teacher_attraction', 'teacher_satisfied_job', 'teacher_satisfied_status', 'better_teachers_promoted' ,'teacher_bonus', 'salary_delays',
                'teacher_selection_deployment', 'teacher_selection','teacher_deployment',
                'teacher_support', 'pre_service','practicum','in_service','opportunities_teachers_share',
                'teaching_evaluation', 'formally_evaluated', 'evaluation_content', 'negative_consequences','positive_consequences',
                'teacher_monitoring','attendance_evaluated' , 'attendance_rewarded' , 'attendence_sanctions', 'miss_class_admin',
                'standards_monitoring',
                'sch_monitoring', 'monitoring_inputs','monitoring_infrastructure','parents_involved',
                'sch_management_clarity', 'infrastructure_scfn','materials_scfn','hiring_scfn', 'supervision_scfn', 'student_scfn' , 'principal_hiring_scfn', 'principal_supervision_scfn',
                'sch_management_attraction', 'principal_satisfaction', 'principal_salary',
                'sch_selection_deployment', 
                'sch_support', 'prinicipal_trained','principal_training','principal_used_skills','principal_offered',
                'principal_evaluation', 'principal_formally_evaluated','principal_evaluation_multiple','principal_negative_consequences','principal_positive_consequences')
    
    po_ind_list<- c(
                'national_learning_goals', 'targeting', 'monitoring', 'incentives', 'community_engagement',
                'mandates_accountability' , 'coherence', 'transparency', 'accountability', 
                'quality_bureaucracy', 'knowledge_skills', 'work_environment', 'merit', 'motivation_attitudes','motivation_relative_start',
                'impartial_decision_making','politicized_personnel_management', 'politicized_policy_making', 'politicized_policy_implementation', 'employee_unions_as_facilitators'
    )
    
```


## Introduction

This file will read in the World Bank spatial polygon files containing the admin1 and admin2 boundaries for all countries. It will then read in the lat/long data in the GEPD school and public officials files and match them to the official admin1 and admin2 boundaries.  This informatin will then be saved.

```{r geojson_prelim}

library(geojsonsf) # reads large .geojson files as sf objects much faster than sf's st_read()

wbgis <- "C:/Users/wb469649/WBG/HEDGE Files - HEDGE Documents/GEPD-Confidential/General/"



# load wb polygon data 

## import at district level (adm2 level)
wb.poly.2 <- geojson_sf(
  file.path(wbgis, "g2015_2014_2.geojson") # where _2 has district level polys
  ) %>%
  filter( ADM0_NAME == country_name) %>%
  distinct(ADM2_CODE, ADM1_CODE, ADM0_CODE, .keep_all = TRUE)  # remove any possible duplicates

# ## import at district level (adm1 level)
# geo1 <- geojson_sf(
#   file.path(wbgis, "GeoJSON/g2015_2014_1.geojson") # where _1 has region-level polys
#   ) %>%
#   filter( ADM0_NAME == country_name) %>%
#   distinct(ADM1_CODE, ADM0_CODE, .keep_all = TRUE)  # remove any possible duplicates
# 
# ## keep only the adm0 code and the geometry column.
# geo1 <- geo1 %>%
#   select(ADM1_CODE, geometry)


# plot to show different geometries: rwa1 has 5 regions and rwa has 30 districts 
#geo1 %>% select(ADM1_CODE) %>% plot(., main = 'region geometry')
wb.poly.2 %>% select(ADM2_CODE) %>% plot(., main = 'district geometry')



```


```{r linkages}

m.po <- public_officials_dta_clean
m.school <- school_dta_short

#get coordinates
po_coord_df <- public_officials_dta_clean %>%
  select(interview__id, lat, lon) %>%
  rename(office_lat=lat,
         office_lon=lon)

school_coord_df <- school_dta_short %>%
  select(school_code, lat, lon) %>%
  rename(school_lat=lat,
         school_lon=lon) 

# convert po + school dataset to sf objects
po <- st_as_sf(m.po,
               coords = c("lon", "lat"), # set geometry/point column first
               na.fail = FALSE)

school <- st_as_sf(m.school,
                   coords = c("lon", "lat"),
                   na.fail = FALSE)



# set the crs of school + po as the same as the world poly crs
st_crs(po) <- st_crs(wb.poly.2)
st_crs(school) <- st_crs(wb.poly.2)

st_is_longlat(po)
st_is_longlat(school)



# set the variable order
order <- c("ADM0_NAME", "ADM1_NAME", "ADM2_NAME",
           "ADM0_CODE", "ADM1_CODE", "ADM2_CODE")



# - - - - - - - - -  join poly and po datasets - - - - - - - - -
# note, this is very important to see that the datasets will be
# joined NOT by the region or dsitrict -level polygon datasets, but
# instead the will be joined by the dataset that defines the polygons
# by the decision-making level

main_po_data <- st_join(po, # points
                        wb.poly.2, #polys
                        largest = TRUE) %>%
  select( interview__id,  order, everything())


# join poly and school datasets: should be joing with wb.poly.2 since schools don't apply to dm level
main_school_data <- st_join(school, # points
                            wb.poly.2, #polys
                            largest = TRUE) %>%
  select(school_code, order, everything())
```
```{r poplot}

po_map <- ggplot() +
  geom_sf(data=wb.poly.2) +
  geom_sf(data=po) +
  theme_map() +
  ggtitle("Locations of Interviews for Survey of Public Officials")
  
school_map <- ggplot() +
  geom_sf(data=wb.poly.2) +
  geom_sf(data=school) +
  theme_map() +
  ggtitle("Locations of Interviews for School Survey")
  
po_map + school_map

combined_map <- ggplot() +
  geom_sf(data=wb.poly.2) +
  geom_sf(data=school, color='red', shape=1) +
  geom_sf(data=po, color='blue', shape=2) +
  theme_map() +
  labs(title="Locations of Interviews for School Survey and Survey of Public Officials",
       caption = "School interviews in red.  Public Offiicals interview in blue.")
  
combined_map  
```


Merge the school and PO data

```{r}
#district linkages
po_district_df <- main_po_data %>%
  left_join(po_coord_df) %>%
  filter(govt_tier=='District office (or equivalent)') %>%
  group_by(ADM2_NAME, ADM2_CODE) %>%
    haven::zap_labels() %>%
  summarise(across(one_of(c(po_ind_list,"office_lat","office_lon")),mean, na.rm=TRUE)) %>%
  as_tibble() %>%
  filter(!is.na(ADM2_NAME))



linked_school_data <- main_school_data %>%
  left_join(school_coord_df) %>%
  left_join(po_district_df) 
  #filter(!is.na(quality_bureaucracy))

#write to csv
linked_school_data_csv <- linked_school_data %>%
  as_tibble() %>% 
  ungroup() %>%
  left_join(keyfile) %>%
  select(hashed_school_code, ADM0_NAME, ADM1_NAME, ADM2_NAME, school_lat, school_lon, colnames(po_district_df)) 

write_excel_csv(linked_school_data_csv, paste0(confidential_folder, "/School/linked_po_school_data_",country,"_",year,".csv"))

```

Keep just the director responses.

```{r directors}
#district linkages

#keep just the directors
po_district_df <- main_po_data %>%
  left_join(po_coord_df) %>%
  filter(govt_tier=='District office (or equivalent)') %>%
  filter(DEM1q12n==1) %>% # just the managers/directors
    haven::zap_labels() %>%
  group_by(ADM2_NAME, ADM2_CODE) %>%
  summarise(across(one_of(c(po_ind_list,"office_lat","office_lon")),mean, na.rm=TRUE)) %>%
  as_tibble() %>%
  filter(!is.na(ADM2_NAME))



linked_school_data <- main_school_data %>%
  left_join(school_coord_df) %>%
  left_join(po_district_df) 
  #filter(!is.na(quality_bureaucracy))

#write to csv
linked_school_data_csv <- linked_school_data %>%
  as_tibble() %>% 
  ungroup() %>%
  left_join(keyfile) %>%
  select(hashed_school_code, ADM0_NAME, ADM1_NAME, ADM2_NAME, school_lat, school_lon, colnames(po_district_df)) 

write_excel_csv(linked_school_data_csv, paste0(confidential_folder, "/School/linked_po_directors_school_data_",country,"_",year,".csv"))

```

Reweighted based on confidence of enumerator

```{r enumconf}
#district linkages

#WEights based on confidence of enumerators
#Did the respondent appear knowledgeable about the work environment, and their organization as a whole?
# 1. Some knowledge of their own working environment, but not about the organization as a whole
# 2. Expert knowledge about their working environment, but not about the organization as a whole
# 3. Expert knowledge about both their own work and about the organization as a whole.

po_district_df <- main_po_data %>%
  left_join(po_coord_df) %>%
  filter(govt_tier=='District office (or equivalent)') %>%
  haven::zap_labels() %>%
  group_by(ADM2_NAME, ADM2_CODE) %>%
  summarise(across(one_of(c(po_ind_list,"office_lat","office_lon")), Hmisc::wtd.mean, weights=ENUMq4, na.rm=TRUE)) %>%
  as_tibble() %>%
  filter(!is.na(ADM2_NAME))



linked_school_data <- main_school_data %>%
  left_join(school_coord_df) %>%
  left_join(po_district_df) 
  #filter(!is.na(quality_bureaucracy))

#write to csv
linked_school_data_csv <- linked_school_data %>%
  as_tibble() %>% 
  ungroup() %>%
  left_join(keyfile) %>%
  select(hashed_school_code, ADM0_NAME, ADM1_NAME, ADM2_NAME, school_lat, school_lon, colnames(po_district_df)) 

write_excel_csv(linked_school_data_csv, paste0(confidential_folder, "/School/linked_po_enum_score_weighted_school_data_",country,"_",year,".csv"))

```

Analysis

```{r eval=FALSE, include=FALSE}

linked_school_data_csv <- linked_school_data_csv %>%
  mutate(dist=distm(.[,c('school_lon', 'school_lat')], .[c('office_lon', 'office_lat')], fun = distHaversine),
                                 dist_miles=dist/1609.35)

hist(linked_school_data_csv$dist_miles) #distance in miles
  
linked_map <- ggplot() +
  geom_sf(data=wb.poly.2, fill='#d8e2dc') +
  geom_sf(data=linked_school_data, color='black', shape=1) +
  geom_point(data=linked_school_data_csv, aes(x=office_lon, y=office_lat), color='red') +
  theme_map() +
  labs(title="Locations of linkable observations for School Survey and Survey of Public Officials"
       )+
  theme(panel.background = element_rect(fill='#ece4db')
  )
linked_map

po_region_df <- main_po_data %>%
  filter(govt_tier=='Regional office (or equivalent)') %>%
  group_by(ADM1_NAME, ADM1_CODE) %>%
  summarise(across(one_of(po_ind_list),mean)) %>%
  as_tibble() %>%
  select(-geometry)

linked_school_region_data <- main_school_data %>%
  left_join(po_region_df)  %>%
  filter(!is.na(quality_bureaucracy))
```


```{r student_knowledge, eval=FALSE, include=FALSE}

ggplot(data=linked_school_data, aes(x=quality_bureaucracy, y=student_knowledge)) +
  geom_point() +
  geom_smooth(method='lm') +
  theme_bw()

ggplot(data=linked_school_data, aes(x=national_learning_goals, y=student_knowledge)) +
  geom_point() +
  geom_smooth(method='lm') +
  theme_bw()

ggplot(data=linked_school_data, aes(x=mandates_accountability, y=student_knowledge)) +
  geom_point() +
  geom_smooth(method='lm') +
  theme_bw()

ggplot(data=linked_school_data, aes(x=impartial_decision_making, y=student_knowledge)) +
  geom_point() +
  geom_smooth(method='lm') +
  theme_bw()

```

```{r inputs, eval=FALSE, include=FALSE}

ggplot(data=linked_school_data, aes(x=quality_bureaucracy, y=inputs)) +
  geom_point() +
  geom_smooth(method='lm') +
  theme_bw()

ggplot(data=linked_school_data, aes(x=national_learning_goals, y=inputs)) +
  geom_point() +
  geom_smooth(method='lm') +
  theme_bw()

ggplot(data=linked_school_data, aes(x=mandates_accountability, y=inputs)) +
  geom_point() +
  geom_smooth(method='lm') +
  theme_bw()

ggplot(data=linked_school_data, aes(x=impartial_decision_making, y=inputs)) +
  geom_point() +
  geom_smooth(method='lm') +
  theme_bw()

```

```{r infrastructure, eval=FALSE, include=FALSE}

ggplot(data=linked_school_data, aes(x=quality_bureaucracy, y=infrastructure)) +
  geom_point() +
  geom_smooth(method='lm') +
  theme_bw()

ggplot(data=linked_school_data, aes(x=national_learning_goals, y=infrastructure)) +
  geom_point() +
  geom_smooth(method='lm') +
  theme_bw()

ggplot(data=linked_school_data, aes(x=mandates_accountability, y=infrastructure)) +
  geom_point() +
  geom_smooth(method='lm') +
  theme_bw()

ggplot(data=linked_school_data, aes(x=impartial_decision_making, y=infrastructure)) +
  geom_point() +
  geom_smooth(method='lm') +
  theme_bw()

```



