---
title: "Global Education Policy Dashboard"
author: "Education Global Practice, World Bank"
date: "10/22/2021"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

#include packages
library(tidyverse)
library(skimr)
library(haven)
library(kableExtra)
library(flextable)
library(ggridges)
library(scales)
library(spatstat)
#library(ggradar)
library(Hmisc)
library(DT)

# define stle for ggplot based on BBC plotting styles
bbc_style <- function() {
  font <- "Helvetica"
  
  ggplot2::theme(
    
    #Text format:
    #This sets the font, size, type and colour of text for the chart's title
    plot.title = ggplot2::element_text(family=font,
                                       size=28,
                                       face="bold",
                                       color="#222222"),
    #This sets the font, size, type and colour of text for the chart's subtitle, as well as setting a margin between the title and the subtitle
    plot.subtitle = ggplot2::element_text(family=font,
                                          size=22,
                                          margin=ggplot2::margin(9,0,9,0)),
    plot.caption = ggplot2::element_blank(),
    #This leaves the caption text element empty, because it is set elsewhere in the finalise plot function
    
    #Legend format
    #This sets the position and alignment of the legend, removes a title and backround for it and sets the requirements for any text within the legend. The legend may often need some more manual tweaking when it comes to its exact position based on the plot coordinates.
    legend.position = "top",
    legend.text.align = 0,
    legend.background = ggplot2::element_blank(),
    legend.title = ggplot2::element_blank(),
    legend.key = ggplot2::element_blank(),
    legend.text = ggplot2::element_text(family=font,
                                        size=18,
                                        color="#222222"),
    
    #Axis format
    #This sets the text font, size and colour for the axis test, as well as setting the margins and removes lines and ticks. In some cases, axis lines and axis ticks are things we would want to have in the chart - the cookbook shows examples of how to do so.
    axis.title = ggplot2::element_blank(),
    axis.text = ggplot2::element_text(family=font,
                                      size=18,
                                      color="#222222"),
    axis.text.x = ggplot2::element_text(margin=ggplot2::margin(5, b = 10)),
    axis.ticks = ggplot2::element_blank(),
    axis.line = ggplot2::element_blank(),
    
    #Grid lines
    #This removes all minor gridlines and adds major y gridlines. In many cases you will want to change this to remove y gridlines and add x gridlines. The cookbook shows you examples for doing so
    panel.grid.minor = ggplot2::element_blank(),
    panel.grid.major.y = ggplot2::element_line(color="#cbcbcb"),
    panel.grid.major.x = ggplot2::element_blank(),
    
    #Blank background
    #This sets the panel background as blank, removing the standard grey ggplot background colour from the plot
    panel.background = ggplot2::element_blank(),
    
    #Strip background (#This sets the panel background for facet-wrapped plots to white, removing the standard grey ggplot background colour and sets the title size of the facet-wrap title to font size 22)
    strip.background = ggplot2::element_rect(fill="white"),
    strip.text = ggplot2::element_text(size  = 22,  hjust = 0)
  )
}

```

##



## Introduction


- The Global Education Policy Dashboard  applies framework of WDR 2018 

- Create and collect a concise set of indicators that allow tracking of key determinants of learning.  

- The Dashboard tracks three levels, the three Ps:
  * Practice
  * Policies
  * Politics.

## Survey of Public Officials

- The Policy Dashboard survey includes the politics, or the political and bureaucratic environment in which those policies are created and implemented:  
  * Are there political incentives and bureaucratic capacity to deliver learning for all children?  


## Survey Details

- Sample a total of 200 public officials.  

- Roughly 60 officials will be surveyed at the federal level
  *  Interview the HR director, finance director, planning director, and three randomly selected service focused departments.  
  *  Sample of 9 professional employees chosen at random from service departments.

- 140 officials surveyed at regional/district level.  
  * Selected from Districts/Regions where we survey schools
  * 7 officials will sampled each office:
    * Head of organization, HR director, two division directors from finance and planning, and 3 randomly selected professional employees 
    
## Notes on Scoring

- Most indicators are scored on a 1-5 scale with 1 being the lowest score and 5 being the best score.

```{r data, include=FALSE}

#set directory to bring in data
 if (str_to_lower(Sys.getenv("USERNAME")) == "wb577189"){

    work_dir  <- "C:/Users/wb577189/OneDrive - WBG/CNT/ETH/ETH_2021_GEPD/ETH_2021_GEPD_v01_RAW/Data/confidential/"
    
 } else if (Sys.info()["user"] == "wb577189"){

    work_dir<- "C:/Users/wb577189/OneDrive - WBG/CNT/ETH/ETH_2021_GEPD/ETH_2021_GEPD_v01_RAW/Data/confidential/"


    
  }

#load public official data
load(paste(work_dir, "Public_Officials/public_officials_indicators_data.RData", sep=""))

#load school data for comparisons
#load(paste(work_dir, "School/school_indicators_data.RData", sep=""))

#Load original sample of schools
# currentDate<-c("2020-02-12")
# sample_frame_name <- paste("C:/Users/WB469649/WBG/Ezequiel Molina - Dashboard (Team Folder)/Country_Work/Jordan/2019/Data/Sampling/school_sample_",currentDate,".RData", sep="")
# 
# load(sample_frame_name)

#compare data collected to original sample
# school_dta_short <- school_dta_short %>%
#   mutate(codigo.modular=as.numeric(school_code_preload)) %>%
#   left_join(data_set_updated) %>%
#   mutate(longitude=as.character(longitude)) %>%
#   mutate(latitude=as.character(latitude)) %>%
#   mutate(lat=if_else(is.na(lat), as.numeric(latitude), lat),
#          lon=if_else(is.na(lon), as.numeric(longitude), lon),
#          school_ipw=weights) %>%
#   mutate(school_ipw=if_else(is.na(school_ipw), median(school_ipw, na.rm=T), school_ipw)*total_4th) %>%
#   mutate(school_ipw=school_ipw/sum(school_ipw, na.rm = T))


#Create a function which will generate new binary variable using case_when, but 
#if value is misisng it will generate binary variable to be missing
#This is done a lot so will create function for it.
#e.g. school_absent=case_when(
#         m2sbq6_efft==6  ~ 1,
#         m2sbq6_efft!=6   ~ 0,
#         is.na(m2sbq6_efft) ~ as.numeric(NA))
bin_var <- function(var, val) {
  case_when(
    var==val  ~ 1,
    var!=val   ~ 0,
    is.na(var) ~ as.numeric(NA))
}

#create function to wrap text
wrapper <- function(x, ...) 
{
  paste(strwrap(x, ...), collapse = "\n")
}

```



## Overall performance

```{r overall, echo=FALSE}


data_plot <- public_officials_dta_clean %>%
  mutate(govt_tier=str_remove(govt_tier, "or equivalent")) %>%
  mutate(govt_tier=str_remove(govt_tier, "\\)")) %>%
    mutate(govt_tier=str_remove(govt_tier, "\\(")) %>%
  group_by(govt_tier) %>%
  select(interview__id,  govt_tier, national_learning_goals, mandates_accountability, quality_bureaucracy, impartial_decision_making) %>%
  pivot_longer(cols=c("national_learning_goals", "mandates_accountability", 
                      "impartial_decision_making","quality_bureaucracy" ),
               names_to = "indicators",
               values_to = "indicator_values") 

dataMedian <- summarise(group_by(data_plot, indicators , govt_tier), MD = round(median(indicator_values, na.rm=T),1))

  ggplot(data_plot, aes(x=indicators, y=indicator_values, fill=govt_tier)) + #now plot the output in a bar graph
    geom_boxplot(position="dodge") +
    geom_text(data = dataMedian, aes(x=indicators, y=MD, label=MD), 
              position = position_dodge(width = 0.8), size = 3, vjust = -0.5) +
    scale_x_discrete(labels = str_wrap(c("Impartial Decision Making",
                                         "Mandates & Accountability",
                                         "National Learning Goals",
                                         "Quality of the Bureaucracy"), width = 25)) + 
  xlab(str_wrap("Survey of Public Officials Indicators", width=75))+
  ylab("Scale (1-5)") +
  ggtitle(str_wrap("Boxplot of Overall Indicators for Survey of Public Officials", width=75)) +
  scale_fill_discrete(name="Government Level") +
  theme_bw() +
    theme(legend.position = "bottom") 

```


## Breakdowns by Central, Regional, District Level

```{r po_breakdown_level, include=FALSE}

ind_list<-c(
                'national_learning_goals', 'targeting', 'monitoring', 'incentives', 'community_engagement',
                'mandates_accountability' , 'coherence', 'transparency', 'accountability', 
                'quality_bureaucracy', 'knowledge_skills', 'work_environment', 'merit', 'motivation_attitudes','motivation_relative_start',
                'impartial_decision_making','politicized_personnel_management', 'politicized_policy_making', 'politicized_policy_implementation'
    )


    indicator_labels<-c(  "National Learning Goals", 'Targeting', 'Monitorinig', 'Incentives', 'Community Engagement',
                        "Mandates and Accountability", 'Coherence', 'Transparency', 'Accountability of Public Officials',
                        "Quality of Bureaucracy", 'Knowledge and Skills', 'Work Environment', 'Merit', 'Motivation and Attitudes', 'Imagine that when you started your motivation was 100. What number would you say your motivation was now relative to that?',
                        "Impartial Decision Making", 'Politicized personnel management', 'Politicized policy-making', 'Politicized policy-implementation'
                        )
  
    labels_df<-data.frame(name=as.character(ind_list),
                          varlabel=as.character(indicator_labels))




df<-final_indicator_data_BIMP


        sum_items<-colnames(public_officials_dta_clean[,grep(x=colnames(public_officials_dta_clean), pattern="IDM|NLG|ACM|QB")])
        metadata<-public_officials_metadata %>%
          mutate(varlabel=as.character(varlabel)) %>%
          bind_rows(labels_df)
        
        #add function to produce weighted summary stats
      my_skim<-    skim_with( numeric = sfl( mean = ~ mean(.,   na.rm=TRUE),
                                     sd = ~ sqrt(var(.,   na.rm=TRUE)),
                                     p25 = ~ (quantile(., probs=c(0.25),   na.rm=TRUE)),
                                     p50 = ~ (quantile(., probs=c(0.5),  na.rm=TRUE)),
                                     p75 = ~ (quantile(., probs=c(0.75),  na.rm=TRUE)),
                                     complete = ~ sum(!is.na(.))))

  public_officials_dta_clean <- public_officials_dta_clean %>%
    mutate(motivation_relative_start=as.numeric(motivation_relative_start))
      
  sumstats_public_officials <- public_officials_dta_clean %>%
              select(one_of(ind_list) ) 


  
  
  
  sumstats_public_officials_df<-my_skim(sumstats_public_officials) %>%
    yank("numeric") %>%
    mutate(variable=skim_variable) %>%
    select(variable, mean, sd, p0, p25, p50, p75, p100, complete,  hist) 
  
  
      sumstats_public_officials_df <- sumstats_public_officials_df %>%
            mutate(name=variable,
                   indicators=variable) %>%
            left_join(metadata) %>%
              mutate(ci_low=as.numeric(mean)-1.96*(as.numeric(sd)/sqrt(as.numeric(complete))),
                    ci_high=as.numeric(mean)+1.96*(as.numeric(sd)/sqrt(as.numeric(complete)))) %>%
            mutate(ci=paste("[",round(ci_low,2),", ", round(ci_high,2),"]", sep="")) %>%
            select(variable, varlabel, mean, ci)
    
  
   #Now do breakdown by govt_tier
    #mineduc
    sumstats_public_officials_mineduc <- public_officials_dta_clean %>%
      filter(govt_tier=="Ministry of Education (or equivalent)") 

    

    sumstats_public_officials_mineduc <- sumstats_public_officials_mineduc %>%
                select(one_of(ind_list) ) 

    
    
    
    sumstats_public_officials_mineduc_df<-my_skim(sumstats_public_officials_mineduc) %>%
    yank( "numeric") %>%
    mutate(variable=skim_variable) %>%
    select(variable, mean, sd, p0, p25, p50, p75, p100, complete,  hist) 
    
    
    #add variable label
    sumstats_public_officials_mineduc_df <- sumstats_public_officials_mineduc_df %>%
      mutate(name=variable,
             indicators=variable) %>%
      left_join(metadata) %>%
      mutate(ci_low=as.numeric(mean)-1.96*(as.numeric(sd)/sqrt(as.numeric(complete))),
             ci_high=as.numeric(mean)+1.96*(as.numeric(sd)/sqrt(as.numeric(complete)))) %>%
      mutate(ci=paste("[",round(ci_low,2),", ", round(ci_high,2),"]", sep="")) %>%
      mutate(mean_mineduc=mean,
             ci_mineduc=ci) %>%
      select(variable, varlabel, mean_mineduc, ci_mineduc)
    
   #region
    sumstats_public_officials_region <- public_officials_dta_clean %>%
      filter(govt_tier=="Regional office (or equivalent)") 

    

    sumstats_public_officials_region <- sumstats_public_officials_region %>%
              select(one_of(ind_list) ) 
    
    
    
    sumstats_public_officials_region_df<-my_skim(sumstats_public_officials_region) %>%
    yank( "numeric") %>%
    mutate(variable=skim_variable) %>%
    select(variable, mean, sd, p0, p25, p50, p75, p100, complete,  hist) 
    
    
    #add variable label
    sumstats_public_officials_region_df <- sumstats_public_officials_region_df %>%
      mutate(name=variable,
             indicators=variable) %>%
      left_join(metadata) %>%
      mutate(ci_low=as.numeric(mean)-1.96*(as.numeric(sd)/sqrt(as.numeric(complete))),
             ci_high=as.numeric(mean)+1.96*(as.numeric(sd)/sqrt(as.numeric(complete)))) %>%
      mutate(ci=paste("[",round(ci_low,2),", ", round(ci_high,2),"]", sep="")) %>%
      mutate(mean_region=mean,
             ci_region=ci) %>%
      select(variable, varlabel, mean_region, ci_region)
    
       #district
    sumstats_public_officials_district <- public_officials_dta_clean %>%
      filter(govt_tier=="District office (or equivalent)") 

    

    sumstats_public_officials_district <- sumstats_public_officials_district %>%
              select(one_of(ind_list) ) 
    
    
    
    sumstats_public_officials_district_df<-my_skim(sumstats_public_officials_district) %>%
          yank( "numeric") %>%
        mutate(variable=skim_variable) %>%
        select(variable, mean, sd, p0, p25, p50, p75, p100, complete,  hist) 
    
    
    #add variable label
    sumstats_public_officials_district_df <- sumstats_public_officials_district_df %>%
      mutate(name=variable,
             indicators=variable) %>%
      left_join(metadata) %>%
      mutate(ci_low=as.numeric(mean)-1.96*(as.numeric(sd)/sqrt(as.numeric(complete))),
             ci_high=as.numeric(mean)+1.96*(as.numeric(sd)/sqrt(as.numeric(complete)))) %>%
      mutate(ci=paste("[",round(ci_low,2),", ", round(ci_high,2),"]", sep="")) %>%
      mutate(mean_district=mean,
             ci_district=ci) %>%
      select(variable, varlabel, mean_district, ci_district)
    
    
    #now bind urban/rural with the main results
    sumstats_public_officials_df <- sumstats_public_officials_df %>%
      left_join(sumstats_public_officials_mineduc_df) %>%
      left_join(sumstats_public_officials_region_df) %>%
      left_join(sumstats_public_officials_district_df)
  
  
  

  sumstats_df <- sumstats_public_officials_df %>%
    arrange(factor(varlabel, levels=indicator_labels))
  

   
   sumstats_df <- sumstats_df %>%
     select(variable, varlabel,  mean, ci, mean_mineduc, ci_mineduc, mean_region, ci_region, mean_district, ci_district)

   
    
   
```



## Breakdowns by Managers vs Technical Staff



```{r po_breakdown_level2, include=FALSE}


        #add function to produce weighted summary stats

    
  
   #Now do breakdown by govt_tier
    #mineduc
    sumstats_public_officials_manager <- public_officials_dta_clean %>%
      filter(DEM1q12n==1) 

    

    sumstats_public_officials_manager <- sumstats_public_officials_manager %>%
                select(one_of(ind_list) ) 

    
    
    
    sumstats_public_officials_manager_df<-my_skim(sumstats_public_officials_manager) %>%
          yank( "numeric") %>%
          mutate(variable=skim_variable) %>%
          select(variable, mean, sd, p0, p25, p50, p75, p100, complete,  hist)  
    
    
    #add variable label
    sumstats_public_officials_manager_df <- sumstats_public_officials_manager_df %>%
      mutate(name=variable,
             indicators=variable) %>%
      left_join(metadata) %>%
      mutate(ci_low=as.numeric(mean)-1.96*(as.numeric(sd)/sqrt(as.numeric(complete))),
             ci_high=as.numeric(mean)+1.96*(as.numeric(sd)/sqrt(as.numeric(complete)))) %>%
      mutate(ci=paste("[",round(ci_low,2),", ", round(ci_high,2),"]", sep="")) %>%
      mutate(mean_manager=mean,
             ci_manager=ci) %>%
      select(variable, varlabel, mean_manager, ci_manager)
    
   #technical
    sumstats_public_officials_technical <- public_officials_dta_clean %>%
      filter(DEM1q12n==2) 

    

    sumstats_public_officials_technical <- sumstats_public_officials_technical %>%
              select(one_of(ind_list) ) 
    
    
    
    sumstats_public_officials_technical_df<-my_skim(sumstats_public_officials_technical) %>%
          yank( "numeric") %>%
          mutate(variable=skim_variable) %>%
          select(variable, mean, sd, p0, p25, p50, p75, p100, complete,  hist) 
    
    
    #add variable label
    sumstats_public_officials_technical_df <- sumstats_public_officials_technical_df %>%
      mutate(name=variable,
             indicators=variable) %>%
      left_join(metadata) %>%
      mutate(ci_low=as.numeric(mean)-1.96*(as.numeric(sd)/sqrt(as.numeric(complete))),
             ci_high=as.numeric(mean)+1.96*(as.numeric(sd)/sqrt(as.numeric(complete)))) %>%
      mutate(ci=paste("[",round(ci_low,2),", ", round(ci_high,2),"]", sep="")) %>%
      mutate(mean_technical=mean,
             ci_technical=ci) %>%
      select(variable, varlabel, mean_technical, ci_technical)
    
       
    
    #now bind urban/rural with the main results
    sumstats_public_officials_df2 <- sumstats_public_officials_df %>%
      left_join(sumstats_public_officials_manager_df) %>%
      left_join(sumstats_public_officials_technical_df) 

  
  

  sumstats_df2 <- sumstats_public_officials_df2 %>%
    arrange(factor(varlabel, levels=indicator_labels))
  

   
   sumstats_df2 <- sumstats_df2 %>%
     select(variable, varlabel,  mean, ci, mean_manager, ci_manager, mean_technical, ci_technical)

   
    
   
```

```{r datatable2, echo=FALSE}
 #add in custom column sub-headers
  sketch = htmltools::withTags(table(
    class = 'display',
    thead(
      tr(
        th( rowspan = 2, 'Indicator'),
        th( rowspan = 2, 'Label'),
        th(colspan = 2, 'Overall'),
        th(colspan = 2, 'Managers'),
        th(colspan = 2, 'Technical Staff'),
      ),
      tr(
        lapply(rep(c('Mean', '95% Confident Interval'), 3), th)
      )
    )
  ))
  
  # create 19 breaks and 20 rgb color values ranging from white to red
  

  DT::datatable(sumstats_df2, caption="Summary Statistics of Dashboard Indicators - Ethiopia 2021",
                container = sketch,
                rownames=FALSE,
                class='cell-border stripe',
                escape = FALSE,
                extensions = c ('Buttons', 'FixedHeader'), 
                options=list(
                  dom = 'Bfrtip',
                  buttons = c('csv'),
                  pageLength = 80,
                  scrollX = TRUE, 
                  paging=FALSE,
                  ordering=F)) %>%
    formatRound(columns = c('mean', 'ci', 'mean_manager', 'ci_manager', 'mean_technical', 'ci_technical'),
                digits=2)  

  



```