---
title: "Chad Sampling Notes"
author: "Brian Stacy"
format: html
date: '2023-03-02'
execute: 
  echo: false
  warning: false
---

```{r}
#|label: setup
#| include: false

library(tidyverse)
library(here)
library(readxl)
library(flextable) 
library(vtable)

#Country name
country <-'TCD'
country_name <- "Chad"
year <- '2023'
#specify name of sampling frame file.  This needs to be a csv file
file_frame<-"Echantillonnage_BM.xlsx"
frame_sheet <- "Feuil1"




set.seed(8473227)


#########################
# File paths #
#########################
#The download_folder will be the location of where raw data is downloaded from the API
#The save_folder will be the location of where cleaned data is stored



if (str_to_lower(Sys.getenv("USERNAME")) == "wb469649" ){
  #project_folder  <- "//wbgfscifs01/GEDEDU/datalib-edu/projects/gepd"
  project_folder  <- paste0("C:/Users/",str_to_lower(Sys.getenv("USERNAME")),"/WBG/HEDGE Files - HEDGE Documents/GEPD/CNT/")
  sampling_folder <-file.path(paste(project_folder,country,paste(country,year,"GEPD", sep="_"),paste(country,year,"GEPD_v01_M", sep="_"),"Data","/Sampling", sep="/"))
  
} else if (str_to_lower(Sys.getenv("USERNAME")) == "wb577189" ){

  project_folder  <- paste0("C:/Users/",str_to_lower(Sys.getenv("USERNAME")),"/OneDrive - WBG/GEPD/CNT/")
  sampling_folder <-file.path(paste(project_folder,country,paste(country,year,"GEPD", sep="_"),paste(country,year,"GEPD_v01_M", sep="_"),"Data","/Sampling", sep="/"))
  
} else {
  download_folder <- choose.dir(default = "", caption = "Select folder to open data downloaded from API")
  save_folder <- choose.dir(default = "", caption = "Select folder to save final data")

}


```


## Introduction

This file outlines the sampling strategy for Chad in 2023.  A sample of 260 schools will be selected.  Schools will be selected by strata based on the region.  Breakdowns will be offered based on the urban/rural status of the school, but because there are roughly equal numbers of urban/rural schools, the urban/rural status is not an explicit part of the strata.

## General Notes on Sampling
The aim of the Global Education Policy Dashboard school survey is to produce nationally representative estimates, which will be able to detect changes in the indicators over time at a minimum power of 80% and with a 0.05 significance level.  We also wish to detect differences by urban/rural location. 

For our school survey, we will employ a two-stage random sample design, where in the first stage a sample of around 200 schools, based on local conditions, is drawn, chosen in advance by the Bank staff.  In the second stage, a sample of teachers and students will be drawn to answer questions from our survey modules, chosen in the field.  A total of 10 teachers will be sampled for absenteeism.  Five teachers will be interviewed and given a content knowledge exam.  Three 1st grade students will be assessed at random, and a classroom of 4th grade students will be assessed at random.  Stratification will be based on the school’s urban/rural classification and based on region. When stratifying by region, we will work with our partners within the country to make sure we include all relevant geographical divisions. 



 

Sampling Approach for Global Education Policy Dashboard

This document will provide an overview of the sampling strategy used in the Global Education Policy Dashboard (GEPD) surveys, as well as remaining questions.  New data for the dashboard will be collected using three main instruments: a School Survey, an Expert Survey, and a Survey of Public Officials. More information pertaining to each can be found below.  The goal of the Global Education Policy Dashboard is to provide summary information at the national level on a set of 35 indicators and to allow countries to track progress on those indicators over a short time frame (every 2 years).  Specifically, we aim to produce nationally representative estimates, which will be able to detect changes in the indicators over time at a minimum power of 80% and with a 0.05 significance level.  We also wish to disaggregate by urban/rural.

School Survey: The School Survey will collect data primarily on Practices (the quality of service delivery in schools), but also on some de facto Policy and school-level Politics indicators.  It will consist of streamlined versions of existing instruments—including SDI and SABER SD on teachers, 4th grade students, and inputs/infrastructure, TEACH on pedagogical practice, GECDD on school readiness of young children, and DWMS on management quality—together with new questions to fill gaps in those instruments.  Though the number of modules is similar to the full version of SDI, the number of items within each module is significantly lower. In each country, this survey will be administered in a nationally representative sample of 200-300 schools, selected through stratified  random sampling. As currently envisioned, the School Survey will include 8 short modules.
Expert Survey: The Expert Survey will collect information to feed into the policy indicators.  This survey will be filled out by key informants in each country, drawing on their knowledge to identify key elements of the policy framework (as in the SABER approach to policy-data collection that the Bank has used over the past 7 years).  The survey will have 4 modules with each including approximately ten questions.

Survey of Public Officials: The Survey of Public Officials will collect information about the capacity and orientation of the bureaucracy, as well as political factors affecting education outcomes. This survey will be a streamlined and education-focused version of the civil-servant surveys that the Bank’s Bureaucracy Lab has implemented recently in several countries, and the dashboard team is collaborating closely with DEC and Governance GP staff to develop this instrument.  As currently envisioned, the survey will be administered to a random sample of about 200 staff serving in the central education ministry and district education offices.  It will include questions about technical and leadership skills, work environment, stakeholder engagement, clientelism, and attitudes and behaviors.

## Chad Sampling


```{r}
#| label: data

#read sample frame
df_raw<-read_excel(paste(sampling_folder, file_frame, sep="/"),
              sheet=frame_sheet,
              skip=2) 

#create some new names
df <- df_raw %>%
  mutate(
    urban_rural=case_when(
      LOCALISATION=="Rural" ~ "Rural",
      LOCALISATION=="Urbain" ~ "Urban"),
    ownership = case_when(
      STATUT=="Public" ~ "Public",
      STATUT=="Privé laïc" ~ "Secular Private",
      STATUT=="Privé islamique" ~ "Islamic Private",
      STATUT=="Privé catholique" ~ "Catholic Private",
      STATUT=="Privé protestant" ~ "Protestant Private",
      STATUT=="Communautaire" ~ "Community"
    ),
    rural=as.numeric(urban_rural=="Rural"),
    public=as.numeric(ownership=="Public"),
    total_students_grade_4=as.numeric(CM1_G) + as.numeric(CM1_F),
    total_students_grade_4_female= as.numeric(CM1_F),
    total_students_grade_4_male=as.numeric(CM1_G),
    total_students_grade_1=as.numeric(CP1_G) + as.numeric(CP1_F),
    total_students_grade_1_female= as.numeric(CP1_F),
    total_students_grade_1_male=as.numeric(CP1_G),
    total_students_male=as.numeric(ENSEMBLE_G),
    total_students_female=as.numeric(ENSEMBLE_F),
    total_students=total_students_male+total_students_female,
    school_code=as.numeric(`CODE ETABLISSEMENT`)
  ) %>%
    filter(!is.na(`CODE ETABLISSEMENT`)
    ) 

#update data frame to just include schools with more than 3 4th grade and 3 1st grade students
df_updated <- df %>%
  filter(total_students_grade_4>=3,
         total_students_grade_1 >=3) %>%
  mutate(Region=DPEN)
```

The raw sampling frame contains `r scales::comma(nrow(df_raw))` schools.  When we restrict to schools with more than three 4th grade students and three 1st grade students, we have `r scales::comma(nrow(df_updated))` schools.


```{r}
#| label: sumstatsframe
#| tbl-cap: Summary Statistics for Sampling Frame

#create list of indicators for 
  indicator_list2<-c('total_students_male',
                    'total_students_female',
                    'total_students',
                    'total_students_grade_4_male',
                    'total_students_grade_4_female',
                    'total_students_grade_4',
                    'total_students_grade_1_male',
                    'total_students_grade_1_female',
                    'total_students_grade_1',                    
                    'public',
                    'rural',
                    'ownership')

indicator_labels2<-c('Total Male Students',
                    'Total Female Students',
                    'Total Students',
                    'Total 4th Grade Male Students',
                    'Total 4th Grade Female Students',
                    'Total 4th Grade Students',
                    'Total 1st Grade Male Students',
                    'Total 1st Grade Female Students',
                    'Total 1st Grade Students',                    
                    'Public Schools',
                    'Rural Schools',
                    'Ownerships'
                    )

sumstats<-df_updated %>%
  dplyr::select(indicator_list2) 

frame_size=nrow(df)

sumtable(sumstats, out='return') %>%
  mutate(Variable=factor(Variable, levels=c(indicator_list2,'... Catholic Private','... Community','... Islamic Private','... Public','... Secular Private'),
                         labels=c(indicator_labels2,'... Catholic Private','... Community','... Islamic Private','... Public','... Secular Private'))) %>%
  flextable() %>%
  autofit() %>%
  theme_booktabs() 
```

Here are the counts by the 23 regions.

```{r}
#| label: sumstatsreg
#| tbl-cap: Regional Counts in the Sampling Frame

#create list of indicators for 
std_border = officer::fp_border(color="black", width = 1)


df_updated %>%
  group_by(DPEN) %>%
  summarise(N=n()) %>%
  ungroup() %>%
  mutate(Percentage = paste0(round(100*N/sum(N),1),"%")) %>%
  janitor::adorn_totals("row")  %>%  
  rename(Region=DPEN) %>%
  flextable() %>%
  theme_booktabs() %>%
  hline( i = 23) %>%
  autofit() 
```



# Sampling

```{r echo=TRUE}


strata_df <- df_updated %>%
    group_by(Region) %>%
    summarise(nstudents_district=sum(total_students),
              total_district=n()
    ) %>%
    ungroup() %>%
    mutate(share_district=100*round(nstudents_district/sum(nstudents_district),3),
           sample_size=share_district*2.5)

# get numbers to select from each district

strata_df <- df_updated %>%
  group_by(Region) %>%
  summarise(nstudents_district=sum(total_students),
                     total_district=n()
) %>%
  ungroup() %>%
  mutate(share_district=100*round(nstudents_district/sum(nstudents_district),3),
         sample_size=case_when(
           Region=="BARH EL GAZAL"     ~ 4,
           Region=="BATHA"  ~ 4,
           Region=="BORKOU" ~ 4,
           Region=="CHARI BAGUIRMI" ~ 8,
           Region=="ENNEDI EST" ~ 4,
           Region=="ENNEDI OUEST" ~ 4,
           Region=="GUERA"        ~ 9,     
           Region=="HADJER LAMIS" ~ 5,     
           Region=="KANEM"        ~ 4,    
           Region=="LAC"        ~ 9,       
           Region=="LOGONE OCCIDENTAL" ~ 21,
           Region=="LOGONE ORIENTAL"   ~ 26,
           Region=="MANDOUL"          ~ 20, 
           Region=="MAYO KEBBI EST"   ~ 22, 
           Region=="MAYO KEBBI OUEST"  ~ 18,
           Region=="MOYEN CHARI"       ~ 16,
           Region=="OUADDAÏ"           ~ 12,
           Region=="SALAMAT" ~ 4,
           Region=="SILA"    ~ 4,          
           Region=="TANDJILE" ~ 20,        
           Region=="TIBESTI"  ~ 4,        
           Region=="VILLE DE NDJAMENA" ~ 32,
           Region=="WADI FIRA" ~ 6,
         ))

strata_df %>%
  flextable() %>%
  add_header_lines('Share of Students per Region and School Type')


```

Select the sample and save.
```{r option2, echo=TRUE}
# set the numbers of schools selected by strata (grade)

sample_df <- df_updated %>%
  left_join(strata_df) %>%
  mutate(
    totalstudents=sum(total_students_grade_4),
  ) %>%
  group_by(Region ) %>%
  mutate(strata_count=n(),
         strata_size=sum(total_students_grade_4),
         strata_school_prob=strata_size/totalstudents) %>%
  sample_n(size = mean(sample_size), weight =total_students_grade_4) %>%
  ungroup() %>%
  mutate(strata_prob=(sample_size)*(total_students_grade_4/strata_size),
         ipw=strata_school_prob*(1/strata_prob))


write_excel_csv(sample_df, file=paste0(sampling_folder, "/GEPD_TCD_sample_",Sys.Date(),".csv"))

#get weights for all schools
weights_df <- df_updated %>%
  left_join(strata_df) %>%
  mutate(
    totalstudents=sum(total_students_grade_4),
  ) %>%
  group_by(Region ) %>%
  mutate(strata_count=n(),
         strata_size=sum(total_students_grade_4),
         strata_school_prob=strata_size/totalstudents) %>%
  ungroup() %>%
  mutate(strata_prob=(sample_size)*(total_students_grade_4/strata_size),
         ipw=strata_school_prob*(1/strata_prob))


write_excel_csv(weights_df, file=paste0(sampling_folder, "/GEPD_TCD_weights_",Sys.Date(),".csv"))
```
Sample by Region

```{r}
sample_df %>%
  group_by(DPEN, rural) %>%
  summarise(N=n()) %>%
  ungroup() %>%
  mutate(Percentage = paste0(round(100*N/sum(N),1),"%")) %>%
  janitor::adorn_totals("row")  %>%  
  rename(Region=DPEN) %>%
  flextable() %>%
  theme_booktabs() %>%
  autofit() 
```

Sample by Urban/Rural

```{r}
sample_df %>%
  group_by(rural) %>%
  summarise(N=n()) %>%
  ungroup() %>%
  mutate(Percentage = paste0(round(100*N/sum(N),1),"%")) %>%
  janitor::adorn_totals("row")  %>%  
  flextable() %>%
  theme_booktabs() %>%
  autofit() 
```


Sample by Ownership

```{r}
sample_df %>%
  group_by(STATUT) %>%
  summarise(N=n()) %>%
  ungroup() %>%
  mutate(Percentage = paste0(round(100*N/sum(N),1),"%")) %>%
  janitor::adorn_totals("row")  %>%  
  flextable() %>%
  theme_booktabs() %>%
  autofit() 
```

# Replacement Schools

Below is a list of replacement schools for each sampled school. Replacement schools were randomly selected among the set of schools in the district, not including the orginally sampled schools. Each row contains the school name, location, and other information for each replacement school.  In the final 5 columns of the database is the school code, school name, region, and district of the originally sampled school for which this school serves as a replacement. 



```{r update_dataset_public, echo=FALSE, message=FALSE, warning=FALSE}
#define sampled schools in sample dataset
sample_chosen <- sample_df %>%
  mutate(sample="Sampled School") 

#add sample schools back to original database
data_set_updated_chosen <- df_updated %>%
  left_join(sample_chosen) 

#get list of tehsil
sampled_districts <- sample_chosen %>%
  group_by( Region) %>% 
  summarise(sampled_districts=n()
            )

# select one replacement per district
sample_replace <- data_set_updated_chosen %>%
  left_join(sampled_districts) %>%
  filter(!is.na(sampled_districts)) %>%
  filter(is.na(sample)) %>%
  group_by(Region) %>% 
  sample_n( mean(3*sampled_districts), weight=total_students_grade_4) %>% #select two replacement schools
  mutate(sample='Replacement School') %>%
  arrange(Region, ETABLISSEMENT) 

sample_replace2 <- sample_chosen %>%
    bind_rows(sample_chosen) %>% #add a duplicate observation for matching to two replacement schools
    bind_rows(sample_chosen) %>% #add a duplicate observation for matching to two replacement schools
    arrange(Region, ETABLISSEMENT ) 


#add in school info for school that will be replaced
sample_replace$replaced_NOM_ETABLISSEMENT=sample_replace2$ETABLISSEMENT
sample_replace$replaced_CODE_ETABLISSEMENT=sample_replace2$`CODE ETABLISSEMENT`
sample_replace$replaced_Region=sample_replace2$Region



sample_replace %>%
  select(ETABLISSEMENT,`CODE ETABLISSEMENT`, ETABLISSEMENT, Region, replaced_NOM_ETABLISSEMENT, replaced_CODE_ETABLISSEMENT, replaced_Region) %>%
  DT::datatable( caption = 'List of Replacement Schools Chosen for Public School Sample') 

sample_replace <- sample_replace %>%
  select(ETABLISSEMENT,`CODE ETABLISSEMENT`, ETABLISSEMENT, Region, replaced_NOM_ETABLISSEMENT, replaced_CODE_ETABLISSEMENT, replaced_Region, everything())
  
write_excel_csv(sample_replace, paste(sampling_folder, '/sample_replacement_schools_', Sys.Date(),  '.csv', sep=""))



```

## May 15 replacements

In Chad, the insecurity prevented us from accessing some schools in Logone and Assila.  Draw replacements for these schools but outside of their respective province

```{r}
#replacements outside of Logon and Assila



#define sampled schools in sample dataset
sample_chosen2 <- sample_df %>%
  mutate(sample="Sampled School") %>%
  bind_rows(sample_replace %>% mutate(sample="1st Replacement Set"))
  

#add sample schools back to original database
data_set_updated_chosen2 <- df_updated %>%
  left_join(sample_chosen2) %>%
  filter(is.na(sample)) 


# select one replacement per district
sample_replace2 <- data_set_updated_chosen2 %>%
  mutate(
    sample_size=case_when(

           Region=="LOGONE OCCIDENTAL"   ~ 11,
           Region=="MANDOUL"          ~ 10, 

           Region=="OUADDAÏ"           ~ 12,
           Region=="SALAMAT" ~ 0,
           TRUE ~ 0

         )) %>%
  group_by(Region) %>% 
  sample_n( mean(sample_size), weight=total_students_grade_4) %>% #select two replacement schools
  mutate(sample='2nd Replacement School') %>%
  arrange(Region, ETABLISSEMENT) 

#list of schools
sch_list <- c(223033,12008,11805,4196,1244,10131,13154,1265,10487,1337,12322)

sample_replace_2 <- sample_chosen %>%
    bind_rows(sample_chosen) %>% #add a duplicate observation for matching to two replacement schools
    bind_rows(sample_chosen) %>% #add a duplicate observation for matching to two replacement schools
    arrange(Region, ETABLISSEMENT )  %>%
  filter(`CODE ETABLISSEMENT` %in% sch_list)


#add in school info for school that will be replaced
#add in school info for school that will be replaced
sample_replace2$replaced_NOM_ETABLISSEMENT=sample_replace_2$ETABLISSEMENT
sample_replace2$replaced_CODE_ETABLISSEMENT=sample_replace_2$`CODE ETABLISSEMENT`
sample_replace2$replaced_Region=sample_replace_2$Region



sample_replace2 %>%
  select(ETABLISSEMENT,`CODE ETABLISSEMENT`, ETABLISSEMENT, Region, replaced_NOM_ETABLISSEMENT, replaced_CODE_ETABLISSEMENT, replaced_Region) %>%
  DT::datatable( caption = 'List of Replacement Schools Chosen for Public School Sample') 

sample_replace2 <- sample_replace2 %>%
  select(ETABLISSEMENT,`CODE ETABLISSEMENT`, ETABLISSEMENT, Region, replaced_NOM_ETABLISSEMENT, replaced_CODE_ETABLISSEMENT, replaced_Region, everything())
  
write_excel_csv(sample_replace2, paste(sampling_folder, '/sample_replacement_schools_', Sys.Date(),  '.csv', sep=""))


```
```


## Pilot Schools

A sample of 30 schools in NDJAMENA that are not in our sample were selected for additional piloting of new instruments.

```{r echo=TRUE}

picked_df <- sample_df %>% bind_rows(sample_replace)

#get list of schools already selected
selected_list <- picked_df$`CODE ETABLISSEMENT`

# get numbers to select from each district
pilot_strata_df <- df_updated %>%
  group_by(Region) %>%
  summarise(nstudents_district=sum(total_students),
                     total_district=n()
) %>%
  ungroup() %>%
  mutate(share_district=100*round(nstudents_district/sum(nstudents_district),3),
         sample_size=case_when(
           Region=="VILLE DE NDJAMENA" ~ 30,
           TRUE ~ 0
         ))

#select the 20 schools
pilot_df <- df_updated %>%
  filter(!(`CODE ETABLISSEMENT` %in% selected_list)) %>%
  left_join(pilot_strata_df) %>%
  mutate(
    totalstudents=sum(total_students_grade_4),
  ) %>%
  filter(Region=="VILLE DE NDJAMENA") %>%
  group_by(Region ) %>%
  mutate(strata_count=n(),
         strata_size=sum(total_students_grade_4),
         strata_school_prob=strata_size/totalstudents) %>%
  sample_n(size = mean(sample_size), weight =total_students_grade_4) %>%
  ungroup() %>%
  mutate(strata_prob=(sample_size)*(total_students_grade_4/strata_size),
         ipw=strata_school_prob*(1/strata_prob))


write_excel_csv(pilot_df, file=paste0(sampling_folder, "/GEPD_Chad_pilot_sample_",Sys.Date(),".csv"))



```

# Sanity Checks

Below I will use the survey weights to estimate aspects of the school that are available in the sampling frame. This includes whether the school is nomadic.  These data were collected as part of the school EMIS in Chad  The population mean from the full sampling frame is compared to the estimated mean from the school sample using the sampling weights.  Estimated means very far from the population mean can indicate there is something wrong with the weights or that the school sample is biased.

The estimates based on the school weights are similar and within the confidence interval of those produced using the sampling frame.

```{r}
library(srvyr)
#sanity check of the sampling weights and results
# use weights to estimate population average of internet prevalence

df_updated %>%
  ungroup() %>%
  summarise(nomadic=mean(as.numeric(`ECOLE_NOMADE? 1=OUI, 0=NON`), na.rm=TRUE),
            grd5_girls=mean(as.numeric(CM2_F), na.rm=TRUE)
            ) %>%
  flextable() %>%
  add_header_lines("Population estimate")




sample_df %>%
  ungroup() %>%
  as_survey_design(strata=c('Region'),
                   weight=ipw) %>%
    summarise(nomadic=survey_mean(as.numeric(`ECOLE_NOMADE? 1=OUI, 0=NON`), na.rm=TRUE),
              grd5_girls=survey_mean(as.numeric(CM2_F), na.rm=TRUE)
              ) %>%
  flextable() %>%
  add_header_lines("Estimate based on Schools Visited and Sampling Weights")
```