---
title: "Madagascar Teacher Cleaning"
author: "Brian Stacy"
date: "9/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(haven)
library(vtable)
library(here)
library(readxl)
library(stringr)
library(Hmisc)
library(naniar)

#Country name
country <-'MDG'
country_name <- "Madagascar"
year <- '2021'

#########################
# File paths #
#########################
#The download_folder will be the location of where raw data is downloaded from the API
#The save_folder will be the location of where cleaned data is stored



if (str_to_lower(Sys.getenv("USERNAME")) == "wb469649" ){
  #project_folder  <- "//wbgfscifs01/GEDEDU/datalib-edu/projects/gepd"
  project_folder  <- "C:/Users/wb469649/WBG/HEDGE Files - HEDGE Documents/GEPD-Confidential/CNT/"
  download_folder <-file.path(paste(project_folder,country,paste(country,year,"GEPD", sep="_"),paste(country,year,"GEPD_v01_RAW", sep="_"),"Data/raw/School", sep="/"))
  sampling_folder <-file.path(paste(project_folder,country,paste(country,year,"GEPD", sep="_"),paste(country,year,"GEPD_v01_RAW", sep="_"),"Data/sampling", sep="/"))
  confidential_folder <- file.path(paste(project_folder,country,paste(country,year,"GEPD", sep="_"),paste(country,year,"GEPD_v01_RAW", sep="_"),"Data/confidential/School", sep="/"))
  save_folder <- file.path(paste(project_folder,country,paste(country,year,"GEPD", sep="_"),paste(country,year,"GEPD_v01_RAW", sep="_"),"Data/anonymized/School", sep="/"))
  backup_onedrive="no"
  save_folder_onedrive <- file.path(paste("C:/Users/wb469649/WBG/Ezequiel Molina - Dashboard (Team Folder)/Country_Work/",country_name,year,"Data/clean/School", sep="/"))
  
} else {
  download_folder <- choose.dir(default = "", caption = "Select folder to open data downloaded from API")
  save_folder <- choose.dir(default = "", caption = "Select folder to save final data")

}


```

```{r functions}

## Function to save metadata for each question in each module
  makeVlist <- function(dta) { 
    varlabels <- sapply(dta, function(x) attr(x,"label"))
    vallabels <- sapply(dta, function(x) attr(x,"labels"))
    tibble(name = names(varlabels),
           varlabel = varlabels, vallabel = vallabels) 
  }

## Function to save the number of NAs per variable
  makeNAlist <- function(dta) { 
    varlabels <- sapply(dta, function(x) attr(x,"label"))
    vallabels <- sapply(dta, function(x) attr(x,"labels"))
    varmissing <- sapply(dta, function(x) sum(is.na(x)))
    tibble(name = names(varlabels),
           varlabel = varlabels, vallabel = vallabels, varmissing=varmissing) 
  }


bin_var <- function(var, val) {
  case_when(
    var==val  ~ 1,
    var!=val   ~ 0,
    is.na(var) ~ as.numeric(NA))
}



bin_var_2 <- function(var, val) {
  if_else(var==val, 
          as.numeric(1),
          as.numeric(var))
}
```


# Load Data

Read in data for Madagascar.  All teacher questionnaire files were numbered as Module 3 in the Madagascar school survey.  These files will be read in one at a time.

Start with non-teacher files, including the school file.

```{r schoolload}
## 2. Calling in datasets ----  
# load sampling frame

sampling_frame <- read_excel(path=paste0(sampling_folder,'/Echantillons SDI V12.xlsx'))

## 1st grade assessment ----
first_grade <- read_dta(file.path(download_folder, "/21-M5.dta")) %>%
  filter(s_type_ecole==3) #just keep dashboard schools

## 4th grade assessment ----
fourth_grade <- read_dta(file.path(download_folder, "/20-M5_liste.dta")) %>%
  filter(s_type_ecole==3) #just keep dashboard schools

## School level data ----
school_dta<-read_dta(file.path(download_folder, "/01-SECABD24DE.dta")) %>%
  filter(s_type_ecole==3) #just keep dashboard schools
vtable(school_dta)

## Infrastructure school ----
infrastructure_dta <- read_dta(file.path(download_folder, "/06-M1SECC.dta")) %>%
  filter(s_type_ecole==3) #just keep dashboard schools
vtable(infrastructure_dta)

## Infrastructure school : blackboard, light, cholk ----
#input_dta <- read_dta(file.path(download_folder, "/astata/17-M4BC..dta"))
input_dta<-read_dta(file.path(download_folder, "/17-M4BC.dta")) %>%
  filter(s_type_ecole==3) #just keep dashboard schools

vtable(input_dta)

## Management school  ----
management_dta <- read_dta(file.path(download_folder, "/11-M3A.dta")) %>%
  filter(s_type_ecole==3) #just keep dashboard schools
vtable(management_dta)



#rename a few key variables up front
school_dta<- school_dta %>%
  mutate(
         enumerator_number=s_enqueteur_code ,
         survey_time=s_date_heure_fin	,
         school_code=s_ecole_code
         # lat=s_latitude,
         # lon=s_longitude,
  ) %>%
  mutate(school_code=if_else(school_code==0, 328328, school_code)) %>%
  mutate(school_code=if_else(school_code==62181, 558163, school_code))  #fix an error where the school code was loaded incorrectly



#------------------------------------------------------------------------------#
## 3. Lists of variables ----  

#list additional info that will be useful to keep in each indicator dataframe
preamble_info <- c( "s_ecole_code", 
                   "s_region_code", "s_cisco_code", "s_commune_name",   
                   "s_commune_code", "s_ecole_name", "s_zap_name", "s_zap_code",
                   "s_urbain", "s_date_visite", "s_enqueteur_code", "s_type_ecole", "s_public", "s_etab_code",
                   "lat","lon"
                   )

school_dta_preamble <- input_dta %>%
  left_join(school_dta) %>%
  mutate(
    lat=s_latitude,
    lon=s_longitude
  ) %>%
  select(preamble_info)

```

Now load the teacher files.

```{r teacherload}
list.files(path=download_folder)

#Teacher absence file
teacher_roster_dta <- read_dta(paste0(download_folder, '/08-M2AB1AB.dta')) %>%
  left_join(school_dta_preamble) %>%
  filter(s_type_ecole==3) #just keep dashboard schools

#Teacher questionnaire file
teacher_questionnaire_dta_raw <- read_dta(paste0(download_folder, '/10-M2BA1_E.dta')) %>%
  select(-c("s_region_code", "s_cisco_code", "s_commune_name", "s_commune_code", "s_ecole_name", "s_zap_name", "s_zap_code", "s_urbain", "s_date_visite", "s_enqueteur_code", "s_public", "s_etab_code")) %>%
  left_join(school_dta_preamble) %>%
  filter(s_type_ecole==3) #just keep dashboard schools

#Teacher assessment file
teacher_assessment_dta_raw <- read_dta(paste0(download_folder, '/24-M6CORR.dta')) %>% #read in the corrected version of the teacher assessment
  select(-c("s_ecole_nom","s_region_code","id1_nom", "s_cisco_code","s_cisco_nom", "s_commune_nom",   "s_commune_code",  "nom_fokontany",   "id4_nom", "numero_fiche" )) %>% #drop some information that may conflict with primary school file.  Just match on school code
  left_join(school_dta_preamble) %>%
  filter(s_type_ecole==3) #just keep dashboard schools

teacher_pedagogy_dta <- read_dta(paste0(download_folder, '/17-M4BC.dta')) %>%
  left_join(school_dta_preamble) %>%
  filter(s_type_ecole==3) #just keep dashboard schools

```
# Practice Indicators

## 1st Grade Assessment

```{r g1}
## 5. Cleaning : 1st grade Level ----  

#create indicator for % correct on student assessment
#Note:  in the future we could incorporate irt program like mirt
#number of missing values
first_grade <- first_grade %>%
  mutate(n_mssing_ECD=n_miss_row(.))

#rename a few key variables up front
first_grade<- first_grade %>%
  mutate(ecd_student_name=d_m5e3_01  ,
         ecd_student_age=d_m5e3_02,
         ecd_student_male=bin_var(d_m5e3_03,1),
         ecd_consent=bin_var(d_m5e3_00,1)
         
  ) %>% # Rename the variables to have them describe clearly the type of assessment being conducted
  
  rename(
    # Vocabulary
    m6s2q1_vocabn = d_m5e3_04a,
    m6s2q1b_vocabn = d_m5e3_04b,
    
    # Comprehension
    m6s2q5a_comprehension = d_m5e3_05a,
    m6s2q5b_comprehension = d_m5e3_05b,
    m6s2q5c_comprehension = d_m5e3_05c, 
    m6s2q5d_comprehension = d_m5e3_05d, 
    m6s2q5e_comprehension = d_m5e3_05e, 
    
    # Letters
    m6s2q2a_letters = d_m5e3_06a,	
    m6s2q2b_letters = d_m5e3_06b,
    m6s2q2c_letters = d_m5e3_06c,
    m6s2q2d_letters = d_m5e3_06d,
    m6s2q2e_letters = d_m5e3_06e,
    m6s2q2f_letters = d_m5e3_06f,
    m6s2q2g_letters  = d_m5e3_06g,
    m6s2q2h_letters = d_m5e3_06h,
    
    # Words
    m6s2q3a_words = d_m5e3_07a,
    m6s2q3b_words = d_m5e3_07b,
    m6s2q3c_words= d_m5e3_07c,
    
    # Sentences
    m6s2q4a_sentence = d_m5e3_08a,
    m6s2q4b_sentence = d_m5e3_08b,
    m6s2q4c_sentence = d_m5e3_08c,	
    
    
    # Name writing
    m6s2q6a_name_writing = d_m5e3_09a,
    m6s2q6b_name_writing = d_m5e3_09b,
    
    # Print
    m6s2q7a_print = d_m5e3_10a,
    m6s2q7b_print = d_m5e3_10b,
    m6s2q7c_print = d_m5e3_10c,
    
    # Counting produce set
    m6s2q8_counting = d_m5e3_11,
    m6s2q9a_produce_set = d_m5e3_12a,
    m6s2q9b_produce_set = d_m5e3_12b,
    m6s2q9c_produce_set = d_m5e3_12c, # NOTE, it should be noted that in the ETH data there are only two while there are three for MAD
    
    # Number identical
    m6s2q10a_number_ident = d_m5e3_13a,
    m6s2q10b_number_ident = d_m5e3_13b,
    m6s2q10c_number_ident= d_m5e3_13c,
    m6s2q10d_number_ident= d_m5e3_13d,
    m6s2q10e_number_ident= d_m5e3_13e,
    m6s2q10f_number_ident= d_m5e3_13f,
    m6s2q10g_number_ident= d_m5e3_13g,
    m6s2q10h_number_ident= d_m5e3_13h,
    m6s2q10i_number_ident= d_m5e3_13i,
    m6s2q10j_number_ident= d_m5e3_13j,
    
    # Number comparison
    m6s2q11a_number_compare = d_m5e3_14a,	
    m6s2q11b_number_compare = d_m5e3_14b,
    m6s2q11c_number_compare = d_m5e3_14c,
    
    # Simple addition
    m6s2q12a_simple_add = d_m5e3_15a,
    m6s2q12b_simple_add = d_m5e3_15b,
    m6s2q12c_simple_add = d_m5e3_15c,
    
    # Backward digits
    m6s2q13a_backward_digit = d_m5e3_16c,
    m6s2q13b_backward_digit = d_m5e3_16d,
    m6s2q13c_backward_digit = d_m5e3_16e,
    m6s2q13d_backward_digit = d_m5e3_16f, # NOTE, should be noted that we do not take into account the first two obs as they are trials
    
    # Head and shoulders
    m6s2q14a_head_shoulders = d_m5e3_17a,
    m6s2q14b_head_shoulders = d_m5e3_17b,
    m6s2q14c_head_shoulders = d_m5e3_17c,
    m6s2q14d_head_shoulders = d_m5e3_17g, # NOTE, here we invert the variables' names to account for the way the survey was administered
    m6s2q14e_head_shoulders = d_m5e3_17h,
    m6s2q14f_head_shoulders = d_m5e3_18d, # NOTE, the first three are here practices that were implemented as such, so we skip them
    m6s2q14g_head_shoulders = d_m5e3_18e,
    m6s2q14h_head_shoulders = d_m5e3_18f,
    m6s2q14i_head_shoulders = d_m5e3_18g,
    m6s2q14j_head_shoulders = d_m5e3_18h,
    m6s2q14k_head_shoulders = d_m5e3_18i,
    m6s2q14l_head_shoulders= d_m5e3_18j,
    m6s2q14m_head_shoulders= d_m5e3_18k,
    m6s2q14n_head_shoulders= d_m5e3_18l,
    m6s2q14o_head_shoulders= d_m5e3_18m, # NOTE, should be noted that trials are again in the data. To ensure a correct matching between names and var, a verification was done with the M_6 DirectAssessement document.
    
    # Perspective
    m6s2q15a_perspective = d_m5e3_19a,
    m6s2q15b_perspective  = d_m5e3_19b,
    m6s2q15c_perspective = d_m5e3_19c, # NOTE, should be noted that the response provided by the students are not present in the data shared by the SDI team

    # Conflict resolution
    m6s2q16a_conflict_resol = d_m5e3_20a,
    m6s2q16b_conflict_resol = d_m5e3_20b # NOTE, should be noted that the response provided by the students are not present in the data shared by the SDI team
    
  )


# Create one copy of each dataframe that never gets touched and is carried forward to public folder
  first_grade_raw <- first_grade

# Recode ECD variables to be 1 if student got it correct and zero otherwise
  first_grade<- first_grade %>%
    mutate_at(vars(ends_with("comprehension"),
                   ends_with("letters"),
                   ends_with("words"),
                   ends_with("sentence"),
                   ends_with("nm_writing"),
                   ends_with("print"),
                   ends_with("produce_set"),
                   ends_with( "number_ident"),
                   ends_with("number_compare"),
                   ends_with("simple_add"),
                   ends_with("backward_digit"),
                   ends_with("perspective"),
                   ends_with("conflict_resol")), ~bin_var(.,1)  ) %>%
   mutate(across(ends_with("head_shoulders"), ~if_else(.x==2 | .x==1,1,0,missing=NULL))) %>%
    mutate(across(ends_with("vocabn"), ~case_when(.x==97 ~ as.numeric(NA),
                                                    .x==99 ~ 0,
                                                    .x==77 ~ 0,
                                                    (.x!=97 & .x!=99 & .x>=10) ~ 1,
                                                    (.x!=97 & .x!=99 & .x<10) ~ as.numeric(.x)/10,
                                                    is.na(.x) ~ as.numeric(NA)))) %>%
    mutate(across(ends_with("counting"), ~case_when(.x==97 ~ as.numeric(NA),
                                                      .x==99 ~ 0,
                                                      .x==77 ~ 0,
                                                      (.x!=97 & .x!=99 & .x>=30) ~ 1,
                                                      (.x!=97 & .x!=99 & .x<30) ~ as.numeric(.x)/30,
                                                      is.na(.x) ~ as.numeric(NA))))



    
    ## Modify manually the answers to questions 7 and 8 based on Vania's email from the 03/09/2021
    
   first_grade <- first_grade %>% 
     
     mutate(Q7_Q8_delete=rowSums(.[grep(x=colnames(first_grade), pattern="a_letters|b_letters|c_letters|d_letters|e_letters")], na.rm=TRUE)) %>% 
     
     mutate(
       
       #Question 7
       m6s2q7a_print = if_else(str_detect(s_ecole_code, "623|646|647|650|719|721|728|738|749|766|799") & Q7_Q8_delete ==0, NA_integer_, as.integer(m6s2q7a_print)),
       m6s2q7b_print = if_else(str_detect(s_ecole_code, "623|646|647|650|719|721|728|738|749|766|799") & Q7_Q8_delete ==0, NA_integer_,as.integer(m6s2q7b_print)),
       m6s2q7c_print = if_else(str_detect(s_ecole_code, "623|646|647|650|719|721|728|738|749|766|799") & Q7_Q8_delete ==0, NA_integer_, as.integer(m6s2q7c_print)),
       
       # Question 8
       m6s2q8_counting = if_else(str_detect(s_ecole_code, "623|646|647|650|719|721|728|738|749|766|799") & Q7_Q8_delete ==0, NA_integer_, as.integer(m6s2q8_counting))
       
       ) 
   
   ## VERIFICATION OF THE DATA RELATED TO THE EXERCICE 17 AND 18. THERE WAS A PROBLEM IN THE IMPLEMENTATION OF THE EXERCICE 17 SINCE
   # THE FIRST THREE PRACTICES WERE ADMINISTERED AS EVALUATIONS, WHICH EXPLAINS THE NAS FOR THE FIRST THREE EVALUATIONS.
     
  
     sample<- first_grade %>%
     mutate(second_stop=rowSums(.[grep(x=colnames(first_grade), pattern="a_head_shoulders|b_head_shoulders|c_head_shoulders|d_head_shoulders|e_head_shoulders")], na.rm=TRUE)) %>% 
    # mutate(second_stop=rowSums(.[grep(x=colnames(first_grade), pattern="d_m5e3_17a|d_m5e3_17b|d_m5e3_17c|d_m5e3_17g|d_m5e3_17h")], na.rm=TRUE)) %>% 
      mutate(first_stop=rowSums(.[grep(x=colnames(first_grade), pattern="a_head_shoulders|b_head_shoulders|c_head_shoulders")], na.rm=TRUE)) %>% 
     #mutate(first_stop=rowSums(.[grep(x=colnames(first_grade), pattern="d_m5e3_17a|d_m5e3_17b|d_m5e3_17c")], na.rm=TRUE)) %>% 
     mutate(first_rule_potential = if_else(first_stop == 0, 1, 0),
            second_rule_potential = if_else(second_stop == 0, 1, 0)) %>% 
     select(ends_with("potential"), ends_with("stop")) %>%
     map(table)
#------------------------------------------------------------------------------#
## 6. Constructing indicator : 1st grade level----  

  #### A. Literacy ----  
  #calculate # of literacy items
  #NOTE: grep is a tool for searching text with specified pattern.  In our case, we are looking for m8s1q, which is the prefix of literacy items
  
  
  lit_items<-colnames(first_grade[,str_detect(
    colnames(first_grade), "vocabn|comprehension|letters|words|sentence|nm_writing$|print")])
  
  first_grade$literacy_length<-length(lit_items)
  
  #calculate students lit items correct
  first_grade <- first_grade %>%
    mutate(ecd_literacy_student_knowledge=100*rowMeans(.[grep(x=colnames(first_grade), 
                                                              pattern="vocabn|comprehension|letters|words|sentence|nm_writing$|print")], na.rm=TRUE))
  
  #### B. Math ----  
  #calculate # of math items
  
  math_items<-colnames(first_grade[,str_detect(
    colnames(first_grade), "counting|produce_set|number_ident|number_compare|simple_add")])
  
  first_grade$math_length<-length(math_items)
  
  
  #calculate students math items correct
  first_grade <- first_grade %>%
    mutate(ecd_math_student_knowledge=100*rowMeans(.[grep(x=colnames(first_grade), 
                                                          pattern="counting|produce_set|number_ident|number_compare|simple_add")], na.rm=TRUE))
  
  #### C. Executive Functioning ----  
  #calculate # of Exec Function items
  
  exec_items<-colnames(first_grade[,str_detect(
    colnames(first_grade), "backward_digit|head_shoulders")])
  
  first_grade$exec_length<-length(exec_items)
  
  
  #calculate students excec items correct
  first_grade <- first_grade %>%
    mutate(ecd_exec_student_knowledge=100*rowMeans(.[grep(x=colnames(first_grade), 
                                                          pattern="backward_digit|head_shoulders")], na.rm=TRUE))
  
  #### D. Socio-Emotional ----  
  #calculate # of Exec Function items
  
  #NOTE:  Ending persepectives and conflict resolution in $ is a grep trick to make sure columns with trailing characters aren't included.  
  #This means specifically the perspetive_responses conflict_resol_responses columns, which are text and just for quality control.
  soc_items<-colnames(first_grade[,str_detect(
    colnames(first_grade), "perspective$|conflict_resol$")])
  
  first_grade$soc_length<-length(soc_items)
  
  
  #calculate students excec items correct
  first_grade <- first_grade %>%
    mutate(ecd_soc_student_knowledge=100*rowMeans(.[grep(x=colnames(first_grade), 
                                                         pattern="perspective$|conflict_resol$")], na.rm=TRUE))
  
  
  #### E. Total score ----  
  #calculate students percent correct
  first_grade <- first_grade %>%
    mutate(ecd_student_knowledge=(ecd_math_student_knowledge+ecd_literacy_student_knowledge+
                                    ecd_exec_student_knowledge + ecd_soc_student_knowledge)/4) %>%
    mutate(ecd_student_proficiency=100*as.numeric(ecd_student_knowledge>=80),
           ecd_math_student_proficiency=100*as.numeric(ecd_math_student_knowledge>=80),
           ecd_literacy_student_proficiency=100*as.numeric(ecd_literacy_student_knowledge>=80),
           ecd_exec_student_proficiency=100*as.numeric(ecd_exec_student_knowledge>=80),
           ecd_soc_student_proficiency=100*as.numeric(ecd_soc_student_knowledge>=80)
    ) 
  #save ecd data at student level anonymized
  first_grade_anon <- first_grade %>%
    select(s_ecole_code, s_date_heure_fin, ecd_student_age, ecd_student_male, 
           ecd_student_knowledge, ecd_math_student_knowledge, ecd_literacy_student_knowledge, ecd_soc_student_knowledge, ecd_exec_student_knowledge,
           ecd_student_proficiency, ecd_math_student_proficiency, ecd_literacy_student_proficiency, ecd_soc_student_proficiency, ecd_exec_student_proficiency,
           math_items, lit_items, soc_items, exec_items)
  
  
  save(first_grade_anon, 
       file = file.path(confidential_folder, "dashboard_ecd_data.RData"))
  
  #calculate % correct for literacy, math, and total
  final_indicator_data_LCAP <- first_grade_anon %>%
    #left_join(school_dta[,c('s_ecole_code',  's_enqueteur_code', 's_date_heure_fin')]) %>%
    group_by(s_ecole_code) %>%
    summarise_all( ~(if(is.numeric(.)) mean(., na.rm = TRUE) else first(.))) %>%
    select(-ends_with('length'), -ends_with('items'), -starts_with('interview'), -starts_with('enumerator'))
  
  #Breakdowns of Male/Female
  final_indicator_data_LCAP_M <- first_grade_anon %>%
    #left_join(school_dta[,c('s_ecole_code', 's_enqueteur_code', 's_date_heure_fin')]) %>%
    filter(ecd_student_male==1) %>%
    group_by(s_ecole_code) %>%
    summarise_all( ~(if(is.numeric(.)) mean(., na.rm = TRUE) else first(.))) %>%
    select(-ends_with('length'), -ends_with('items'), -starts_with('interview'), -starts_with('enumerator'))
  
  final_indicator_data_LCAP_F <- first_grade_anon %>%
    #left_join(school_dta[,c('s_ecole_code', 's_enqueteur_code', 's_date_heure_fin')]) %>%
    filter(ecd_student_male==0) %>%
    group_by(s_ecole_code) %>%
    summarise_all( ~(if(is.numeric(.)) mean(., na.rm = TRUE) else first(.))) %>%
    select(-ends_with('length'), -ends_with('items'), -starts_with('interview'), -starts_with('enumerator'))
  
  

```

## 4th grade Assessment

```{r g4}

 ## 8. Cleaning : 4th grade Level ----  
  

  
  #number missing
  fourth_grade <- fourth_grade %>%
    mutate(n_mssing_LERN=n_miss_row(.))
  
  #create indicator for % correct on student assessment
  #Note:  in the future we could incorporate irt program like mirt
  
  
  #rename a few key variables up front
  fourth_grade<- fourth_grade %>%
    mutate(student_name=m5sa1q2  ,
           student_number=m5sa1q1,
           student_age=m5sa1q3,
           student_male=bin_var(m5sa1q4,1),
    )
  
  # Create one copy of each dataframe that never gets touched and is carried forward to public folder
  fourth_grade_raw <- fourth_grade
  
  
  # create a function to score questions m8saq2 and m8saq3, in which students identify letters/words that enumerator calls out.
  # This question is tricky, because enumerators would not always follow instructions to say out loud the same letters/words
  # In order to account for this, will assume if 80% of the class has a the exact same response, then this is the letter/word called out
  # Score this so that if there is a deviation from what 80% of the class says, then it is wrong.
  call_out_scorer <- function(var, pctl) {
    1-abs(var - quantile(var, pctl, na.rm=T))
  }
  
  
  fourth_grade <- fourth_grade %>%  # Rename the variables to have them match the standard ones
   
     rename(
      # Maths
       m8sbq3a_arithmetic = m5sabq3a,
       m8sbq3b_arithmetic = m5sabq3b,
       m8sbq3c_arithmetic = m5sabq3c,
       m8sbq3d_arithmetic = m5sabq3d,
       m8sbq3e_arithmetic = m5sabq3e,
       m8sbq3f_arithmetic = m5sabq3f,
       m8sbq3g_arithmetic = m5sabq3g,
       m8sbq3h_arithmetic = m5sabq3h,
       m8sbq3i_arithmetic = m5sabq3i,
       m8sbq3j_arithmetic = m5sabq3j,
       
       m8sbq4_arithmetic = m5sabq4, # corresponds to the question S_M5E2_23 in the questionnaire about the smallest result
       m8sbq5_word_problem = m5sabq5, # corresponds to the question S_M5E2_24 about oranges
       m8sbq6_sequences = m5sabq6, # corresponds to the question S_M5E2_25 about the sequence of number
       m8sbq1_number_sense = m5sabq1, # identification of numbers indicated by the enumerator
       # NOTE - on this one we assume that 0 means that no answers were correct while 3 means all 3 numbers were correctly identified
       m8sbq2_number_sense = m5sabq2, # order number from smallest to highest

       
       m8saq2_id = m5sa2q1, #corresponds to the number of letters correctly identified 
       m8saq3_id = m5sa2q2, #corresponds to the number of words correctly identified 
       m8saq4_id = m5sa2q3, # corresponds to the number of images correctly identified (from 0 to 4)
       
       m8saq5_story = m5sa2q6a, # first question on the text
       m8saq6_story = m5sa2q6b # second question on the text
       # NOTE - the third question corresponding to the variable m5sa2q6c in the SDI questionnaire does not seem to have an equivalent in the GEPD one
       
    )
  
  ## Recoding of literacy and maths variables
  
  #recode assessment variables to be 1 if student got it correct and zero otherwise
  fourth_grade<- fourth_grade %>%
    mutate_at(vars(starts_with("m8saq5"), 
                   starts_with("m8saq6"),
                   starts_with("m8sbq2"),
                   starts_with("m8sbq3"),
                   starts_with("m8sbq4"),
                   starts_with("m8sbq5"),
                   starts_with("m8sbq6"),
    ), ~bin_var(.,1)  ) %>% #now handle the special cases
    mutate(m8saq4_id=if_else(m8saq4_id==5,4, as.numeric(m8saq4_id))) %>% #fix case where some enumerators recorded the pre-filled answer.
    # mutate(m8saq7a_gir=bin_var(m8saq7a_gir, 3),
    #        m8saq7b_gir=bin_var(m8saq7b_gir, 3),
    #        m8saq7c_gir=bin_var(m8saq7c_gir, 2),
    #        m8saq7d_gir=bin_var(m8saq7d_gir, 3),
    #        m8saq7e_gir=bin_var(m8saq7e_gir, 4),
    #        m8saq7f_gir=bin_var(m8saq7f_gir, 1),
    #        m8saq7g_gir=bin_var(m8saq7g_gir, 2),
    #        m8saq7h_gir=bin_var(m8saq7h_gir, 2),
    #        m8saq7i_gir=bin_var(m8saq7i_gir, 4),
    #        m8saq7j_gir=bin_var(m8saq7j_gir, 1),
    #        m8saq7k_gir=bin_var(m8saq7k_gir, 3)) %>% #grade lonely giraffe question
  
  ## NOTE - no question on the lonely giraffe from the SDI team
    group_by(s_ecole_code) %>%
    mutate_at(vars(starts_with("m8saq2_id"),starts_with("m8saq3_id"), starts_with("m8sbq1_number_sense")),
              ~call_out_scorer(.,0.8)) %>%
    ungroup() %>%
    # mutate(m8saq2_id=(rowSums(.[grep(x=colnames(fourth_grade), pattern="m8saq2_id")])-7)/3, #subtract some letters not assessed and make out of 3 points
    #        m8saq3_id=(rowSums(.[grep(x=colnames(fourth_grade), pattern="m8saq3_id")])-7)/3) %>%
    mutate(m8saq2_id=if_else(m8saq2_id<0,0,m8saq2_id), #subtract some letters not assessed and make out of 3 points
           m8saq3_id=if_else(m8saq3_id<0,0,m8saq3_id)) %>%
    mutate(m8saq2_id=if_else(m8saq2_id>1,1,m8saq2_id), #subtract some letters not assessed and make out of 3 points
           m8saq3_id=if_else(m8saq3_id>1,1,m8saq3_id)) %>%
    mutate(m8saq4_id=if_else(m8saq4_id!=99, m8saq4_id/4,0)) %>% 
           
           #m8saq7_word_choice=bin_var(m8saq7_word_choice,2),
           # NOTE - not found in SDI dataset
           #m8sbq1_number_sense=(rowSums(.[grep(x=colnames(assess_4th_grade_dta), pattern="m8sbq1_number_sense")])-7)/3)         
          
    mutate( 
      m8sbq1_number_sense=if_else(m8sbq1_number_sense<0,0,m8sbq1_number_sense)) %>%
    mutate(
      m8sbq1_number_sense=if_else(m8sbq1_number_sense>1,1,m8sbq1_number_sense)) %>%
    select(-starts_with("m8saq2_id__"),-starts_with("m8saq3_id__"),-starts_with("m8sbq1_number_sense__"))
  
  
  #------------------------------------------------------------------------------#
  ## 9. Constructing indicators - Fourth grade ---    
  
  ####Literacy####
  #calculate # of literacy items
  #note: grep is a tool for searching text with specified pattern.  In our case, we are looking for m8s1q, which is the prefix of literacy items
  fourth_grade$literacy_length<-length(grep(x=colnames(fourth_grade), pattern="m8saq"))
  
  lit_items<-colnames(fourth_grade[,grep(x=colnames(fourth_grade), pattern="m8saq")])
  
  
  #calculate students lit items correct
  fourth_grade <- fourth_grade %>%
    mutate(literacy_student_knowledge=100*rowMeans(.[grep(x=colnames(fourth_grade), pattern="m8saq")], na.rm=TRUE),
           literacy_student_knowledge_nogiraffe=100*rowMeans(.[c('m8saq4_id', 'm8saq5_story', 'm8saq6_story', 
                                                                 #'m8saq7_word_choice', '
                                                                 'm8saq2_id', 'm8saq3_id')], na.rm=TRUE))
  
  ####Math####
  #calculate # of math items
  fourth_grade$math_length<-length(grep(x=colnames(fourth_grade), pattern="m8sbq"))
  
  math_items<-colnames(fourth_grade[,grep(x=colnames(fourth_grade), pattern="m8sbq")])
  
  
  #calculate students math items correct
  fourth_grade <- fourth_grade %>%
    mutate(math_student_knowledge=100*rowMeans(.[grep(x=colnames(fourth_grade), pattern="m8sbq")], na.rm=TRUE))
  
  ####Total score####
  #calculate students percent correct
  fourth_grade <- fourth_grade %>%
    mutate(student_knowledge=(math_student_knowledge+literacy_student_knowledge)/2) %>%
    mutate(student_proficient=100*as.numeric(student_knowledge>=82.9), #34/41
           student_proficient_nogiraffe=100*as.numeric((literacy_student_knowledge_nogiraffe+math_student_knowledge)/2>=86.6), #12/13 points
           student_proficient_70=100*as.numeric(student_knowledge>=70),
           student_proficient_75=100*as.numeric(student_knowledge>=75),
           literacy_student_proficient_nogiraffe=100*as.numeric(literacy_student_knowledge_nogiraffe>=92), #12/13 points
           literacy_student_proficient=100*as.numeric(literacy_student_knowledge>=83.3), #20/24 points
           literacy_student_proficient_70=100*as.numeric(literacy_student_knowledge>=70),
           literacy_student_proficient_75=100*as.numeric(literacy_student_knowledge>=75),
           math_student_proficient=100*as.numeric(math_student_knowledge>=82), #14/17 points
           math_student_proficient_70=100*as.numeric(math_student_knowledge>=70),
           math_student_proficient_75=100*as.numeric(math_student_knowledge>=75))
  
  
  #save  4th grade data at student level anonymized
  assess_4th_grade_anon <- fourth_grade %>%
    select(s_ecole_code, s_eleve_code, student_age, student_male, 
           contains('student_proficient'),
           contains('student_knowledge'),
           contains('ses'),
           math_items, lit_items)
  
  
  assess_4th_grade_metadata <- makeVlist(fourth_grade)
  
  
  save(assess_4th_grade_anon, assess_4th_grade_metadata, 
       file = file.path(confidential_folder, "dashboard_4th_grade_assessment_data.RData"))
  
  
  
  
  
  #calculate % correct for literacy, math, and total
  final_indicator_data_LERN <- assess_4th_grade_anon %>%
    #left_join(school_dta[,c('interview__key', 'm8_teacher_name', 'm8_teacher_code')]) %>%
    group_by(s_ecole_code) %>%
    mutate(n_students=n()) %>%
    summarise_all( ~(if(is.numeric(.)) mean(., na.rm = TRUE) else first(.))) %>%
    select(-ends_with('length'), -ends_with('items') , -starts_with('interview'), -starts_with('enumerator'))
  
  
  #Breakdowns by Male/Female
  final_indicator_data_LERN_M <- assess_4th_grade_anon %>%
    #left_join(school_dta[,c('interview__key', 'm8_teacher_name', 'm8_teacher_code')]) %>%
    filter(student_male==1) %>%
    group_by(s_ecole_code) %>%
    mutate(n_students=n()) %>%
    summarise_all( ~(if(is.numeric(.)) mean(., na.rm = TRUE) else first(.))) %>%
    select(-ends_with('length'), -ends_with('items') , -starts_with('interview'), -starts_with('enumerator'))
  
  final_indicator_data_LERN_F <- assess_4th_grade_anon %>%
    #left_join(school_dta[,c('interview__key', 'm8_teacher_name', 'm8_teacher_code')]) %>%
    filter(student_male==0) %>%
    group_by(s_ecole_code) %>%
    mutate(n_students=n()) %>%
    summarise_all( ~(if(is.numeric(.)) mean(., na.rm = TRUE) else first(.))) %>%
    select(-ends_with('length'), -ends_with('items') , -starts_with('interview'), -starts_with('enumerator'))
  
  

```


## Teacher Absence

```{r absence}



#############################################
##### Teacher Absence ###########
#############################################

# School survey. Percent of teachers absent. Teacher is coded absent if they are: 
#   - not in school 
# - in school but absent from the class 
# - in the class but not teaching.

#create absence file containing just teacher selected for absence check
teacher_absence_dta <- teacher_roster_dta %>%
  filter(s_m2aa_09a==1)
  


#number missing
teacher_absence_dta <- teacher_absence_dta %>%
  mutate(n_mssing_EFFT=n_miss_row(.))

#rename a few key variables up front
teacher_absence_dta<- teacher_absence_dta %>%
  mutate(
         teacher_number=s_m2aa_02c ,
         teacher_position=s_m2aa_04,
         teacher_permanent=bin_var(s_m2aa_05,1),
         teacher_contract=bin_var(s_m2aa_05,2),
         #teacher_temporary=bin_var(m2saq5,3),
         teacher_volunteer=bin_var(s_m2aa_05,5),
         #teacher_ngo=bin_var(m2saq5,5)==5,
         # teacher_other=case_when(
         #   m2saq5==97 ~ m2saq5_other,
         #   m2saq5!=97 ~ "NA"
         # ),
         teacher_fulltime=bin_var(s_m2aa_06,1),
         teacher_male=bin_var(s_m2aa_03,1),
         teacher_grd1=bin_var(s_m2aa_08aa,1),
         teacher_grd2=bin_var(s_m2aa_08ab,1),
         teacher_grd3=bin_var(s_m2aa_08ac,1),
         teacher_grd4=bin_var(s_m2aa_08ad,1),
         teacher_grd5=bin_var(s_m2aa_08ae,1),
         #teacher_language=bin_var(m2saq8__1,1),
         #teacher_math=bin_var(m2saq8__2,1),
         #teacher_both_subj=bin_var(m2saq8__3,1),
         #teacher_other_subj=bin_var(m2saq8__97,1),
  )

teacher_absence_dta<- teacher_absence_dta %>%
  mutate(temp=rowSums(select(.,teacher_grd1, teacher_grd2, teacher_grd3, teacher_grd4, teacher_grd5))) %>% # here we count the number of grades present in the classroom
  mutate(multigrade=case_when(temp > 1 ~ 1,
                              TRUE ~ 0)) %>% #this variable is equal to 1 if there are several grades and zero otherwise
  select(-temp)

#  We create a unique grade variable

teacher_absence_dta <- teacher_absence_dta %>%
  mutate(grade=case_when(teacher_grd1==1 & multigrade!=1 ~ 1,
                         teacher_grd2==1 & multigrade!=1 ~ 2,
                         teacher_grd3==1 & multigrade!=1 ~ 3,
                         teacher_grd4==1 & multigrade!=1 ~ 4,
                         teacher_grd5==1 & multigrade!=1 ~ 5,
                         multigrade==1 ~ 6,
                         TRUE ~ NA_real_)) %>%
  mutate(grade=factor(grade, levels=c(1,2,3,4,5,6), labels=c("Grade 1", "Grade 2", "Grade 3", "Grade 4", "Grade 5", "Multigrade")))

label(teacher_absence_dta$grade) <- "Grade"

#list additional info that will be useful to keep in each indicator dataframe
preamble_info_absence <- c('teacher_number',
                           'teacher_position', 'teacher_permanent', 'teacher_contract', 'teacher_volunteer', 
                           'teacher_fulltime', 'teacher_male', 'teacher_grd1', 'teacher_grd2', 'teacher_grd3', 'teacher_grd4', 'teacher_grd5', 
                            's_m2ab1a_01', 's_m2ab1b_01')

#create indicator for whether each teacher was absent from school
teacher_absence_dta <- teacher_absence_dta %>%
  mutate(
    sch_absence_rate_1st=100*case_when(
      s_m2ab1a_01==5 ~ 1,
      s_m2ab1a_01!=5   ~ 0,
      is.na(s_m2ab1a_01) ~ as.numeric(NA)
    ),
    
    sch_absence_rate_2nd=100*case_when(
      s_m2ab1b_01==5 ~ 1,
      s_m2ab1b_01!=5   ~ 0,
      is.na(s_m2ab1b_01) ~ as.numeric(NA)
    ))

#create indicator for whether each teacher was absent from classroom or school
teacher_absence_dta <- teacher_absence_dta %>%
  mutate(

    
    absence_rate_1st=100*case_when(
      s_m2ab1a_01==5 | s_m2ab1a_01==3  ~ 1,
      s_m2ab1a_01==1 | s_m2ab1a_01==2 | s_m2ab1a_01==4   ~ 0,
      is.na(s_m2ab1a_01) ~ as.numeric(NA)
    ),
    
    absence_rate_2nd=100*case_when(
      s_m2ab1b_01==5 | s_m2ab1b_01==3  ~ 1,
      s_m2ab1b_01==1 | s_m2ab1b_01==2 | s_m2ab1b_01==4   ~ 0,
      is.na(s_m2ab1b_01) ~ as.numeric(NA)
    )) 
    
    
#set absence measure to be second measure
teacher_absence_dta <- teacher_absence_dta %>%
  mutate(absence_rate=absence_rate_2nd,
         sch_absence_rate=sch_absence_rate_2nd)
  
teacher_absence_final<- teacher_absence_dta %>%
  select(preamble_info, preamble_info_absence, contains('absence')) %>%
  group_by(s_ecole_code, teacher_number) %>%
  summarise_all( ~(if(is.numeric(.)) mean(., na.rm = TRUE) else first(.)))

     #plot the indicator  
 hist(teacher_absence_dta$absence_rate)  
 hist(teacher_absence_dta$sch_absence_rate)  


#Build teacher absence practice indicator
final_indicator_data_EFFT <- teacher_absence_dta %>%
  group_by(s_ecole_code) %>%
  summarise_all( ~(if(is.numeric(.)) mean(., na.rm = TRUE) else first(.)))

#Breakdowns by Male/Female
final_indicator_data_EFFT_M <- teacher_absence_dta %>%
  filter(teacher_male==1) %>%
  group_by(s_ecole_code) %>%
  summarise_all( ~(if(is.numeric(.)) mean(., na.rm = TRUE) else first(.))) 

final_indicator_data_EFFT_F <- teacher_absence_dta %>%
  filter(teacher_male==0) %>%
  group_by(s_ecole_code) %>%
  summarise_all( ~(if(is.numeric(.)) mean(., na.rm = TRUE) else first(.))) 


```

## Teacher Content Knowledge

```{r content}

# School survey. Fraction correct on teacher assessment. In the future, we will align with SDG criteria for minimum proficiency.


  #number missing
  teacher_assessment_dta <- teacher_assessment_dta_raw %>%
    mutate(n_mssing_CONT=n_miss_row(.),
           teacher_number=id12) 
    
  
  

  

  
  #drop the correct the letter and other tasks not usually featured in assessment
  teacher_assessment_dta <- teacher_assessment_dta %>% 
    select(-starts_with("t1s2_"),-starts_with("t11"),-f9_comment2)
  
  #recode assessment variables to be 1 if teacher got it correct and zero otherwise
  teacher_assessment_dta<- teacher_assessment_dta %>%
    mutate_at(vars(starts_with("t1"), starts_with("t2")), ~bin_var(.,1)  )
  
  # because two scorers were used to grade test, take the average of the scores per teacher
  teacher_assessment_dta<- teacher_assessment_dta %>%
    group_by(s_ecole_code, teacher_number) %>%
    summarise_all( ~(if(is.numeric(.)) mean(., na.rm = TRUE) else first(.))) %>%
    ungroup()
 
  
  
  ####Literacy####
  #calculate # of literacy items
  #note: grep is a tool for searching text with specified pattern.  In our case, we are looking for m5s1q, which is the prefix of literacy items
  teacher_assessment_dta$literacy_length<-length(grep(x=colnames(teacher_assessment_dta), pattern="t1"))
  
  
  lit_items<-colnames(teacher_assessment_dta[,grep(x=colnames(teacher_assessment_dta), pattern="t1")])
  
  #calculate teachers lit items correct
  teacher_assessment_dta <- teacher_assessment_dta %>%
    mutate(literacy_content_knowledge=100*rowMeans(.[grep(x=colnames(teacher_assessment_dta), pattern="t1")], na.rm=TRUE),
           correct_letter=100*rowMeans(.[grep(x=colnames(teacher_assessment_dta), pattern="t1s2_")], na.rm=TRUE),
           cloze=100*rowMeans(.[grep(x=colnames(teacher_assessment_dta), pattern="t13")], na.rm=TRUE),
           grammar=100*rowMeans(.[grep(x=colnames(teacher_assessment_dta), pattern="t12")], na.rm=TRUE),
           read_passage=100*rowMeans(.[grep(x=colnames(teacher_assessment_dta), pattern="t14")], na.rm=TRUE)) #there is no such item in the test in madagascar
  
  ####Math####
  #calculate # of math items
  teacher_assessment_dta$math_length<-length(grep(x=colnames(teacher_assessment_dta), pattern="t2"))
  
  math_items<-colnames(teacher_assessment_dta[,grep(x=colnames(teacher_assessment_dta), pattern="t2")])
  
  #calculate teachers math items correct
  teacher_assessment_dta <- teacher_assessment_dta %>%
    mutate(math_content_knowledge=100*rowMeans(.[grep(x=colnames(teacher_assessment_dta), pattern="t2")], na.rm=TRUE),
           arithmetic_number_relations=100*rowMeans(.[grep(x=colnames(teacher_assessment_dta), pattern="t21|t22|t23|t24|t25|t211|t212")], na.rm=TRUE),
           geometry=100*rowMeans(.[grep(x=colnames(teacher_assessment_dta), pattern="t26|t27|t213")], na.rm=TRUE),
           interpret_data=100*rowMeans(.[grep(x=colnames(teacher_assessment_dta), pattern="t28|t29|t210")], na.rm=TRUE))
  
  
  #do some renaming so that everything is harmonized
  teacher_assessment_dta <- teacher_assessment_dta %>%
    rename(
      #literacy (Note these are different questions than in usual dashboard because of SDI)
      m5s1q1a_grammer=t12a,
      m5s1q1b_grammer=t12b,
      m5s1q1c_grammer=t12c,
      m5s1q1d_grammer=t12d,
      m5s1q1e_grammer=t12e,
      m5s1q1f_grammer=t12f,
      m5s1q2a_cloze=t13a,
      m5s1q2b_cloze=t13b,
      m5s1q2c_cloze=t13c,
      m5s1q2d_cloze=t13d,
      m5s1q2e_cloze=t13e,
      m5s1q2f_cloze=t13f,
      m5s1q2g_cloze=t13g,
      m5s1q2h_cloze=t13h,
      m5s1q2i_cloze=t13i,
      m5s1q2j_cloze=t13j,
      m5s1q2k_cloze=t13k,
      #math (First two questions differ from traditional dashboard survey)
      m5s2q1c_number=t21c,
      m5s2q1d_number=t21d,
      m5s2q1e_number=t21e,
      m5s2q2_number=t22,
      m5s2q3_number=t23,
      m5s2q4a_number=t24a,
      m5s2q4b_number=t24b,
      m5s2q5_number=t25,
      m5s2q6_geometric=t26,
      m5s2q7_geometric=t27,
      m5s2q8_data=t28,
      m5s2q9a_data=t29a,
      m5s2q9b_data=t29b,
      m5s2q10a_data=t210a,
      m5s2q10b_data=t210b,
      m5s2q11a_number=t211a,
      m5s2q11b_number=t211b,
      m5s2q11c_number=t211c,
      m5s2q12_number=t212,
      m5s2q13a_geometric=t213a,
      m5s2q13b_geometric=t213b
    )
  
 
     #plot the indicator  
 hist(teacher_assessment_dta$literacy_content_knowledge)    
 hist(teacher_assessment_dta$math_content_knowledge)    
  
  #calculate % correct for literacy, math, and total
  final_indicator_data_CONT <- teacher_assessment_dta %>%
    group_by(s_ecole_code) %>%
    add_count(s_ecole_code,name='m5_teach_count') %>%
    mutate(content_knowledge=case_when(
      (!is.na(math_content_knowledge) & !is.na(literacy_content_knowledge)) ~ (math_content_knowledge+literacy_content_knowledge)/2,
      is.na(math_content_knowledge)  ~ literacy_content_knowledge,
      is.na(literacy_content_knowledge)  ~ math_content_knowledge)) %>%
    # mutate(content_proficiency=100*as.numeric(content_knowledge>=80),
    #        content_proficiency_70=100*as.numeric(content_knowledge>=70),
    #        content_proficiency_75=100*as.numeric(content_knowledge>=75),
    #        literacy_content_proficiency=100*as.numeric(literacy_content_knowledge>=80),
    #        literacy_content_proficiency_70=100*as.numeric(literacy_content_knowledge>=70),
    #        literacy_content_proficiency_75=100*as.numeric(literacy_content_knowledge>=75),
    #        math_content_proficiency=100*as.numeric(math_content_knowledge>=80),
    #        math_content_proficiency_70=100*as.numeric(math_content_knowledge>=70),
    #        math_content_proficiency_75=100*as.numeric(math_content_knowledge>=75)) %>%
    summarise_all( ~(if(is.numeric(.)) mean(., na.rm = TRUE) else first(.))) 
  # 
  
  #### TO DO #####
  
  
  # #Breakdown by Male/Female
  # final_indicator_data_CONT_M <- teacher_assessment_dta %>%
  #   mutate(TEACHERS__id=g4_teacher_number) %>%
  #   left_join(select(teacher_absence_dta,c('m2saq3','school_code', 'TEACHERS__id')), by=c('school_code', 'TEACHERS__id')) %>%
  #   filter(m2saq3==1) %>%
  #   group_by(school_code) %>%
  #   add_count(school_code,name='m5_teach_count') %>%
  #   mutate(content_knowledge=case_when(
  #     (!is.na(math_content_knowledge) & !is.na(literacy_content_knowledge)) ~ (math_content_knowledge+literacy_content_knowledge)/2,
  #     is.na(math_content_knowledge)  ~ literacy_content_knowledge,
  #     is.na(literacy_content_knowledge)  ~ math_content_knowledge)) %>%
  #   mutate(content_proficiency=100*as.numeric(content_knowledge>=80),
  #          content_proficiency_70=100*as.numeric(content_knowledge>=70),
  #          content_proficiency_75=100*as.numeric(content_knowledge>=75),
  #          literacy_content_proficiency=100*as.numeric(literacy_content_knowledge>=80),
  #          literacy_content_proficiency_70=100*as.numeric(literacy_content_knowledge>=70),
  #          literacy_content_proficiency_75=100*as.numeric(literacy_content_knowledge>=75),
  #          math_content_proficiency=100*as.numeric(math_content_knowledge>=80),
  #          math_content_proficiency_70=100*as.numeric(math_content_knowledge>=70),
  #          math_content_proficiency_75=100*as.numeric(math_content_knowledge>=75)) %>%
  #   summarise_all( ~(if(is.numeric(.)) mean(., na.rm = TRUE) else first(.))) %>%
  #   
  #   select(-ends_with('length'), -ends_with('items'), -starts_with('interview'), -starts_with('enumerator'),
  #          -starts_with('g4_teacher'), -c('teacher_assessment_answers__id', 'm5sb_troster', 'm5sb_tnum')) 
  # 
  # final_indicator_data_CONT_F <- teacher_assessment_dta %>%
  #   mutate(TEACHERS__id=g4_teacher_number) %>%
  #   left_join(select(teacher_absence_dta,c('m2saq3','school_code', 'TEACHERS__id')), by=c('school_code', 'TEACHERS__id')) %>%
  #   filter(m2saq3==2) %>%
  #   group_by(school_code) %>%
  #   add_count(school_code,name='m5_teach_count') %>%
  #   mutate(content_knowledge=case_when(
  #     (!is.na(math_content_knowledge) & !is.na(literacy_content_knowledge)) ~ (math_content_knowledge+literacy_content_knowledge)/2,
  #     is.na(math_content_knowledge)  ~ literacy_content_knowledge,
  #     is.na(literacy_content_knowledge)  ~ math_content_knowledge)) %>%
  #   mutate(content_proficiency=100*as.numeric(content_knowledge>=80),
  #          content_proficiency_70=100*as.numeric(content_knowledge>=70),
  #          content_proficiency_75=100*as.numeric(content_knowledge>=75),
  #          literacy_content_proficiency=100*as.numeric(literacy_content_knowledge>=80),
  #          literacy_content_proficiency_70=100*as.numeric(literacy_content_knowledge>=70),
  #          literacy_content_proficiency_75=100*as.numeric(literacy_content_knowledge>=75),
  #          math_content_proficiency=100*as.numeric(math_content_knowledge>=80),
  #          math_content_proficiency_70=100*as.numeric(math_content_knowledge>=70),
  #          math_content_proficiency_75=100*as.numeric(math_content_knowledge>=75)) %>%
  #   summarise_all( ~(if(is.numeric(.)) mean(., na.rm = TRUE) else first(.))) %>%
  #   
  #   select(-ends_with('length'), -ends_with('items'), -starts_with('interview'), -starts_with('enumerator'),
  #          -starts_with('g4_teacher'), -c('teacher_assessment_answers__id', 'm5sb_troster', 'm5sb_tnum')) 
  # 
  # 
  

```

## Inputs

```{r INPT}

#############################################
##### School Inputs ###########
#############################################

# School survey. Total score starts at 1 and points added are the sum of whether a school has: 
#   - Functional blackboard 
# - Pens, pencils, textbooks, exercise books 
# - Fraction of students in class with a desk 
# - Used ICT in class and have access to ICT in the school.


#functioning blackboard and chalk
school_data_INPT <- input_dta %>%
  mutate(blackboard_functional=case_when(
    s_m4ab_13>=1 & s_m4ab_15==1 & s_m4ab_20==1  ~ 1,
    s_m4ab_13==0 | s_m4ab_15!=1 | s_m4ab_20!=1 ~ 0)) 

#pens, pencils, textbooks, exercise books
school_data_INPT <- school_data_INPT %>%
  mutate(share_textbook=(s_m4ab_04)/(s_m4ab_01)) %>%
  mutate(share_pencil=(s_m4ab_05)/(s_m4ab_01)) %>%
  mutate(share_exbook=(s_m4ab_10)/(s_m4ab_01)) %>%
  mutate(pens_etc=case_when(
    share_pencil>=0.9 & share_exbook>=0.9  ~ 1,
    share_pencil<0.9 | share_exbook<0.9 ~ 0),
    textbooks=case_when(
      share_textbook>=0.9   ~ 1,
      share_textbook<0.9  ~ 0)) 

#basic classroom furniture (NOTE doesn't seem to have been asked)
# school_data_INPT <- school_data_INPT %>% 
#   mutate(share_desk=1-(m4scq11_inpt)/(s_m4ab_01))


#Used ICT 
school_teacher_questionnaire_INPT <- teacher_questionnaire_dta_raw %>%
  group_by(s_ecole_code) %>%
  summarise(used_ict_pct=mean(bin_var(d_m2bb2_04,1), na.rm=TRUE))


#access to ICT
school_data_INPT2 <- infrastructure_dta %>%
  mutate(access_ict=case_when(
    d_m1c_11a!=1 | d_m1c_11b!=1 ~ 0,
    (d_m1c_11a>=1 & d_m1c_11b==1 ) ~ 1,
    #(d_m1c_11a>=1 & m1sbq13_inpt==1 ) ~ 0.5, #Internet didn't work when tested
    (is.na(d_m1c_11a) | is.na(d_m1c_11b) ) ~ as.numeric(NA)
  )) %>%
  select(s_ecole_code, access_ict)



inpt_list<-c('blackboard_functional', 'pens_etc', 'textbooks',   'used_ict', 'access_ict')

final_indicator_data_INPT <- school_data_INPT %>%
  left_join(school_data_INPT2) %>%
  left_join(school_teacher_questionnaire_INPT) %>%
  mutate(used_ict=if_else((used_ict_pct>=0.5), 1,0))     %>%  #Set percentage of teachers to use ICT over 50% 
  group_by(s_ecole_code) %>%
  summarise_all(~first(na.omit(.))) %>%
  mutate(n_mssing_INPT=n_miss_row(.)) %>%
  mutate(inputs=1.2*textbooks+1.2*blackboard_functional + 1.2*pens_etc +  0.6*used_ict + 0.6*access_ict) %>%
  select( -starts_with('interview'), -starts_with('enumerator'))


hist(final_indicator_data_INPT$inputs)
hist(final_indicator_data_INPT$textbooks)
hist(final_indicator_data_INPT$blackboard_functional)
hist(final_indicator_data_INPT$pens_etc)
hist(final_indicator_data_INPT$used_ict)
hist(final_indicator_data_INPT$access_ict)


```


## Infrastructure

```{r infr}

  # School survey. Total score starts at 1 and points added are the sum of whether a school has: 
  #   - Access to adequate drinking water 
  # -Functional toilets.  Extra points available if are separate for boys/girls, private, useable, and have hand washing facilities 
  # - Electricity  in the classroom 
  # - Internet
  # - School is accessible for those with disabilities (road access, a school ramp for wheelchairs, an entrance wide enough for wheelchairs, ramps to classrooms where needed, accessible toilets, and disability screening for seeing, hearing, and learning disabilities with partial credit for having 1 or 2 or the 3).)
  
  ## Create the metadata for the infrastructure
  infrastructure_metadata <- makeVlist(infrastructure_dta)

  
  #drinking water
  infrastructure_dta <- infrastructure_dta %>%
    #
    mutate(drinking_water=if_else(d_m12c_08a==1, 1,0, as.numeric(NA) ))
  
  #functioning toilets
  infrastructure_dta <- infrastructure_dta %>%
    mutate(toilet_exists=if_else(s_m1c_01==1 ,1,0),
           toilet_separate=if_else((s_m1c_02==1 | s_m1_c01a==3),1,0),#by separate here we mean between boys and girls as well as teachers and students
           toilet_private=as.numeric(s_m1c_03==1), #here it means having a door on the toilets for instance
           toilet_usable=as.numeric(s_m1c_04==1),
           toilet_handwashing=as.numeric(s_m1c_07==1)
           #toilet_soap=as.numeric(m1sbq8_infr)
           ) %>% # This one is included in the one above
    mutate(functioning_toilet=case_when(
      # exist, separate for boys/girls, clean, private, useable,  handwashing available
      toilet_exists==1 & toilet_usable==1 & toilet_separate==1  & toilet_private==1  & toilet_handwashing==1 ~ 1,
      toilet_exists==0 | toilet_usable==0 | toilet_separate==0  | toilet_private==0  | toilet_handwashing==0 ~ 0
    )) 
  
  #visibility ## ATTENTION TO MODIFY
  inf_input_dta <- input_dta %>%
    left_join(infrastructure_dta %>% select(s_ecole_code, s_date_heure_fin, d_m1c_11c) %>% rename(s_date_heure_fin_f09=s_date_heure_fin)) %>% 
    select(s_ecole_code, s_date_heure_fin_f09, s_m4ab_15, s_m4ab_21, d_m1c_11c) %>%
    mutate(visibility=case_when(
      s_m4ab_15==1 &  s_m4ab_21==1  ~ 1,
      s_m4ab_15==2 & s_m4ab_21==1 ~ 0)) 
  
  #electricity
  infrastructure_dta <- infrastructure_dta %>%
    mutate(class_electricity=if_else(d_m1c_10==1,1,0)) 
  
  
  #accessibility for people with disabilities
  final_indicator_data_INFR <- infrastructure_dta %>%
    filter(s_type_ecole == 3) %>% # schools from sample
    group_by(s_ecole_code) %>%
    summarise_all(~first(na.omit(.))) %>%
    mutate(
      disab_road_access=if_else((s_m1c_09 == 1 | s_m1c_09 == 2 | s_m1c_09 == 3), 1, 0), #here the walking, boat and other were considered as no road access
      
    disab_school_ramp=case_when(
        d_m1c_15a==0 ~ 1,
        (d_m1c_15b	==1 & d_m1c_15a	==1) ~ 1,
        (d_m1c_15b	==2 & d_m1c_15a	==1) ~ 0,
        is.na(d_m1c_15b) ~ as.numeric(NA)),
  
      disab_school_entr=if_else(d_m1c_15c ==1, 1, 0),
  
      disab_class_ramp=case_when(
        d_m1c_15b==0 ~ 1,
        (d_m1c_15b==1 & d_m1c_15b==1) ~ 1,
        (d_m1c_15b==2 & d_m1c_15b==1) ~ 0,
        is.na(d_m1c_15b) ~ as.numeric(NA)),
  
     ##  disab_class_entr -THIS ONE DOES NOT EXIST IN THE MADAGASCAR DATA
  
      disab_screening=rowMeans(select(.,d_m1c_13_01,d_m1c_13_02,d_m1c_13_03), na.rm = TRUE),
  
      #sum up all components for overall disability accessibility score
      disability_accessibility=(disab_road_access+disab_school_ramp+disab_school_entr+
                                  disab_class_ramp+
                                  #disab_class_entr+ # DOES NOT EXIST HERE
                                  if_else(s_m1c_01==2,0,as.numeric(d_m1c_06a==1))+
                                  disab_screening)/6
    ) %>%
    mutate(internet=case_when(
      d_m1c_11c==1  ~ 1,
      d_m1c_11c==2   ~ 0,
      is.na(as.numeric(d_m1c_11c)) ~ 0,
      TRUE ~ 0) ) # 
  
  
  infr_list<-c('drinking_water', 'functioning_toilet', 'internet',  'class_electricity', 'disability_accessibility')
  
  final_indicator_data_INFR <- final_indicator_data_INFR %>%
    mutate(n_mssing_INFR=n_miss_row(.)) %>%
    mutate(infrastructure=(drinking_water+ functioning_toilet+ internet + class_electricity+ disability_accessibility)) %>%
    select(s_ecole_code, s_region_code, s_urbain, s_cisco_code, s_commune_code, s_ecole_name, s_zap_name, s_date_visite,s_zap_code,
           s_enqueteur_code, s_type_ecole, infrastructure, everything()) %>%
    select( -starts_with('interview'), -starts_with('enumerator'))  

  #plot the data
  hist(final_indicator_data_INFR$infrastructure)
  hist(final_indicator_data_INFR$functioning_toilet)
  hist(final_indicator_data_INFR$toilet_exists)
  hist(final_indicator_data_INFR$toilet_usable)
  hist(final_indicator_data_INFR$toilet_separate)
  hist(final_indicator_data_INFR$toilet_private)
  hist(final_indicator_data_INFR$toilet_handwashing)
  
  hist(final_indicator_data_INFR$internet)
  hist(final_indicator_data_INFR$class_electricity)
  hist(final_indicator_data_INFR$disability_accessibility)

    
```


## School Operational Management

```{r managementclean}


  
  ## Create the metadata for the infrastructure
  management_metadata <- makeVlist(management_dta)
  
  ## Rename the variable in accordance with the matrix
  management_dta <- management_dta %>% 
    rename(
      
      # Vignette 1
      m7sbq1_opmn = d_m3ab_01, # do the school fix the problem
      m7sbq2_opmn= d_m3ab_02, # how
      m7sbq3_opmn = d_m3ab_03, # within one year
      m7sbq4_opmn = d_m3ab_04, # who if not the school 
      m7sbq5_opmn = d_m3ab_05, # still within a year?
      
      # Vignette 2
      m7scq1_opmn = d_m3ac_01, #responsible to provide textbook
      m7scq2_opmn = d_m3ac_02, 
      m7scq3_opmn =d_m3ac_03,
      m7scq4_opmn = d_m3ac_04,
      
      
      # Goal setting
      m7sdq1_pman = d_m3ad_01,
      m7sdq2_pman = d_m3ad_02,
      m7sdq4_pman = d_m3ad_04,
      m7sdq5_pman = d_m3ad_05,
      
      # Problem solving 
      m7seq1_pman = d_m3ae_01, 
      m7seq3_pman = d_m3ae_03,
      
      
      # Principal knowledge of the school
      m7sfq1_pknw = d_m3af_02,
      m7sfq2_pknw = d_m3af_03,
      m7sfq3_pknw = d_m3af_04, 
      m7sfq4_pknw = d_m3af_05,
      m7sfq5_pknw = d_m3af_06,
      m7sfq6_pknw = d_m3af_07,
      m7sfq7_pknw = d_m3af_08,
      m7sfq10_pknw = d_m3af_1103,
      m7sfq11_pknw = d_m3af_12,
      m7sfq12_pknw = d_m3af_13, 
      m7sfq13_pknw = d_m3af_14, 
      m7sfq14_pknw = d_m3af_15, 
      
      ## NOTE - the questions like m7sfq15(a)_pknw about the policy knowledge of the principal appear to be missing
      
      # Recruitement, training and evaluation
      m7sgq2_ssld = d_m3ag_02 ,
      m7sgq3_ssup = d_m3ag_03,
      m7sgq5_ssup = d_m3ag_05,
      m7sgq7_ssup = d_m3ag_07,
      m7sgq8_sevl = d_m3ag_08,
      m7sgq9_sevl = d_m3ag_09,
      
      #Job satisfaction
      m7shq1_satt = d_m3ah_01, #satisfy 
      m7shq2_satt = d_m3ah_02 # public net salary
      
    ) %>% 

    # clean variable names in wide format
    setNames(tolower(gsub("d_m3ac_05","m7scq5_opmn",names(.)))) %>% 
    setNames(tolower(gsub("d_m3ad_03","m7sdq3_pman",names(.)))) %>% # d_m3ad_03 01 to 05
    setNames(tolower(gsub("d_m3ae_02","m7seq2_pman",names(.)))) %>% # d_m3ae_02a to f
    setNames(tolower(gsub("d_m3ag_01","m7sgq1_ssld",names(.)))) %>% #d_m3ag_01 01 06 08 97
    setNames(tolower(gsub("d_m3ag_04","m7sgq4_ssup",names(.)))) %>% # d_m3ag_04 01  to 03 99
    setNames(tolower(gsub("d_m3ag_06","m7sgq6_ssup",names(.)))) %>% #d_m3ag_06a to t
    setNames(tolower(gsub("d_m3ag_10","m7sgq10_sevl",names(.)))) %>% # d_m3ag_10 01 to 09 99
    setNames(tolower(gsub("d_m3ag_11","m7sgq11_sevl",names(.)))) %>% # d_m3ag_11 01 06 99 98
    setNames(tolower(gsub("d_m3ag_12","m7sgq12_sevl",names(.)))) # d_m3ag_12 01 05 99 98
  
  

```


```{r OPMN}
 ############################################
  ##### School Operational Management ###########
  #############################################
  
  #Principals/head teachers are given two vignettes:
  #- One on solving the problem of a hypothetical leaky roof 
  #- One on solving a problem of inadequate numbers of textbooks.  
  #Each vignette is worth 2 points.  
  #
  #The indicator will measure two things: presence of functions and quality of functions. In each vignette: 
  #- 0.5 points are awarded for someone specific having the responsibility to fix 
  #- 0.5 point is awarded if the school can fully fund the repair, 0.25 points is awarded if the school must get partial help from the community, and 0 points are awarded if the full cost must be born by the community 
  #- 1 point is awarded if the problem is fully resolved in a timely manner, with partial credit given if problem can only be partly resolved.
  

  
  #############################################
  ##### Problem solving - vignettes ###########
  #############################################  
  final_indicator_data_OPMN <- management_dta %>%
    group_by(s_ecole_code) %>%
    summarise_all(~first(na.omit(.))) %>%
    mutate(
      vignette_1_resp=if_else((m7sbq1_opmn==0 & (m7sbq4_opmn==4 | m7sbq4_opmn==98)), 0, 0.5),
      vignette_1_finance=case_when(
        m7sbq2_opmn==1 ~ 0.5,
        (m7sbq2_opmn==2 | m7sbq2_opmn==97) ~ 0.25,
        m7sbq2_opmn==3 ~ 0,
        m7sbq1_opmn==0 & !(m7sbq4_opmn==4 | m7sbq4_opmn==98) ~ 0.5),
      vignette_1_address=if_else(m7sbq1_opmn==1, case_when(
        m7sbq3_opmn==1 ~ 0,
        (m7sbq3_opmn==2 | m7sbq3_opmn==97) ~ .5,
        m7sbq3_opmn==3 ~ 1),
        case_when(
          m7sbq5_opmn==1 ~ 0,
          m7sbq5_opmn==2 ~ .5,
          m7sbq5_opmn==3 ~ 1))) %>% 
    #give total score for this vignette
    mutate(vignette_1=vignette_1_resp+vignette_1_finance+vignette_1_address) %>% 
    mutate(vignette_2_resp=if_else(m7scq1_opmn==98, 0, 0.5), # no one responsible that is known
           vignette_2_finance=if_else(m7scq1_opmn==1,0,0.5),      #parents are forced to buy textbooks          
           #give partial credit based on how quickly it will be solved <1 month, 1-3, 3-6, 6-12, >1 yr
           vignette_2_address=case_when(
             m7scq2_opmn==1 ~ 1,
             m7scq2_opmn==2 ~ .75,
             m7scq2_opmn==3 ~ .5,
             m7scq2_opmn==4 ~ .25,
             (m7scq2_opmn==5 |m7scq2_opmn==98) ~ 0)) %>%
    mutate(vignette_2=vignette_2_resp+vignette_2_finance+vignette_2_address) %>%          #sum all components for overall score
    mutate(operational_management=1+vignette_1+vignette_2 )

  
    
  
  final_indicator_data_OPMN <- final_indicator_data_OPMN %>%
    mutate(n_mssing_OPMN=n_miss_row(.))  %>%
    select( -starts_with('interview'), -starts_with('enumerator'))  
  
 
     #plot the indicator  
 hist(final_indicator_data_OPMN$operational_management)    
 hist(final_indicator_data_OPMN$vignette_1)     
 hist(final_indicator_data_OPMN$vignette_2)     
  
   #Breakdowns by Male/Female
  # final_indicator_data_OPMN_M <- final_indicator_data_OPMN %>%
  #   filter(m7saq10==1) %>%
  #   mutate(n_mssing_OPMN=n_miss_row(.))  %>%
  #   select( -starts_with('interview'), -starts_with('enumerator'))  
  # 
  # final_indicator_data_OPMN_F <- final_indicator_data_OPMN %>%
  #   filter(m7saq10==2) %>%
  #   mutate(n_mssing_OPMN=n_miss_row(.))  %>%
  #   select( -starts_with('interview'), -starts_with('enumerator'))  
  
 
```

## School Principal School Knowledge 

```{r}


  
  #############################################
  ##### School Principal School Knowledge ###########
  #############################################
  # The aim of this indicator is to measure the extent to which principals have the knowledge about their own schools that is necessary for them to be effective managers. A score from 1 to 5 capturing the extent to which the principal is familiar with certain key aspects of the day-to-day workings of the school (in schools that have principals). Principal receives points in the following way: 
  #   - 5 points. Principal gets all 90-100% of questions within accuracy bounds (defined below). 
  # - 4 points. Principal gets 80-90% of question within accuracy bounds. 
  # - 3 points. Principal gets 70-80% of question within accuracy bounds. 
  # - 2 points. Principal gets 60-70% of question within accuracy bounds. 
  # - 1 points. Principal gets under 60% of question within accuracy bounds. 
  # 
  # Accuracy bounds for each question. 
  # Within 1 teacher/student for each of the following: 
  #   - Out of these XX teachers, how many do you think would be able to correctly add triple digit numbers (i.e. 343+215+127)? 
  #   - Out of these XX teachers, how many do you think would be able to correctly to multiply double digit numbers (i.e. 37 x 13)? 
  #   - Out of these XX teachers, how many do you think would be able to complete sentences with the correct world (i.e. The accident _____ (see, saw, had seen, was seen) by three people)? 
  #   - Any of these XX teachers have less than 3 years of experience? 
  #   - Out of these XX teachers, which ones have less than 3 years of experience as a teacher? 
  # Within 3 teacher/student for each of the following: 
  #   - In the selected 4th grade classroom, how many of the pupils have the relevant textbooks? 
  #   Must identify whether or not blackboard was working in a selected 4th grade classroom.
  
  #------------------------------------------------------------------------------#


#first create a database containing actual values for each question for the principal
pknw_actual_cont <- final_indicator_data_CONT %>%
  select(s_ecole_code, m5_teach_count, m5_teach_count, m5s2q1c_number, m5s2q1e_number, m5s1q1f_grammer )

pknw_actual_exper <- teacher_questionnaire_dta_raw %>%
  add_count(s_ecole_code,name='m7_teach_count_pknw') %>%
  select(s_ecole_code, s_m2ba1_05, m7_teach_count_pknw ) %>%
  mutate(experience=(2021-s_m2ba1_05)) %>%
  group_by(s_ecole_code) %>%
  summarise(teacher_count_experience_less3=sum(experience <3),
            m7_teach_count_pknw=first(m7_teach_count_pknw))

#principal answers
pknw_guess_exper <- read_dta(paste0(download_folder, '/12-M3A_D_M3AF_10_EXP.dta')) %>%
  group_by(s_ecole_code) %>%
  summarise(exper_guess=sum(d_m3af_10_exp==1, na.rm=T))

pknw_actual_school_inpts <- final_indicator_data_INPT %>%
  select(s_ecole_code, blackboard_functional, s_m4ab_04, s_m4ab_01)

pknw_actual_combined <- pknw_actual_school_inpts %>%
  left_join(pknw_actual_cont) %>%
  left_join(pknw_actual_exper) %>%
  mutate(teacher_count_experience_less3=if_else(is.na(teacher_count_experience_less3), as.numeric(0), as.numeric(teacher_count_experience_less3)),
         m5s2q1c_number=m5s2q1c_number*m5_teach_count,
         m5s2q1e_number=m5s2q1e_number*m5_teach_count,
         m5s1q1f_grammer=m5s1q1f_grammer*m5_teach_count)


#create function to compare principal responses to actual
# if principal is within 1 student/teacher, then score as 1, 0 otherwise
principal_scorer <- function(var_guess, var_actual, var_total, margin1, margin2) {
  if_else(
    ((1-abs(var_guess-var_actual)/var_total>= as.numeric(margin1)) | (var_guess-var_actual <= as.numeric(margin2))),
    1,
    0)
}



final_indicator_data_PKNW <- management_dta %>%
  mutate(n_mssing_PKNW=n_miss_row(.))  %>%
  select( -starts_with('interview'), -starts_with('enumerator'))  %>%
  left_join(pknw_actual_combined) %>%
  left_join(pknw_guess_exper) %>%
  mutate(add_triple_digit_pknw=principal_scorer(m7sfq5_pknw, m5s2q1c_number, m7_teach_count_pknw,0.8,1),
         multiply_double_digit_pknw=principal_scorer(m7sfq6_pknw, m5s2q1e_number, m7_teach_count_pknw,0.8,1),
         complete_sentence_pknw=principal_scorer(m7sfq7_pknw, m5s1q1f_grammer, m7_teach_count_pknw,0.8,1),
         experience_pknw=principal_scorer(exper_guess, teacher_count_experience_less3, m7_teach_count_pknw,0.8,1),
         textbooks_pknw=principal_scorer(m7sfq10_pknw, s_m4ab_04, s_m4ab_01,0.8,3),
         blackboard_pknw=if_else(m7sfq11_pknw==blackboard_functional,1,0)) %>%
  mutate(principal_knowledge_avg=rowMeans(select(.,add_triple_digit_pknw, multiply_double_digit_pknw, complete_sentence_pknw, experience_pknw, textbooks_pknw, blackboard_pknw), na.rm=TRUE)) %>%
  mutate(principal_knowledge_score=case_when(
    principal_knowledge_avg ==1 ~ 5,
    (principal_knowledge_avg >=5/6 & principal_knowledge_avg<1) ~ 4,
    (principal_knowledge_avg >=4/6 & principal_knowledge_avg<5/6) ~ 3,
    (principal_knowledge_avg >=3/6 & principal_knowledge_avg<4/6) ~ 2,
    (principal_knowledge_avg <3/6 ) ~ 1  )
  ) 

#plot data
hist(final_indicator_data_PKNW$principal_knowledge_score)
hist(final_indicator_data_PKNW$principal_knowledge_avg)
hist(final_indicator_data_PKNW$add_triple_digit_pknw)
hist(final_indicator_data_PKNW$multiply_double_digit_pknw)
hist(final_indicator_data_PKNW$complete_sentence_pknw)
hist(final_indicator_data_PKNW$experience_pknw)
hist(final_indicator_data_PKNW$textbooks_pknw)
hist(final_indicator_data_PKNW$blackboard_pknw)



                              # #Breakdowns by Male/Female
                              # final_indicator_data_PKNW_M <- final_indicator_data_PKNW %>%
                              #   filter(m7saq10==1) %>%
                              #   select( -starts_with('interview'), -starts_with('enumerator'))  
                              # 
                              # final_indicator_data_PKNW_F <- final_indicator_data_PKNW %>%
                              #   filter(m7saq10==2) %>%
                              #   select( -starts_with('interview'), -starts_with('enumerator'))  
```



```{r}

  
  #############################################
  ##### School Principal Management Skills ###########
  #############################################
  
  
  # Score of 1-5 based on sum of following: 
  #   - 1 Point. School Goals Exists 
  # - 1 Point. School goals are clear to school director, teachers, students, parents, and other members of community (partial credit available) 
  # - 1 Point. Specific goals related to improving student achievement ( improving test scores, improving pass rates, reducing drop out, reducing absenteeism, improving pedagogy, more resources for infrastructure, more resources for inputs) 
  # - 1 Point. School has defined system to measure goals (partial credit available)
  
  #Create variables for whether school goals exists, are clear, are relevant to learning, and are measured in an appropriate way.
  
  
  final_indicator_data_PMAN <- management_dta %>%
    mutate(across(c(contains("m7sdq3_pman"),contains("m7seq2_pman"),contains("d_m3ad")), ~bin_var(.,1))) %>%
    mutate(sch_goals_exist=bin_var(m7sdq1_pman,1),
           sch_goals_clear=if_else(m7sdq1_pman==1, 
                                   rowMeans(select(.,m7sdq3_pman01, m7sdq3_pman02, m7sdq3_pman03, m7sdq3_pman04, m7sdq3_pman05), na.rm=TRUE),
                                   0) ,
           sch_goals_relevant_total=rowSums(select(.,d_m3ad_04a, d_m3ad_04b, d_m3ad_04d, d_m3ad_04e, d_m3ad_04f, d_m3ad_04g, d_m3ad_04h, d_m3ad_04i, d_m3ad_04j), na.rm=TRUE),
           sch_goals_relevant=if_else(m7sdq1_pman==1, 
                                      case_when(
                                        (sch_goals_relevant_total > 0) ~ 1,
                                        (sch_goals_relevant_total == 0) ~ 0),
                                      0),
           sch_goals_measured=if_else((m7sdq1_pman==1), 
                                      case_when(
                                        (m7sdq5_pman==1) ~ 0,
                                        (m7sdq5_pman==2 | m7sdq5_pman==97 ) ~ 0.5,
                                        (m7sdq5_pman==3) ~ 1),
                                      0)) %>%
    mutate(goal_setting=1+sch_goals_exist+sch_goals_clear+sch_goals_relevant+sch_goals_measured) %>%
    
    # Now for problem solving
    mutate(
      problem_solving_proactive=case_when(
        (m7seq1_pman==4 ) ~ 1,
        (m7seq1_pman==2 | m7seq1_pman==3 ) ~ 0.5,
        (m7seq1_pman==1 | m7seq1_pman==98 ) ~ 0,
        TRUE ~ 0),
      problem_solving_info_collect=(m7seq2_pmana+m7seq2_pmanb + m7seq2_pmanc + m7seq2_pmand)/4,
      problem_solving_stomach=case_when(
        (m7seq3_pman==4 ) ~ 1,
        (m7seq3_pman==3 ) ~ 0.5,
        (m7seq3_pman==1 | m7seq3_pman==2 | m7seq3_pman==98 ) ~ 0.25,
        TRUE ~ 0)
      
    ) %>%
    mutate(problem_solving=1+(4/3)*problem_solving_proactive+(4/3)*problem_solving_info_collect+(4/3)*problem_solving_stomach) %>%
    
    mutate(principal_management=(goal_setting+problem_solving)/2)
  
hist(final_indicator_data_PMAN$principal_management)
hist(final_indicator_data_PMAN$problem_solving)
hist(final_indicator_data_PMAN$problem_solving_proactive)
hist(final_indicator_data_PMAN$problem_solving_info_collect)
hist(final_indicator_data_PMAN$problem_solving_stomach)
hist(final_indicator_data_PMAN$goal_setting)
hist(final_indicator_data_PMAN$sch_goals_exist)
hist(final_indicator_data_PMAN$sch_goals_clear)
hist(final_indicator_data_PMAN$sch_goals_relevant)  
hist(final_indicator_data_PMAN$sch_goals_measured)  

    
```




# Policy Indicators

## Teacher Teaching Attraction

```{r tatt}

 #############################################
  ##### Teacher Teaching Attraction ###########
  #############################################
  
  # In the school survey, a number of De Facto questions on teacher attraction are asked. 0.8 points is awarded for each of the following: 
  #   - 0.8 Points. Teacher satisfied with job 
  # - 0.8 Points. Teacher satisfied with status in community 
  # - 0.8 Points. Would better teachers be promoted faster? 
  #   - 0.8 Points. Do teachers receive bonuses? 
  #   - 0.8 Points. One minus the fraction of months in past year with a salary delay.
  
  
  #create function to clean teacher attitudes questions.  Need to reverse the order for scoring for some questions.  
  #Should have thought about this, when programming in Survey Solutions and scale 1-5.
  
  attitude_fun  <- function(x) {
    case_when(
      x==98 ~ as.numeric(NA),
      TRUE ~ x
    )
  }
  
  attitude_fun_rev  <- function(x) {
    case_when(
      x==98 ~ as.numeric(NA),
      x==1 ~ 5,
      x==2 ~ 4,
      x==3 ~ 3,
      x==4 ~ 2,
      x==5 ~ 1
    )
  }
  
  
  teacher_questionnaire_dta <- teacher_questionnaire_dta_raw %>%
    mutate(teacher_satisfied_job=attitude_fun_rev(d_m2be_01)/5,
           teacher_satisfied_status=attitude_fun_rev(d_m2be_02)/5,
           better_teachers_promoted=bin_var(d_m2be_03,1),
           teacher_bonus=bin_var(d_m2be_04,1),
           teacher_bonus_attend=if_else(d_m2be_04==1,
                                        bin_var(d_m2be_05a,1),
                                        0),
           teacher_bonus_student_perform=if_else(d_m2be_04==1,
                                                 bin_var(d_m2be_05b,1),
                                                 0),
           teacher_bonus_extra_duty=if_else(d_m2be_04==1,
                                            bin_var(d_m2be_05c,1),
                                            0),
           teacher_bonus_hard_staff=if_else(d_m2be_04==1,
                                            bin_var(d_m2be_05d,1),
                                            0),
           # teacher_bonus_subj_shortages=if_else(d_m2be_04==1,
           #                                      bin_var(d_m2be_05e,1),
           #                                      0),
           teacher_bonus_add_qualif=if_else(d_m2be_04==1,
                                            bin_var(d_m2be_05e,1),
                                            0),
           teacher_bonus_school_perform=if_else(d_m2be_04==1,
                                                bin_var(d_m2be_05f,1),
                                                0),
           teacher_bonus_other=if_else(d_m2be_04==1,
                                       if_else(d_m2be_05g==1,d_m2be_05au,"NA"),
                                       "NA"),
           salary_delays=s_m2bb1_01) %>%
    mutate(salary_delays=if_else(salary_delays>12,12,salary_delays)) %>%
    mutate(teacher_attraction=1+0.8*teacher_satisfied_job+.8*teacher_satisfied_status+.8*better_teachers_promoted+.8*teacher_bonus+.8*(1-salary_delays/12))

   #plot the indicator  
 hist(teacher_questionnaire_dta$teacher_attraction)    
  
  final_indicator_data_TATT <- teacher_questionnaire_dta %>%
    mutate(n_mssing_TATT=n_miss_row(.)) %>%
    group_by(s_ecole_code) %>%
    summarise_all( ~(if(is.numeric(.)) mean(., na.rm = TRUE) else first(.))) 
  
  
```

## Teacher Teaching Selection and Deployment

```{r tsdp}
  
  #############################################
  ##### Teacher Teaching Selection and Deployment ###########
  #############################################
  
  # School Survey. The De Facto portion of the Teacher Selection and Deployment Indicator considers two issues: how teachers are selected into the profession and how teachers are assigned to positions (transferred) once in the profession. Research shows that degrees and years of experience explanin little variation in teacher quality, so more points are assigned for systems that also base hiring on content knowledge or pedagogical skill. 2 points are available for the way teachers are selected and 2 points are available for deployment. 
  # 
  # Selection 
  # - 0 Points. None of the below 
  # - 1 point. Teachers selected based on completion of coursework, educational qualifications, graduating from tertiary program (including specialized programs), selected based on experience 
  # - 2 points. Teacher recruited based on passing written content knowledge test, passed interview stage assessment, passed an assessment conducted by supervisor based on practical experience, conduct during mockup class. 
  # 
  # Deployment 
  # - 0 Points. None of the below 
  # - 1 point. Teachers deployed based on years of experience or job title hierarchy 
  # - 2 points. Teacher deployed based on performance assessed by school authority, colleagues, or external evaluator, results of interview.
  
  
  teacher_questionnaire_dta <- teacher_questionnaire_dta %>%
    mutate(
      teacher_selection=case_when(
        (d_m2bd_01c==1 | d_m2bd_01d==1 | d_m2bd_01f==1 | d_m2bd_01g==1 )  ~ 2,
        (d_m2bd_01a==1 | d_m2bd_01b==1 | d_m2bd_01e==1) ~ 1,
        (d_m2bd_01a!=1 & d_m2bd_01b!=1 & d_m2bd_01c!=1 & d_m2bd_01d!=1 & d_m2bd_01e!=1 & d_m2bd_01f!=1 & d_m2bd_01g!=1 ) ~ 0
      ),
      teacher_deployment=case_when(
        (d_m2be_06bb==1 | d_m2be_06bc==1 | d_m2be_06bd==1  )  ~ 2,
        (d_m2be_06ba==1 | d_m2be_06bf==1) ~ 1,
        ((d_m2be_06ba!=1 & d_m2be_06bb!=1 & d_m2be_06bc!=1 & d_m2be_06bd!=1 | d_m2be_06bf!=1) ) ~ 0
        
      )
    ) %>%
    mutate(teacher_selection_deployment=1+teacher_selection+teacher_deployment)
  
 #plot the indicator  
 hist(teacher_questionnaire_dta$teacher_selection_deployment)   
  
  final_indicator_data_TSDP <- teacher_questionnaire_dta %>%  
    mutate(n_mssing_TSDP=n_miss_row(.)) %>%
    group_by(s_ecole_code) %>%
    summarise_all( ~(if(is.numeric(.)) mean(., na.rm = TRUE) else first(.))) 
  
  
```

## Teacher Teaching Support

```{r tsup}
  #############################################
  ##### Teacher Teaching Support ###########
  #############################################
  
  
  # School survey. Our teaching support indicator asks teachers about participation and the experience with several types of formal/informal training: 
  #   
  #   Pre-Service (Induction) Training: 
  #   - 0.5 Points. Had a pre-service training 
  # - 0.5 Points. Teacher reported receiving usable skills from training 
  # 
  # Teacher practicum (teach a class with supervision) 
  # - 0.5 Points. Teacher participated in a practicum 
  # - 0.5 Points. Practicum lasted more than 3 months and teacher spent more than one hour per day teaching to students. 
  # 
  # In-Service Training: 
  #   - 0.5 Points. Had an in-service training 
  # - 0.25 Points. In-service training lasted more than 2 total days 
  # - 0.125 Points. More than 25% of the in-service training was done in the classroom. 
  # - 0.125 Points. More than 50% of the in-service training was done in the classroom. 
  # 
  # Opportunities for teachers to come together to share ways of improving teaching: 
  #   - 1 Point if such opportunities exist.
  

  teacher_questionnaire_dta <- teacher_questionnaire_dta %>%
    mutate(opportunities_teachers_share=bin_var(d_m2bd_14,1),
           pre_training_exists=bin_var(d_m2bd_03,1)/2,
           pre_training_useful=if_else(d_m2bd_03==1,
                                       bin_var(d_m2bd_04,1),
                                       0)/2,
           pre_training_practicum=bin_var(d_m2bd_06,1)/2,
           pre_training_practicum_lngth=case_when(
             (d_m2bd_06==1 & (d_m2bd_07m>=3 | d_m2bd_07a>=1) & d_m2bd_08>=1) ~  0.5,
             (d_m2bd_06==1 & ((d_m2bd_07m<3 & d_m2bd_07a<1) | d_m2bd_08<1))  ~ 0,
             d_m2bd_06==2 ~ 0,
             TRUE ~ 0),
           in_service_exists=bin_var(d_m2bd_09,1),
           in_servce_lngth=case_when(
             (d_m2bd_09==1 & d_m2bd_10>2 ) ~ 1,
             (d_m2bd_09==1 & d_m2bd_10<=2) ~ 0,
             d_m2bd_09==0 ~ 0,
             TRUE ~ 0
           ),
           in_service_classroom=case_when(
             (d_m2bd_09==1 & d_m2bd_13>=3)  ~ 1,
             (d_m2bd_09==1 & d_m2bd_13==2)  ~ 0.5,
             (d_m2bd_09==1 & d_m2bd_13==1)  ~ 0,
             d_m2bd_09==0 ~ 0,
             TRUE ~ 0
           )
    ) %>%
    mutate(pre_service=pre_training_exists+pre_training_useful,
           practicum=pre_training_practicum+pre_training_practicum_lngth,
           in_service=0.5*in_service_exists+0.25*in_servce_lngth+0.25*in_service_classroom) %>%
    mutate(teacher_support=1+pre_service+practicum+in_service+opportunities_teachers_share) 
  # mutate(teacher_support=if_else(teacher_support>5,5,teacher_support)) #need to fix
  
  
 #plot the indicator  
 hist(teacher_questionnaire_dta$teacher_support) 
  
  
  
  final_indicator_data_TSUP <- teacher_questionnaire_dta %>%
    mutate(n_mssing_TSUP=n_miss_row(.)) %>%
    group_by(s_ecole_code) %>%
    summarise_all( ~(if(is.numeric(.)) mean(., na.rm = TRUE) else first(.)))  
  
  
```
## Teacher Teaching Evaluation

```{r tevl}
  #############################################
  ##### Teacher Teaching Evaluation ###########
  #############################################
  
  # School survey. This policy lever measures whether there is a teacher evaluation system in place, and if so, the types of decisions that are made based on the evaluation results. Score is the sum of the following: 
  #   - 1 Point. Was teacher formally evaluated in past school year? 
  #   - 1 Point total. 0.2 points for each of the following: Evaluation included evaluation of attendance, knowledge of subject matter, pedagogical skills in the classroom, students' academic achievement, students' socio-emotional development 
  # - 1 Point. Consequences exist if teacher receives 2 or more negative evaluations 
  # - 1 Point. Rewards exist if teacher receives 2 or more positive evaluations
  
  

  
  teacher_questionnaire_dta<- teacher_questionnaire_dta %>%
    mutate(formally_evaluated=bin_var(d_m2bb2_06,1),
           evaluation_content=if_else(d_m2bb2_06==1,
                                      (as.numeric(d_m2bb2_08b==1)+as.numeric(d_m2bb2_08c==1)+ as.numeric(d_m2bb2_08d==1) + as.numeric(d_m2bb2_08e==1) + as.numeric(d_m2bb2_08f==1))/5,
                                      0),
           negative_consequences=case_when(
             (d_m2bb2_09a==1 | d_m2bb2_09b==1 | d_m2bb2_09c==1 | d_m2bb2_09d==1 | d_m2bb2_09f==1) ~ 1,
              TRUE ~ 0),
           positive_consequences=case_when(
             (d_m2bb2_10a==1 | d_m2bb2_10b==1 | d_m2bb2_10c==1 | d_m2bb2_10d==1 | d_m2bb2_10f==1) ~ 1,
             TRUE ~ 0)
    ) %>%
    mutate(teaching_evaluation=1+formally_evaluated+evaluation_content+negative_consequences+positive_consequences)

#plot the indicator  
 hist(teacher_questionnaire_dta$teaching_evaluation)
  
  final_indicator_data_TEVL <- teacher_questionnaire_dta %>%
    mutate(n_mssing_TEVL=n_miss_row(.)) %>%
    group_by(s_ecole_code) %>%
    summarise_all( ~(if(is.numeric(.)) mean(., na.rm = TRUE) else first(.))) 
  
  
  
```
## Teacher  Monitoring and Accountability

```{r tmna}
  
  #############################################
  ##### Teacher  Monitoring and Accountability ###########
  #############################################
  
  # School Survey. This policy lever measures the extent to which teacher presence is being monitored, whether attendance is rewarded, and whether there are consequences for chronic absence. Score is the sum of the following: 
  #   - 1 Point. Teachers evaluated by some authority on basis of absence. 
  # - 1 Point. Good attendance is rewarded. 
  # - 1 Point. There are consequences for chronic absence (more than 30% absence). 
  # - 1 Point. One minus the fraction of teachers that had to miss class because of any of the following: collect paycheck, school administrative procedure, errands or request of the school district office, other administrative tasks.
  

  
  teacher_questionnaire_dta <- teacher_questionnaire_dta %>%
    mutate(attendance_evaluated=if_else(d_m2bb2_06==1,
                                        case_when(
                                          (d_m2bb2_08a==1) ~ 1,
                                          TRUE ~ 0
                                        ),
                                        0),
           attendance_rewarded=if_else(d_m2be_04==1,
                                       case_when(
                                         (d_m2be_05a==1) ~ 1,
                                         TRUE ~ 0
                                       ),
                                       0),
           attendence_sanctions=case_when(
             (d_m2bb2_021==1 | d_m2bb2_022==1 | d_m2bb2_023==1 | d_m2bb2_024==1 | d_m2bb2_025==1 | d_m2bb2_028==1) ~ 1,
             
             TRUE ~ 0
           ),
           miss_class_admin=case_when(
             (d_m2bb2_01a==1 | d_m2bb2_01b==1 | d_m2bb2_01c==1 | d_m2bb2_01d==1 | d_m2bb2_01e==1) ~ 1,
             TRUE ~ 0
           )
    )  %>%
    mutate(teacher_monitoring=1+attendance_evaluated + 1*attendance_rewarded + 1*attendence_sanctions + (1-miss_class_admin))

#plot the indicator  
 hist(teacher_questionnaire_dta$teacher_monitoring)
 hist(teacher_questionnaire_dta$attendance_evaluated)
 hist(teacher_questionnaire_dta$attendance_rewarded)
 hist(teacher_questionnaire_dta$attendence_sanctions)
 hist(teacher_questionnaire_dta$miss_class_admin)
  
  final_indicator_data_TMNA <- teacher_questionnaire_dta %>%
    mutate(n_mssing_TMNA=n_miss_row(.)) %>%
    group_by(s_ecole_code) %>%
    summarise_all( ~(if(is.numeric(.)) mean(., na.rm = TRUE) else first(.))) 
  
  
```
## Teacher  Intrinsic Motivation 

```{r tinm}
  
  #############################################
  ##### Teacher  Intrinsic Motivation ###########
  #############################################
  
  # 
  # School Survey. This lever measures whether teachers are intrinsically motivated to teach. The question(s) aim to address this 
  # phenomenon by measuring the level of intrinsic motivation among teachers as well as teacher values that may be relevant for 
  # ensuring that the teacher is motivated to focus on all children and not just some. Average score (1 (worst) - 5 (best)) on items 
  # given to teachers on intrinsic motivation.
    intrinsic_motiv_q_rev <- c('d_m2bc_01','d_m2bc_02', 'd_m2bc_03', 'd_m2bc_04', 'd_m2bc_05', 'd_m2bc_06')
  
  #intrinsic_motiv_q <- c( 'm3scq11_tinm', 'm3scq14_tinm')
  

  attitude_fun_rev2  <- function(x) {
    case_when(
      x==97 ~ as.numeric(NA),
      x==1 ~ 5,
      x==2 ~ 3.67,
      x==3 ~ 2.33,
      x==4 ~ 1
    )
  }
  
  teacher_questionnaire_dta <- teacher_questionnaire_dta %>%
    mutate(n_mssing_TINM=n_miss_row(.)) %>%
    mutate(    
      SE_PRM_TINM_1 = 100*if_else(d_m2bc_01>=3,1,0),  #(De Facto) Percent of teachers that agree or strongly agrees with It is acceptable for a teacher to be absent if the ~
      SE_PRM_TINM_2 = 100*if_else(d_m2bc_02>=3,1,0),  #(De Facto) Percent of teachers that agree or strongly agrees with It is acceptable for a teacher to be absent if stud~
      SE_PRM_TINM_3 = 100*if_else(d_m2bc_03>=3,1,0),  #(De Facto) Percent of teachers that agree or strongly agrees with It is acceptable for a teacher to be absent if the ~
      SE_PRM_TINM_4 = 100*if_else(d_m2bc_04>=3,1,0),  #(De Facto) Percent of teachers that agree or strongly agrees with Students deserve more attention if they attend scho~
      SE_PRM_TINM_5 = 100*if_else(d_m2bc_05>=3,1,0),  #(De Facto) Percent of teachers that agree or strongly agrees with Students deserve more attention if they come to sch~
      SE_PRM_TINM_6 = 100*if_else(d_m2bc_06>=3,1,0),  #(De Facto) Percent of teachers that agree or strongly agrees with Students deserve more attention if they are motivat~
      #SE_PRM_TINM_7 = 100*if_else(m3scq7_tinm>=3,1,0),  #(De Facto) Percent of teachers that agree or strongly agrees with Students have a certain amount of intelligence and ~
      #SE_PRM_TINM_8 = 100*if_else(m3scq10_tinm>=3,1,0),  #(De Facto) Percent of teachers that agree or strongly agrees with To be honest, students can't really change how inte~
      #SE_PRM_TINM_9 = 100*if_else(m3scq11_tinm>=3,1,0),  #(De Facto) Percent of teachers that agree or strongly agrees with Students can always substantially change how intell~
      #SE_PRM_TINM_10 = 100*if_else(m3scq14_tinm>=3,1,0) #(De Facto) Percent of teachers that agree or strongly agrees with \"Students can change even their basic intelligence l~
    ) %>%
    mutate_at(intrinsic_motiv_q_rev, attitude_fun_rev2 ) %>%
    #mutate_at(intrinsic_motiv_q, attitude_fun ) %>%
    mutate(acceptable_absent=(d_m2bc_01+ d_m2bc_02 + d_m2bc_03)/3,
           students_deserve_attention=(d_m2bc_04+ d_m2bc_05 + d_m2bc_06 )/3,
           #growth_mindset=(m3scq7_tinm + m3scq10_tinm + m3scq11_tinm + m3scq14_tinm)/4,
           motivation_teaching=case_when(
             d_m2bc_09==1 ~ 0, #penalize teachers who report the number 1 reason is to have steady career rather than helping students or internal motivation.
             d_m2bc_09!=1 ~ 1,
             TRUE ~ as.numeric(NA)
           )) %>%
    mutate(intrinsic_motivation=1+(.2*acceptable_absent + .2*students_deserve_attention  + motivation_teaching+bin_var(d_m2bd_02,1))) 

#plot the indicator  
 hist(teacher_questionnaire_dta$intrinsic_motivation)
 hist(teacher_questionnaire_dta$acceptable_absent)
 hist(teacher_questionnaire_dta$students_deserve_attention)
 hist(teacher_questionnaire_dta$motivation_teaching)
 hist(teacher_questionnaire_dta$d_m2bd_02)
 
 
  final_indicator_data_TINM <- teacher_questionnaire_dta %>%
    mutate(n_mssing_TINM=n_miss_row(.)) %>%
    group_by(s_ecole_code) %>%
    summarise_all( ~(if(is.numeric(.)) mean(., na.rm = TRUE) else first(.)))  
  
  

```
## School Management Clarity of Functions

the codes below does not work because I could not find the data about policy knowledge from the principal.  Can we pull from other questions to infer whether school management is clear.


```{r SCFN, eval=FALSE, include=FALSE}

  #############################################
  ##### School School Management Clarity of Functions  ###########
  #############################################
  
  #------------------------------------------------------------------------------#
  ##### NOTE - the codes below does not work because I could not find the data about policy knowledge from the principal
  
                          school_data_SCFN <- management_dta %>%
                            mutate(infrastructure_scfn=if_else((m7sfq15a_pknw__0==1 | m7sfq15a_pknw__98==1),0,1),
                                   materials_scfn=if_else((m7sfq15b_pknw__0==1 | m7sfq15b_pknw__98==1),0,1),
                                   hiring_scfn=if_else((m7sfq15c_pknw__0==1 | m7sfq15c_pknw__98==1),0,1),
                                   supervision_scfn=if_else((m7sfq15d_pknw__0==1 | m7sfq15d_pknw__98==1),0,1),
                                   student_scfn=if_else((m7sfq15e_pknw__0==1 | m7sfq15e_pknw__98==1),0,1),
                                   principal_hiring_scfn=if_else((m7sfq15f_pknw__0==1 | m7sfq15f_pknw__98==1),0,1),
                                   principal_supervision_scfn=if_else((m7sfq15g_pknw__0==1 | m7sfq15g_pknw__98==1),0,1)
                            ) %>%
                            mutate(sch_management_clarity=1+
                                     (infrastructure_scfn+materials_scfn)/2+
                                     (hiring_scfn + supervision_scfn)/2 +
                                     student_scfn +
                                     (principal_hiring_scfn+ principal_supervision_scfn)/2
                            )
                          final_indicator_data_SCFN <- school_data_SCFN %>%
                            group_by(s_ecole_code) %>%
                            summarise_all(~first(na.omit(.))) %>%
                            mutate(n_mssing_SCFN=n_miss_row(.))  %>%
                            select( -starts_with('interview'), -starts_with('enumerator'))

```

## School Management Attraction


```{r SATT}


  
  #############################################
  ##### School School Management Attraction  ###########
  #############################################
  
  # This policy lever measures whether the right candidates are being attracted to the profession of school principals. The questions will aim to capture the provision of benefits to attract and maintain the best people to serve as principals. 
  # 
  # Scoring: 
  #   -score is between 1-5 based on how satisfied the principal is with status in community. We will also add in component based on Principal salaries.
  # For salary, based GDP per capita from 2018 World Bank  https://data.worldbank.org/indicator/NY.GDP.PCAP.CN?locations=MG.  
  
  school_data_SATT <- management_dta %>%
    mutate(principal_satisfaction=attitude_fun_rev(m7shq1_satt),
           principal_salary=12*m7shq2_satt/1876796	) %>%
    mutate(
      principal_salary_score=case_when(
        between(principal_salary,0,0.5) ~ 1,
        between(principal_salary,0.5,0.75) ~ 2,
        between(principal_salary,0.75,1) ~ 3,
        between(principal_salary,1,1.5) ~ 4,
        between(principal_salary,1.5,5) ~ 5)) %>%
    mutate(sch_management_attraction=(principal_satisfaction+principal_salary_score)/2) 
  final_indicator_data_SATT <- school_data_SATT %>%
    group_by(s_ecole_code) %>%
    summarise_all(~first(na.omit(.))) %>%
    mutate(n_mssing_SATT=n_miss_row(.))  %>%
    select( -starts_with('interview'), -starts_with('enumerator'))  
  
hist(school_data_SATT$sch_management_attraction)  
hist(school_data_SATT$principal_satisfaction)  
hist(school_data_SATT$principal_salary_score)  
school_data_SATT %>%
  ggplot(aes(x=m7shq2_satt)) +
    geom_histogram() +
    scale_x_continuous(label=scales::comma)
  
  
```
## School Management Selection and Deployment 

```{r SSLD}

  
  #############################################
  ##### School School Management Selection and Deployment  ###########
  #############################################
  
  
  # This policy lever measures whether the right candidates being selected. These questions will probe what the recruitment process is like to 
  # ensure that these individuals are getting the positions. The question would ultimately be based on: 1) there is a standard approach for selecting principals,
  # 2) that approach relies on professional/academic requirements, and 3) those requirements are common in practice. 
  # 
  # Scoring: 
  #   - 1 (lowest score) Most important factor is political affiliations or ethnic group. 
  # - 2 Political affiliations or ethnic group is a consideration, but other factors considered as well. 
  # - 3 Most important factor is years of experience, good relationship with owner/education department, and does not factor in quality teaching, demonstrated management qualities, or knowledge of local community. 
  # - 4 Quality teaching, demonstrated management qualities, or knowledge of local community is a consideration in hiring, but not the most important factor 
  # - 5 Quality teaching, demonstrated management qualities, or knowledge of local community is the most important factor in hiring.
  
  school_data_SSLD <- management_dta %>%
    mutate(sch_selection_deployment=case_when(
      (m7sgq2_ssld==2 | m7sgq2_ssld==3 | m7sgq2_ssld==8) ~ 5,
      (m7sgq2_ssld==6 | m7sgq2_ssld==7) ~ 1,
      (!(m7sgq2_ssld==6 | m7sgq2_ssld==7) & (m7sgq1_ssld02==1 | m7sgq1_ssld03==1 | m7sgq1_ssld08==1) ) ~ 4,
      (!(m7sgq2_ssld==6 | m7sgq2_ssld==7) & (m7sgq1_ssld01==1 | m7sgq1_ssld04==1 | m7sgq1_ssld05==1 | m7sgq1_ssld99==1) ) ~ 3,
      (m7sgq1_ssld06==1 | m7sgq1_ssld07==1 ) ~ 2, 
      TRUE ~ as.numeric(NA))
    )%>% 
    rename(school_code = s_ecole_code)
  
  final_indicator_data_SSLD <- school_data_SSLD %>%
    mutate(n_mssing_SSLD=n_miss_row(.))  %>%
    select( -starts_with('interview'), -starts_with('enumerator'))  
  
hist(school_data_SSLD$sch_selection_deployment)
    
```
## School Management Support

```{r SSUP}
  #############################################
  ##### School School Management Support  ###########
  #############################################
  
  
  # This policy lever measures the extent to which principals receive training and/or exposure to other professional opportunities that could help them be better school leaders. 
  # The questions aim to figure out if such programs are provided, and if they are, their level of quality. 
  # 
  # Scoring (sum of components below): 
  #   - 1 Point. Principal has received formal training on managing school. 
  # - 1/3 Point. Had management training for new principals. 
  # - 1/3 Point. Had management in-service training. 
  # - 1/3 Point. Had mentoring/coaching by experienced principals. 
  # - 1 Point. Have used skills gained at training. 
  # - 1 Point. Principals offered training at least once per year
  
  school_data_SSUP <- management_dta %>%
    mutate(across(matches("^m7sgq4_ssup[0-9]{2}$"), ~bin_var(.,1))) %>%
    mutate(prinicipal_trained=bin_var(m7sgq3_ssup,1),
           principal_training=if_else(m7sgq3_ssup==1,
                                      rowMeans(.[grep(x=colnames(management_dta), 
                                                      pattern="^m7sgq4_ssup[0-9]{2}$")], na.rm=TRUE),
                                      0),
           principal_used_skills=if_else(m7sgq3_ssup==1,
                                         bin_var(m7sgq5_ssup,1),0),
           principal_offered=if_else((m7sgq7_ssup==2 | m7sgq7_ssup==3 | m7sgq7_ssup==4 | m7sgq7_ssup==5),1,0)
    ) %>%
    mutate(sch_support=1+prinicipal_trained+principal_training+principal_used_skills+principal_offered)%>% 
    rename(school_code = s_ecole_code)
  
  final_indicator_data_SSUP <- school_data_SSUP %>%
    mutate(n_mssing_SSUP=n_miss_row(.))  %>%
    select( -starts_with('interview'), -starts_with('enumerator'))  
  
  hist(final_indicator_data_SSUP$principal_offered)
  hist(final_indicator_data_SSUP$principal_used_skills)
  hist(final_indicator_data_SSUP$principal_training)
  hist(final_indicator_data_SSUP$prinicipal_trained)
  hist(final_indicator_data_SSUP$sch_support)

```

## School Management Evaluation 

```{r SEVL}


  
  #############################################
  ##### School School Management Evaluation  ###########
  #############################################
  
  # School Survey. This policy lever measures the extent to which principal performance is being monitored and enforced via accountability measures. 
  # The idea is that the indicator will be based on: 1) there is a legislation outlining the need to monitor, 2) principals are being evaluated, 3) 
  # principals are being evaluated on multiple things, and 4) there the accountability mechanisms in place.
  
  
  
  school_data_SEVL<- management_dta %>%
    mutate(across(matches("m7sgq10_sevl[0-9]{2}$|m7sgq10_sevl98"), ~bin_var(.,1))) %>%
    mutate(principal_formally_evaluated=bin_var(m7sgq8_sevl,1),
           principal_eval_tot=rowSums(.[grep(x=colnames(management_dta), 
                                             pattern="m7sgq10_sevl[0-9]{2}$")], na.rm=TRUE)-m7sgq10_sevl98) %>%
    mutate(principal_evaluation_multiple=if_else(m7sgq8_sevl==1,
                                                 case_when(
                                                   principal_eval_tot>=5 ~ 1,
                                                   (principal_eval_tot>1 & principal_eval_tot<5) ~ 0.666667,
                                                   principal_eval_tot==1 ~ 0.3333333,
                                                   TRUE ~ 0
                                                 ),
                                                 0),
           principal_negative_consequences=case_when(
             (m7sgq11_sevl01==1 | m7sgq11_sevl02==1 | m7sgq11_sevl03==1 | m7sgq11_sevl04==1 | m7sgq11_sevl99==1) ~ 1,
             TRUE ~ 0),
           principal_positive_consequences=case_when(
             (m7sgq12_sevl01==1 | m7sgq12_sevl02==1 | m7sgq12_sevl03==1 | m7sgq12_sevl04==1 | m7sgq12_sevl99==1) ~ 1,
             TRUE ~ 0)
    ) %>%
    mutate(principal_evaluation=1+principal_formally_evaluated+principal_evaluation_multiple+principal_negative_consequences+principal_positive_consequences)%>% 
    rename(school_code = s_ecole_code)
  
  final_indicator_data_SEVL <- school_data_SEVL %>%
    mutate(n_mssing_SEVL=n_miss_row(.))  %>%
    select( -starts_with('interview'), -starts_with('enumerator'))  
  

hist(final_indicator_data_SEVL$principal_evaluation)
hist(final_indicator_data_SEVL$principal_formally_evaluated)  
hist(final_indicator_data_SEVL$principal_evaluation_multiple)  
hist(final_indicator_data_SEVL$principal_negative_consequences)  
hist(final_indicator_data_SEVL$principal_positive_consequences)  

  
```

## Inputs and Infrastructure Standards

```{r}
 #------------------------------------------------------------------------------#
  ## 13. School  Inputs and Infrastructure Standards ###########
  
  # - 1 Point. Are there standards in place to monitor blackboard and chalk, pens and pencils, basic classroom furniture, computers, textbooks, exercise books, toilets, electricity, drinking water, accessibility for those with disabilities? (partial credit available) 
  
  ## Filtering
  school_data_IMON <- read_dta(file.path(download_folder, "/01-SECABD24DE.dta")) %>% 
    # Only var of interest
    select(-starts_with("s_m")) %>% 
        # Only schools from sample
    filter(s_type_ecole ==3)
    
    
  
  ## Metadata
  meta_IMON <- makeVlist(school_data_IMON)
    ## Computation of indicators
  school_data_ISTD <- school_data_IMON %>%
    # Rename for matching
    setNames(tolower(gsub("d_m1_e11","m1scq9_imon__",names(.)))) %>% 
    setNames(tolower(gsub("d_m1e_04","m1scq4_imon__",names(.)))) %>% 
    setNames(tolower(gsub("d_m1e_13","m1scq13_imon__",names(.)))) %>%
    setNames(tolower(gsub("d_m1e_14","m1scq14_imon__",names(.)))) %>%
    mutate(across(matches("m1scq13_imon__|m1scq14_imon__"),~bin_var(.,1))) %>%
  
    # Computation as previously established
    mutate(standards_monitoring_input=rowMeans(.[grep(x=colnames(.), 
                                                      pattern="m1scq13_imon__")], na.rm=TRUE),
           standards_monitoring_infrastructure=rowMeans(.[grep(x=colnames(.), 
                                                               pattern="m1scq14_imon__")], na.rm=TRUE) ) %>%
    mutate(standards_monitoring=(standards_monitoring_input*6+standards_monitoring_infrastructure*4)/2) %>% 
    
    rename(school_code = s_ecole_code)
  
  
  final_indicator_data_ISTD <- school_data_ISTD %>%
    mutate(n_mssing_ISTD=n_miss_row(.))  %>%
    select( -starts_with('interview'), -starts_with('enumerator'))  
  
  hist(final_indicator_data_ISTD$standards_monitoring_input)
  hist(final_indicator_data_ISTD$standards_monitoring_infrastructure)
  hist(final_indicator_data_ISTD$standards_monitoring)
  
```

## Inputs and Infrastructure Monitoring

```{r}


 
  
  #############################################
  ##### School  Inputs and Infrastructure Monitoring ###########
  #############################################
  
  # School Survey. A score of 1-5 based on 3 factors. Each factor has received an equal weight in terms of points. The factors are the following: 
  #-	Someone is monitoring 
  #-	System for monitoring available (E.g. inventory)
  #-	Community involved in monitoring 
  
  
  school_data_IMON <- read_dta(file.path(download_folder, "/01-SECABD24DE.dta")) %>% 
    # Only var of interest
    select(-starts_with("s_m")) %>% 
        # Only schools from sample
    filter(s_type_ecole ==3) %>%
    
    rename(
      m1scq3_imon = d_m1e_10, 
      m1scq5_imon = d_m1e_05, # inventory for school intrants
      m1scq1_imon = d_m1e_01,
      m1scq7_imon = d_m1e_07
      ) %>% 
    setNames(tolower(gsub("d_m1_e11","m1scq9_imon__",names(.)))) %>% 
    setNames(tolower(gsub("d_m1e_04","m1scq4_imon__",names(.)))) %>% 
    setNames(tolower(gsub("d_m1e_13","m1scq13_imon__",names(.)))) %>%
    setNames(tolower(gsub("d_m1e_14","m1scq14_imon__",names(.)))) %>%
    mutate(across(matches("m1scq4_imon__|m1scq9_imon__"),~bin_var(.,1))) %>%
    
    mutate(m1scq3_imon=bin_var(m1scq3_imon,1),
           system_in_place=case_when(
             m1scq5_imon==0 ~ 0,
             m1scq5_imon==1 ~ 1,
             m1scq5_imon==2 ~ 0.5,
             TRUE ~ 0
           )) %>%
    mutate(monitoring_inputs=if_else(m1scq1_imon==1,
                                     rowMeans(.[grep(x=colnames(school_data_IMON), 
                                                     pattern="m1scq4_imon__")], na.rm=TRUE),
                                     0),
           monitoring_infrastructure=if_else(m1scq7_imon==1,
                                             rowMeans(.[grep(x=colnames(school_data_IMON), 
                                                             pattern="m1scq9_imon__")], na.rm=TRUE),
                                             0),
    ) %>%
    mutate(parents_involved=if_else(m1scq3_imon==1,1,0,0)) %>%
    mutate(sch_monitoring=1+(monitoring_inputs+monitoring_infrastructure)/2+system_in_place+parents_involved) %>% 
    rename(school_code = s_ecole_code)
  
  
  
  
  final_indicator_data_IMON <- school_data_IMON %>%
    mutate(n_mssing_IMON=n_miss_row(.))  %>%
    select( -starts_with('interview'), -starts_with('enumerator'))  
  
  hist(final_indicator_data_IMON$monitoring_inputs)
  hist(final_indicator_data_IMON$monitoring_infrastructure)
  hist(final_indicator_data_IMON$system_in_place)
  hist(final_indicator_data_IMON$parents_involved)

  hist(final_indicator_data_IMON$sch_monitoring)
  

```

