
---
title: "Data Quality Checks - School Survey"
author: "GEPD Team"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#load relevant libraries
library(tidyverse)
library(haven)
library(plotly)
library(naniar)
library(crosstalk)
library(leaflet)
library(Hmisc)
library(DT)
library(mice)
library(stargazer)
library(skimr)
library(knitr)
library(kableExtra)

#Country name and year of survey
country <-'Pakistan_all'
country_name <- "Pakistan_all"
year <- '2021'
province <- "KP"
api_user <- "GEPD_api_PAK"

#Load the data
#read in school level file
#Add your UPI here and set the directory paths of your choice.
if (Sys.getenv("USERNAME") == "wb469649"){
  #project_folder  <- "//wbgfscifs01/GEDEDU/datalib-edu/projects/gepd"
  project_folder  <- "C:/Users/wb469649/WBG/Ezequiel Molina - Dashboard (Team Folder)/Country_Work/"
  download_folder <-file.path(paste(project_folder,country_name,year,"Data/02. Provinces",province,"/school_survey/raw/", sep="/"))
  save_folder <- file.path(paste(project_folder,country_name,year,"Data/02. Provinces",province,"/school_survey/clean/", sep="/"))
  
  backup_onedrive="yes"
  save_folder_onedrive <- file.path(paste("C:/Users/wb469649/WBG/Ezequiel Molina - Dashboard (Team Folder)/Country_Work/", country_name,year,"Data/01. Pilot/clean", sep="/"))
  
} else if (Sys.getenv("USERNAME") == "wb577189"){
  #project_folder  <- "//wbgfscifs01/GEDEDU/datalib-edu/projects/gepd"
  project_folder  <- "C:/Users/wb577189/OneDrive - WBG/My files/Dashboard (Team Folder)/Country_Work/"
  download_folder <-file.path(paste(project_folder,country_name,year,"Data/02. Provinces",province,"/school_survey/raw/", sep="/"))
  save_folder <- file.path(paste(project_folder,country_name,year,"Data/02. Provinces",province,"/school_survey/clean/", sep="/"))
  
  backup_onedrive="yes"
  save_folder_onedrive <- file.path(paste("C:/Users/wb577189/OneDrive - WBG/My files/Dashboard (Team Folder)/Country_Work/", country_name,year,"Data/01. Pilot/clean", sep="/"))
  
} else {
  download_folder <- choose.dir(default = "", caption = "Select folder to open data downloaded from API")
  save_folder <- choose.dir(default = "", caption = "Select folder to save final data")
  save_folder_onedrive <- choose.dir(default = "", caption = "Select folder to save backed up data to onedrive")
  
}

load(file=paste(save_folder, "paradata_light.RData", sep="/"))
```

## Introduction

This file produces a set of basic quality checks to highlight potential issues in data collection.  

## Paradata on Interview Lengths & Time Completed

The following figures and tables show the time length of each section.  Specific information for each enumerator, date, and module is available.

A useful check is to examine the length of time that passes between questions in a section.  It may be useful for detecting anomalies with respect to enumerators, and also could be useful for streamlining our survey.  The filter in the sidebar gives the user the ability to filter by length of time that passes between sections.  By scrolling all the way to the right, only the sections that take an exceptionally long time to fill out appear.  Additionally, the user has the option to filter by enumerator, date of survey, and module.

```{r, echo=FALSE, warning=FALSE}

######################################
# Length of each question by Enumerator
#######################################

# para_df_tab <- para_df %>%
#   select( responsible, date, module, section, indicator, question, varlabel, timelength_sec, ï..interview__id)

# linked_q_df<-SharedData$new(para_df_tab)
#
#
# bscols(widths=c(3,NA),
#        list(
#          filter_slider("time", "Length in Seconds", linked_q_df, ~timelength_sec),
#          filter_select("enumerator", "Enumerator", linked_q_df, ~responsible),
#          filter_checkbox("date", "Date of Survey", linked_q_df, ~as.character(date), inline=FALSE),
#          filter_checkbox("module", "Module", linked_q_df, ~module, inline=FALSE)
#
#        ),
#
#        list (
#          plot_ly(linked_q_df, x=~responsible, y=~timelength_sec, type='scatter', mode='markers', color=~question) %>%
#            layout(title='Question Length by Enumerator',yaxis=list(title='Length in Seconds'), xaxis=list(title='Enumerator ID'))
#          # datatable(linked_q_df,
#          #           colnames=c( 'Enumerator' = 'responsible', 'Date' = 'date', 'Module' = 'module', 'Section' = 'section',
#          #                    'Indicator' = 'indicator', 'Question ID' = 'question', 'Question'='varlabel', 'Length in Seconds' = 'timelength_sec'),
#          #           extensions="Scroller", style="bootstrap", class="compact", width="100%",
#          #           options=list(deferRender=TRUE, scrollY=300, scrollX=TRUE))
#
#        )
#
# )

######################################
# Length of each section by Enumerator
#######################################


linked_s_df<-SharedData$new(para_df_section)


bscols(widths=c(3,NA),
       list(
         filter_slider("time", "Length in Seconds", linked_s_df, ~timelength_sec),
         filter_select("enumerator", "Enumerator", linked_s_df, ~responsible),
         filter_checkbox("date", "Date of Survey", linked_s_df, ~as.character(date), inline=FALSE),
         filter_checkbox("module", "Module", linked_s_df, ~module, inline=FALSE)
       ),
       list (
       plot_ly(linked_s_df, x=~responsible, y=~timelength_sec, type='scatter', mode='markers', color=~section) %>%
         layout(title='Section Length by Enumerator',yaxis=list(title='Length of Section in Seconds'), xaxis=list(title='Enumerator ID'))
      
        # datatable(linked_s_df, 
        #          colnames=c('Enumerator' = 'responsible', 'Date' = 'date', 'Module' = 'module', 'Section' = 'section',
        #                     'Length in Seconds' = 'timelength_sec'),
        #          extensions="Scroller", style="bootstrap", class="compact", width="100%",
        #          options=list(deferRender=TRUE, scrollY=300, scrollX=TRUE))
        # 
       )
       
)

  

```

The next graph shows the time of day each section was completed by each enumerator.  One quality check that this provides is to determine when the enumerator filled out the questions.  Enumerators that fill out questions outside of normal operating hours of the school can be asked to clarify why they did so.

```{r time_day, echo=FALSE, warning=FALSE}

######################################
# Time of Day of each question by Enumerator
#######################################



linked_t_df<-SharedData$new(para_df_tab)




bscols(widths=c(3,NA),
       list(
         filter_slider("Time", "Time Section Completed", linked_t_df, ~timestamp),
         filter_select("enumerator", "Enumerator", linked_t_df, ~responsible),
         filter_checkbox("date", "Date of Survey", linked_t_df, ~as.character(date), inline=FALSE),
         filter_checkbox("module", "Module", linked_t_df, ~module, inline=FALSE)
         
       ),
       
       list (
         plot_ly(linked_t_df, x=~section, y=~timestamp, type='scatter', mode='markers', color=~responsible) %>%
           layout(title='Time Section Completed by Enumerator',yaxis=list(title='Time'), xaxis=list(title='Section ID'))
         # datatable(linked_t_df, 
         #           colnames=c('Interview Code'='ï..interview__id', 'Enumerator' = 'responsible', 'Date' = 'date', 'Module' = 'module', 'Section' = 'section',
         #                      'Indicator' = 'indicator', 'Question ID' = 'question', 'Question'='varlabel', 'Time' = 'timestamp'),
         #           extensions="Scroller", style="bootstrap", class="compact", width="100%",
         #           options=list(deferRender=TRUE, scrollY=300, scrollX=TRUE)) 
         
       )
       
)  

```



## Missing Values and Other Checks

To start, the following figures and tables will highlight missing values for a few of our key indicators. 


First, we will display the modules with information collected in each school.

```{r school_modules_completed, echo=FALSE}

datatable(school_modules_complete,
          caption='Modules That Have at Least Some Information for Each School',
          class='cell-border stripe',
          extensions = c ('Buttons' ), 
                options=list(
                  dom = 'Bfrtip',
                  buttons = c('copy', 'csv','excel'),
                  pageLength = 60,
                  ordering=F))
write_excel_csv(school_modules_complete, path = paste(save_folder, "school_modules_complete.csv", sep="/")) 



```


```{r missings, echo=FALSE, error=FALSE, message=FALSE, fig.width=8,fig.height=13}

load(paste(save_folder, "school_survey_data.RData", sep="/"))

#Load original sample of schools
# currentDate<-c("2019-08-30")
# sample_frame_name <- paste("C:/Users/WB469649/WBG/Ezequiel Molina - Dashboard (Team Folder)/Country_Work/Rwanda/2019/Data/Sampling/school_sample_",currentDate,".RData", sep="")
# 
# load(sample_frame_name)

# sample_frame_name <- read.csv("C:/Users/wb577189/OneDrive - WBG/Desktop/Education GP/01. GEPD/02. Country_Work/Sierra Leone/04. Data/Sampling/Cleaning/sample_clean_2022-05-03.csv") %>% 
#   select(-internet) %>% 
#   rename(sch_id = idemis_code)

#list additional info that will be useful to keep in each indicator dataframe
preamble_info <- c('interview__id', 'school_code',
                   'school_name_preload', 
                   'school_province_preload', 'school_district_preload', 'school_code_preload',
                   'school_info_correct', 'm1s0q2_name', 'm1s0q2_code', 'm1s0q2_emis',
                   'survey_time', 'lat', 'lon')

keep_info <-       c('school_code',
                     'school_name_preload', 
                     'school_province_preload', 'school_district_preload', 'school_code_preload',
                     'school_info_correct', 'm1s0q2_name', 'm1s0q2_code', 'm1s0q2_emis',
                     'survey_time', 'lat', 'lon')


orig_colnames<-colnames(school_dta_short)

#compare data collected to original sample
school_dta_short <- school_dta_short %>%
  mutate(sch_id=as.numeric(school_emis_preload)) %>%
  #left_join(sample_frame_name, by="sch_id") %>%
  mutate(school_ipw=1)
  
 # school_dta_short %>% data_set
 #    group_by(rural) %>%
 #    summarise(N=n()) 
 # 
 


#plot missing values by indicator
gg_miss_var(school_dta_short[,orig_colnames])
```

Below the missings plot is a table of summary statistics for a few key indicators. This shows the min, 25th percentile, median, 75th percentile, max, mean, standard deviation, total number of schools, and number of schools with missing information for each variable.  The underlying data is aggregated to the school, and the means reported are raw means, not weighted means, which will be produced in the report.  These are meant to give a basic idea of the data.

```{r missings2, include=FALSE}

#table of summary stats
#merge on teacher content knowledge

indicator_list<-c("student_knowledge",
                  "student_proficient", 
                  'student_attendance',
                  "absence_rate", 
                  "content_knowledge", 
                  "teach_score",
                  "ecd_student_knowledge",
                  "ecd_student_proficiency", 
                  "inputs", 
                  "infrastructure", 
                  "operational_management", 
                  "instructional_leadership",
                  'principal_knowledge_score', 
                  'principal_management',
                  'teacher_attraction',
                  'teacher_selection_deployment',
                  'teacher_support',
                  'teaching_evaluation',
                  'teacher_monitoring',
                  'intrinsic_motivation',
                  'school_monitoring',
                  'sch_management_attraction',
                  'school_selection_deployment',
                  'school_support',
                  'principal_evaluation'
                  )

indicator_labels<-c("4th Grade Student Knowledge (Fraction Correct)", 
                    "Proficiency on GEPD assessment",
                    "Student Attendance Rate",
                    "Teacher Absence Rate", 
                    "Teacher Content Knowledge", 
                    "Teacher Pedagogy (TEACH)",
                    "1st Grade Assessment (Fraction Correct)",
                    "Readiness for learning",
                    "Inputs", 
                    "Infrastructure",
                    "Operational Management",
                    "Instructional Leadership",
                    'Principal Knowledge',
                    'Principal Management Skills',
                    'Teacher Attraction (De Facto)',
                    'Teacher Selection & Deployment (De Facto)',
                    'Teacher Support (De Facto)',
                    'Teacher Evaluation (De Facto)',
                    'Teacher Monitoring & Accountability (De Facto)',
                    "Teacher Intrinsic Motivation",
                    "Inputs and Infrastructure Monitoring",
                    "School Management Attraction",
                    "School Management Selection & Deployment",
                    "School Management Support",
                    "School Management Evaluation"
                    )

sumstats<-school_dta_short %>%
  select(indicator_list) %>% select(-operational_management)

#impute missing weights with median
school_dta_short <- school_dta_short %>%
  mutate(school_ipw=if_else(is.na(school_ipw), median(school_ipw, na.rm=T), school_ipw)) %>%
  mutate(school_ipw=if_else(is.na(school_ipw), 1, school_ipw))

sch_ipw<-school_dta_short$school_ipw 


#add function to produce weighted summary stats
          my_skim<-    skim_with( numeric = sfl( mean = ~ wtd.mean(.,  w=sch_ipw, na.rm=TRUE),
                                                 sd = ~ sqrt(wtd.var(.,  weights=sch_ipw, na.rm=TRUE)),
                                                 p25 = ~ (wtd.quantile(., probs=c(0.25),  weights=sch_ipw, na.rm=TRUE)),
                                                 p50 = ~ (wtd.quantile(., probs=c(0.5), weights=sch_ipw, na.rm=TRUE)),
                                                 p75 = ~ (wtd.quantile(., probs=c(0.75), weights=sch_ipw, na.rm=TRUE)),
                                                 complete = ~ sum(!is.na(.))))



sumstats_df<-my_skim(sumstats) %>%
           yank("numeric") %>%
           mutate(variable=skim_variable) %>%
           select(variable, mean, sd, p0, p25, p50, p75, p100, complete,  hist) %>%
  mutate(variable=factor(variable, levels=indicator_list,
                         labels=indicator_labels)) %>%
  mutate(ci_low=as.numeric(mean)-1.96*(as.numeric(sd)/sqrt(as.numeric(complete))),
         ci_high=as.numeric(mean)+1.96*(as.numeric(sd)/sqrt(as.numeric(complete)))) %>%
  mutate(ci=paste("[",round(ci_low,2),", ", round(ci_high,2),"]", sep="")) %>%
  select(variable, mean, ci, sd, p0, p25, p50, p75, p100, complete, hist) %>%
  arrange(match(variable, indicator_labels))

#export Indicators sumstats
write_excel_csv(sumstats_df, paste(save_folder,'GEPD_school_Indicators.csv',sep=""))

```


```{r missings_kable, echo=FALSE}

knitr::kable(sumstats_df, caption="Summary Statistics of Key Indicator Variables" , col.names = c("Indicator", "Mean", "95% Confidence Interval", "Std Dev","Min", "25th Percentile", "Median", "75th Percentile", "Max", "# Complete Cases", "Histogram"), digits = 2 ) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive")) 
# %>%
#   footnote(general="Weighted Summary Statistics using School Survey Weights")

```


In the next check, we will asssess whether any schools were not part of the pre-loaded list of schools.

```{r, echo=FALSE}
# We export the observations for which the schools are not part of the pre-loaded list
# We identify these schools using the variable "school_name_preload", because this variable is not filled in case the school is not on the list


df_school_preloaded <- school_dta_short %>%
  filter(is.na(school_name_preload)) %>%
  select(m1s0q2_name, m1s0q2_code, m1s0q2_emis) 




#setExcelSheet "Schools and Teachers"

```

These schools are not part of the pre-loaded list of schools (an empty list is good!):

```{r message=FALSE, warning=FALSE, echo=FALSE}

kable(df_school_preloaded) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

```









## Interactive Map
In the following map below, users may click on specific provinces or regions to examine missing indicators.  The slider controls the schools that appear based on the number of missing indicators.  For instance, sliding the slider to 4 will keep only schools that are missing four or more indicators, indicating a relatively severe missing data problem.  In the future, I may also include checkboxes for specific survey supervisors, to examine if any particular supervisors have worse performance than others.  I could also add filters by day the survey took place.  

The map is color coded.  Green indicators, for instance, have no missing information on our key indicators: 4th grade student achievement, teacher absence, teacher content knowledge, Capacity for Learning (ECD student knowledge), basic inputs, and basic infrastructure ).  Black indicators are missing all six indicators.  More indicators can be added to this list, but for now in the SDI data this is what we could produce before our data collection.

```{r map_guts, warning=FALSE, include=FALSE}

####################################################################
#######Map of schools with missing school info#####
####################################################################
school_map <- school_dta_short %>%
  filter(!is.na(lat) & !is.na(lon))

#Create indicator of schools with missing values in our indicators

school_map <- school_map %>%
  mutate(missings=(is.na(student_knowledge) | is.na(absence_rate) | is.na(student_attendance) | is.na(content_knowledge) | 
                     is.na(ecd_student_knowledge) | is.na(inputs) | is.na(infrastructure) |  is.na(operational_management)
                   | is.na(intrinsic_motivation) | is.na(instructional_leadership) | is.na(principal_management) | is.na(teacher_attraction) | is.na(teacher_selection_deployment)
                   | is.na(teacher_support) | is.na(teaching_evaluation) | is.na(teacher_monitoring)
                   | is.na(school_monitoring) | is.na(sch_management_attraction) | is.na(school_selection_deployment) 
                   | is.na(school_support) | is.na(principal_evaluation))
         
         )%>%
  mutate(total_missing=is.na(student_knowledge) + is.na(absence_rate) + is.na(student_attendance) + is.na(content_knowledge) + 
           is.na(ecd_student_knowledge) + is.na(inputs) + is.na(infrastructure) + is.na(operational_management)
         + is.na(intrinsic_motivation) + is.na(instructional_leadership) + is.na(principal_management) + is.na(teacher_attraction) + is.na(teacher_selection_deployment) + is.na(teacher_support) + is.na(teaching_evaluation) +
         is.na(teacher_monitoring) + is.na(school_monitoring) + is.na(sch_management_attraction) + is.na(school_selection_deployment) +
         is.na(school_support) + is.na(principal_evaluation))


#color coded markers for missing values
getColor <- function(df_input) {
  sapply(df_input$total_missing, function(total_missing) {
    if (total_missing == 0) {
      "#12E539" #green
    } 
    else if (total_missing == 1) {
      "#1232E5" #blue
    } 
    else if (total_missing == 2) {
      "#E5E512" #yellow
    } 
    else if (total_missing == 3) {
      "#E59412" #orange
    }     
    else if (total_missing == 4) {
      "#8A12E5" #purple
    } 
    else if (total_missing == 5) {
      "#E51212" #red
    }
    else {
      "#000000" #black
    } 
    })
}

#add legend for icons
pal <- colorFactor(
  levels = c( '0','1', '2', '3', '4', '5', '6+'),
  palette = c('#12E539', '#1232E5', '#E5E512', '#E59412', '#8A12E5', '#E51212', '#000000'),
  domain = school_map$total_missing
)

#create icons
icons <- awesomeIcons(
  icon = 'graduation-cap',
  iconColor = getColor(school_map),
  library = 'fa',
  markerColor = 'black'
)



map <- function(df_input) {    leaflet(df_input, height=1200, width=1020) %>% 
  addTiles()  %>%
  addAwesomeMarkers(lng=~lon, lat= ~lat, icon=icons,
                    popup = paste("Name: ", school_map$school_name_preload, " <br>",
                                  "Province: ", school_map$school_province_preload, " <br>",
                                  "District: ", school_map$school_district_preload, " <br>",
                                  "EMIS Code: ", school_map$school_emis_preload, " <br>",
                                  "<font color='red' > Outcomes ", " <br> <font color='black' >",
                                  "Avg 4th Grade Learning Score:", round(school_map$student_knowledge, digits=2), "% <br>",
                                  "Avg 4th Grade Student Attendance:", round(school_map$student_attendance, digits=2), "% <br>",
                                  "<font color='red' > Practice Indicators ", " <br> <font color='black' >",
                                  "Teacher Absence Rate: ", round(school_map$absence_rate, digits=2), "% <br>",
                                  "Teacher Content Knowledge Score: ", round(school_map$content_knowledge, digits=2),"% <br>",
                                  "Teacher Pedagogy (TEACH)", round(school_map$teach_score, digits=2), " <br>",
                                  "Basic Inputs: ", round(school_map$inputs, digits=2), " <br>",
                                  "Basic Infrastructure: ", round(school_map$infrastructure, digits=2), " <br>",
                                  "Capacity for Learning: ", round(school_map$ecd_student_knowledge, digits=2), "% <br>",
                                  "Operational Management: ", round(school_map$operational_management, digits=2), " <br>",
                                  "Instructional Leadership: ", round(school_map$instructional_leadership, digits=2), " <br>",
                                  "Principal Management Skills: ", round(school_map$principal_management, digits=2), " <br>",
                                  "<font color='blue' > Policy Indicators ", " <br> <font color='black' >",
                                  "Teacher Attraction (De Facto): ", round(school_map$teacher_attraction, digits=2), " <br>",
                                  "Teacher Selection & Deployment (De Facto): ", round(school_map$teacher_selection_deployment, digits=2), " <br>",
                                  "Teacher Support (De Facto): ", round(school_map$teacher_support, digits=2), " <br>",
                                  "Teacher Evaluation (De Facto): ", round(school_map$teaching_evaluation, digits=2), " <br>",
                                  "Teacher Monitoring & Accoutability (De Facto): ", round(school_map$teaching_evaluation, digits=2), " <br>",

                                  "Teacher Intrinsic Motivation: ", round(school_map$intrinsic_motivation, digits=2), "<br>",
                                  "Inputs & Infrastructure Monitoring (De Facto): ", round(school_map$school_monitoring, digits=2), "<br>",
                                  "School Management Attraction (De Facto): ", round(school_map$sch_management_attraction, digits=2), "<br>",
                                  "School Management Selection & Deployment: ", round(school_map$school_selection_deployment, digits=2), "<br>",
                                  "School Management Support: ", round(school_map$school_support, digits=2), "<br>",
                                  "School Management Evaluation: ", round(school_map$principal_evaluation, digits=2), "<br>"


                                  ) )  %>%
    addLegend("bottomright", pal=pal, values=~total_missing, title="Missing Indicators"    )

}

```


```{r map_plot, echo=FALSE, warning=FALSE}


linked_df<-SharedData$new(school_map)



bscols(widths=c(3,NA),
  list(
  filter_slider("missings", "Missing Indicators", linked_df, ~total_missing),
  filter_select("prov", "Province", linked_df, ~school_province_preload),
  filter_select("reg", "District", linked_df, ~school_district_preload),
  filter_slider("student_knowledge", "4th Grade Student Knowledge", linked_df, ~student_knowledge),
  filter_slider("student_attendance", "4th Grade Student Attendance", linked_df, ~student_attendance),
  filter_slider("absence_rate", "Teacher Absence Rate", linked_df, ~absence_rate),
  filter_slider("content_knowledge", "Teacher Content Knowledge Score", linked_df, ~content_knowledge),
  filter_slider("inputs", "Basic Inputs", linked_df, ~inputs),
  filter_slider("infrastructure", "Basic Infrastructure", linked_df, ~infrastructure),
  filter_slider("ecd_student_knowledge", "Capacity for Learning", linked_df, ~ecd_student_knowledge),
  filter_slider("operational_management", "Operational Management", linked_df, ~operational_management),
  filter_slider("instructional_leadership", "Instructional Leadership", linked_df, ~instructional_leadership),
  filter_slider("principal_management", "Principal Management Skills", linked_df, ~principal_management)

  ),
  map(linked_df) 

               
)
```


```{r plain_map}

#create icons
icons2 <- awesomeIcons(
  icon = 'graduation-cap',
  iconColor = 'white',
  library = 'fa',
  markerColor = 'blue'
)


map2 <- function(df_input) {    leaflet(df_input, height=1200, width=1020) %>% 
  addTiles()  %>%
  addAwesomeMarkers(lng=~lon, lat= ~lat, icon=icons2,
                    popup = paste("Name: ", school_map$school_name_preload, " <br>",
                                  "Province: ", school_map$school_province_preload, " <br>",
                                  "District: ", school_map$school_district_preload, " <br>",
                                  "EMIS Code: ", school_map$school_emis_preload, " <br>",
                                  "<font color='red' > Outcomes ", " <br> <font color='black' >",
                                  "Avg 4th Grade Learning Score:", round(school_map$student_knowledge, digits=2), "% <br>",
                                  "Avg 4th Grade Student Attendance:", round(school_map$student_attendance, digits=2), "% <br>",
                                  "<font color='red' > Practice Indicators ", " <br> <font color='black' >",
                                  "Teacher Absence Rate: ", round(school_map$absence_rate, digits=2), "% <br>",
                                  "Teacher Content Knowledge Score: ", round(school_map$content_knowledge, digits=2),"% <br>",
                                  "Teacher Pedagogy (TEACH)", round(school_map$teach_score, digits=2), " <br>",
                                  "Basic Inputs: ", round(school_map$inputs, digits=2), " <br>",
                                  "Basic Infrastructure: ", round(school_map$infrastructure, digits=2), " <br>",
                                  "Capacity for Learning: ", round(school_map$ecd_student_knowledge, digits=2), "% <br>",
                                  "Operational Management: ", round(school_map$operational_management, digits=2), " <br>",
                                  "Instructional Leadership: ", round(school_map$instructional_leadership, digits=2), " <br>",
                                  "Principal Management Skills: ", round(school_map$principal_management, digits=2), " <br>",
                                  "<font color='blue' > Policy Indicators ", " <br> <font color='black' >",
                                  "Teacher Attraction (De Facto): ", round(school_map$teacher_attraction, digits=2), " <br>",
                                  "Teacher Selection & Deployment (De Facto): ", round(school_map$teacher_selection_deployment, digits=2), " <br>",
                                  "Teacher Support (De Facto): ", round(school_map$teacher_support, digits=2), " <br>",
                                  "Teacher Evaluation (De Facto): ", round(school_map$teaching_evaluation, digits=2), " <br>",
                                  "Teacher Monitoring & Accoutability (De Facto): ", round(school_map$teaching_evaluation, digits=2), " <br>",

                                  "Teacher Intrinsic Motivation: ", round(school_map$intrinsic_motivation, digits=2), "<br>",
                                  "Inputs & Infrastructure Monitoring (De Facto): ", round(school_map$school_monitoring, digits=2), "<br>",
                                  "School Management Attraction (De Facto): ", round(school_map$sch_management_attraction, digits=2), "<br>",
                                  "School Management Selection & Deployment: ", round(school_map$school_selection_deployment, digits=2), "<br>",
                                  "School Management Support: ", round(school_map$school_support, digits=2), "<br>",
                                  "School Management Evaluation: ", round(school_map$principal_evaluation, digits=2), "<br>"


                                  ) )  %>%
    addLegend("bottomright", pal=pal, values=~total_missing, title="Missing Indicators"    )

}


map2(school_map)

```



## Orphan Teachers

The following table shows teachers in the teacher questionnaire module who could not be matched back to the original teacher roster based on the name and number.  This doesn't necessarily indicate a problem, because the difference may only be due to spelling, but should be investigated.

```{r orphans, warning=FALSE, include=FALSE}

###
#Create list of orphan teachers (cant be matched to questionnaire,  or teacher exam files)
###

#Teachers who can't be matched between questionnaire and examiniation

teacher_roster_list<-teacher_roster %>%
  left_join(school_data_preamble) %>%
  filter(!is.na(questionnaireteachcode2)) %>%
  select( school_code, questionnaireteachcode2,  teacher_number, teacher_name, school_province_preload, school_district_preload, school_name_preload, lat, lon) 

# 
# orphan_fix_list <- readxl::read_xlsx(path=paste(save_folder, 'Corrections/jordan_orphan_teachers.xlsx', sep="/"), sheet = 'jordan_orphan_teachers') %>%
#   select(school_code, interview__key, m3sb_tnumber, corrected_code) %>%
#   mutate(teacher_number=as.numeric(corrected_code),
#          m3sb_tnumber=as.numeric(m3sb_tnumber),
#          corrected_code=as.numeric(corrected_code)) %>%
#   left_join(teacher_roster_list) %>%
#   mutate(corrected_name=teacher_name) %>%
#   select(school_code, m3sb_tnumber, corrected_name, corrected_code)
# 
# orphan_ok_list <- readxl::read_xlsx(path=paste(save_folder, 'orphan teachers.xlsx', sep="/"), sheet = 'matched ok') %>%
#   select(school_code, interview__key, m3sb_tnumber, questionnaireteachcode2) %>%
#   mutate(teacher_number=questionnaireteachcode2) %>%
#   left_join(teacher_roster_list) %>%
#   mutate(corrected_name=teacher_name,
#          corrected_code=as.numeric(questionnaireteachcode2),
#          m3sb_tnumber=as.numeric(m3sb_tnumber)) %>%
#   select(school_code, m3sb_tnumber, corrected_name, corrected_code)
# 
# orphan_fixes <- orphan_fix_list %>%
#   bind_rows(orphan_ok_list) %>%
#   filter(!is.na(corrected_name))

teacher_questionnaire_list<-teacher_questionnaire %>%
  select(interview__key, school_code, teacher_name, teacher_number, m3sb_troster, m3sb_tnumber,school_province_preload, school_district_preload, lat, lon) 
  # left_join(orphan_fixes) %>%
  # mutate(teacher_number=if_else(!is.na(corrected_code), as.numeric(corrected_code), as.numeric(m3sb_tnumber)),
  #        teacher_name=if_else(!is.na(corrected_name), corrected_name, m3sb_troster))

orphans_number_questionnaire <- teacher_questionnaire_list %>%
  anti_join(teacher_roster_list, by=c('teacher_name', 'teacher_number')) %>%
  select(school_code, teacher_name, teacher_number,  school_province_preload, school_district_preload, lat, lon) 


```

```{r orphans2, eval=FALSE, include=FALSE}

datatable(orphans_number_questionnaire,
                   extensions="Scroller", style="bootstrap", class="compact", width="100%",
                   options=list(deferRender=TRUE, scrollY=300, scrollX=TRUE)
          )  

```


```{r orphan_map_guts, eval=FALSE, include=FALSE}

####################################################################
#######Map of schools with missing school info#####
####################################################################
orphan_map <- orphans_number_questionnaire %>%
  filter(!is.na(lat) & !is.na(lon))

#Create indicator of schools with missing values in our indicators

orphan_map_counts <- orphan_map %>%
  group_by(school_code) %>%
  summarise(orphan_count=n())
  
orphan_map <- orphan_map %>%
  left_join(orphan_map_counts)

#color coded markers for missing values
getColor <- function(df_input) {
  sapply(df_input$orphan_count, function(orphan_count) {
    if (orphan_count == 1) {
      "#0EF293" #green
    } 
    else if (orphan_count == 2) {
      "#0E43F2" #blue
    } 
    else if (orphan_count == 3) {
      "#EAF20E" #yellow
    } 
    else if (orphan_count == 4) {
      "#F2AD0E" #orange
    }     
    else if (orphan_count == 5) {
      "#F2210E" #red
    }
    else {
      "#000000" #black
    } 
    })
}

#add legend for icons
pal2 <- colorFactor(
  levels = c( '1', '2', '3', '4', '5', '6+'),
  palette = c('#0EF293', '#0E43F2', '#EAF20E', '#F2AD0E',  '#F2210E', '#000000'),
  domain = orphan_map$orphan_count
)

#create icons
icons <- awesomeIcons(
  icon = 'graduation-cap',
  iconColor = getColor(orphan_map),
  library = 'fa',
  markerColor = 'black'
)



map <- function(df_input) {    leaflet(df_input, height=1200, width=1020) %>% 
  addTiles()  %>%
  addAwesomeMarkers(lng=~lon, lat= ~lat, icon=icons,
                    popup = paste("Name: ", orphan_map$school_name_preload, " <br>",
                                  "Province: ", orphan_map$school_province_preload, " <br>",
                                  "District: ", orphan_map$school_district_preload, " <br>",
                                  "EMIS Code: ", orphan_map$school_emis_preload, " <br>",
                                  "<font color='red' > Number of Orphan Teachers ", " <br> <font color='black' >",
                                  "Orphan Teachers: ", orphan_map$orphan_count, " <br>"))   %>%
    addLegend("bottomright", pal=pal2, values=~orphan_count, title="Orphan Teachers"    )

}

```


```{r orphan_map_plot, eval=FALSE, include=FALSE}


linked_df_orphan<-SharedData$new(orphan_map)



bscols(widths=c(3,NA),
  list(
  filter_slider("orphans", "Orphan Teacher Count", linked_df_orphan, ~orphan_count),
  filter_select("prov", "Province", linked_df_orphan, ~school_province_preload),
  filter_select("reg", "District", linked_df_orphan, ~school_district_preload)
  
  ),
  map(linked_df_orphan) 

)

```


## Validation rules
Define set of rules for validating the data
```{r rules, echo=FALSE}
library(digest)
library(validate)
library(GGally)
#teacher effort
EFFT_rules <- validator(
  abs_minmax=in_range(absence_rate,0,100),
  sch_abs_minmax=in_range(sch_absence_rate,0,100),
  abs_nomiss=(!is.na(m2sbq6_efft) | teacher_available==2)
)

#content knowledge
CONT_rules <- validator(
  cont_minmax=in_range(content_knowledge,0,100),
  math_minmax=in_range(math_content_knowledge,0,100),
  lit_minmax=in_range(literacy_content_knowledge,0,100),
  math_lit_cor=cor(math_content_knowledge, literacy_content_knowledge, use="pairwise.complete.obs")>0.2
  )

#student attendance rules
ATTD_rules <- validator(
  attd_minmax=in_range(student_attendance,0,100),
  m4scq4_inpt<=m4scq12_inpt
)

#pedagogy rules
PEDG_rules <- validator(
  class_cult_minmax=in_range(classroom_culture,1,5),
  instruction_minmax=in_range(instruction,1,5),
  socio_emotional_skills_minmax=in_range(socio_emotional_skills,1,5),
  teach_score_minmax=in_range(teach_score,1,5),
  teach_sum_check=teach_score==(classroom_culture+instruction + socio_emotional_skills)/3
  
)

#4th grade learning
LERN_rules <- validator(
  mat_minmax=in_range(math_student_knowledge,0,100),
  li_minmax=in_range(literacy_student_knowledge,0,100),
  g4_minmax=in_range(student_knowledge,0,100),
  math_lit_cor=cor(math_student_knowledge, literacy_student_knowledge, use="pairwise.complete.obs")>0.2
)

#ECD rules

LCAP_rules <- validator(
  mat_minmax=in_range(ecd_math_student_knowledge,0,100),
  li_minmax=in_range(ecd_literacy_student_knowledge,0,100),
  ex_minmax=in_range(ecd_exec_student_knowledge,0,100),
  so_minmax=in_range(ecd_soc_student_knowledge,0,100),  
  g1_minmax=in_range(ecd_student_knowledge,0,100),
  math_lit_cor=cor(ecd_math_student_knowledge, ecd_literacy_student_knowledge, use="pairwise.complete.obs")>0.2,
  math_ex_cor=cor(ecd_math_student_knowledge, ecd_exec_student_knowledge, use="pairwise.complete.obs")>0.2,
  math_so_cor=cor(ecd_math_student_knowledge, ecd_soc_student_knowledge, use="pairwise.complete.obs")>0.2
)

#inputs
INPT_rules <- validator(
  blackboard_functional=in_range(blackboard_functional,0,1),
  pens_etc=in_range(pens_etc,0,1),
  textbooks=in_range(textbooks,0,1),
  share_desk=in_range(share_desk,0,1),
  used_ict=in_range(used_ict,0,1),
  access_ict=in_range(access_ict,0,1),
  input=in_range(inputs,0,5),
  textbook_pens_cor=cor(pens_etc, textbooks, use="pairwise.complete.obs")>0.2
)

#inputs
INFR_rules <- validator(
  drinking_water=in_range(drinking_water,0,1),
  functioning_toilet=in_range(functioning_toilet,0,1),
  internet=in_range(internet,0,1),
  class_electricity=in_range(class_electricity,0,1),
  disability_accessibility=in_range(disability_accessibility,0,1),
  infra=in_range(infrastructure,0,5),
  textbook_pens_cor=cor(pens_etc, textbooks, use="pairwise.complete.obs")>0.2
)

#operational management
OPMN_rules <- validator(
  vignette_1=in_range(vignette_1,0,2),
  vignette_2=in_range(vignette_2,0,2),
  operational_management=in_range(operational_management,1,5)
)

# Instructional Leadership
ILDR_rules <- validator(
  classroom_observed=in_range(classroom_observed,0,1),
  classroom_observed_recent=in_range(classroom_observed_recent,0,1),
  discussed_observation=in_range(discussed_observation,0,1),
  feedback_observation=in_range(feedback_observation,0,1),
  lesson_plan_w_feedback=in_range(lesson_plan_w_feedback,0,1),
  instructional_leadership=in_range(instructional_leadership,1,5)
)

# Principal knowledge
PKNW_rules <- validator(
  add_triple_digit_pknw=in_range(add_triple_digit_pknw,0,1),
  multiply_double_digit_pknw=in_range(multiply_double_digit_pknw,0,1),
  complete_sentence_pknw=in_range(complete_sentence_pknw,0,1),
  experience_pknw=in_range(experience_pknw,0,1),
  textbooks_pknw=in_range(textbooks_pknw,0,1),
  blackboard_pknw=in_range(blackboard_pknw,0,1),
  principal_knowledge_score=in_range(principal_knowledge_score,1,5)
)

# Principal knowledge
PMAN_rules <- validator(
  sch_goals_exist=in_range(sch_goals_exist,0,1),
  sch_goals_clear=in_range(sch_goals_clear,0,1),
  sch_goals_relevant=in_range(sch_goals_relevant,0,1),
  sch_goals_measured=in_range(sch_goals_measured,0,1),
  problem_solving_proactive=in_range(problem_solving_proactive,0,1),
  problem_solving_info_collect=in_range(problem_solving_info_collect,0,1),
  problem_solving_stomach=in_range(problem_solving_stomach,0,1),
  
  goal_setting=in_range(goal_setting,1,5),
  problem_solving=in_range(problem_solving,1,5),
  principal_management=in_range(principal_management,1,5)
  
)

# Teacher attraction
TATT_rules <- validator(
  teacher_satisfied_job=in_range(teacher_satisfied_job,0,1),
  teacher_satisfied_status=in_range(teacher_satisfied_status,0,1),
  better_teachers_promoted=in_range(better_teachers_promoted,0,1),
  teacher_bonus=in_range(teacher_bonus,0,1),
  salary_delays=in_range(salary_delays,0,12),
  teacher_attraction=in_range(teacher_attraction,1,5)
)

# Teacher Selection and Deployment
TSDP_rules <- validator(
  teacher_selection=in_range(teacher_selection,0,5),
  teacher_deployment=in_range(teacher_deployment,0,5),
  teacher_selection_deployment=in_range(teacher_selection_deployment,1,5)
)

# Teacher Support

TSUP_rules <- validator(
  pre_training_exists=in_range(pre_training_exists,0,.5),
  pre_training_useful=in_range(pre_training_useful,0,.5),
  pre_service=in_range(pre_service,0,1),
  pre_training_practicum=in_range(pre_training_practicum,0,.5),
  pre_training_practicum_lngth=in_range(pre_training_practicum_lngth,0,.5),
  practicum=in_range(practicum,0,1),
  in_service_exists=in_range(in_service_exists,0,1),
  in_service_classroom=in_range(in_service_classroom,0,1),
  pre_training_practicum_lngth=in_range(pre_training_practicum_lngth,0,.5),
  in_service=in_range(in_service,0,1),
  
  teacher_support=in_range(teacher_support,1,5)
)

# Teacher Evaluation

TEVL_rules <- validator(
  formally_evaluated=in_range(formally_evaluated,0,1),
  evaluation_content=in_range(evaluation_content,0,1),
  negative_consequences=in_range(negative_consequences,0,1),
  positive_consequences=in_range(positive_consequences,0,1),
  teaching_evaluation=in_range(teaching_evaluation,1,5)
)

TMNA_rules <- validator(
  attendance_evaluated=in_range(attendance_evaluated,0,1),
  attendance_rewarded=in_range(attendance_rewarded,0,1),
  attendence_sanctions=in_range(attendence_sanctions,0,1),
  miss_class_admin=in_range(miss_class_admin,0,1),
  teacher_monitoring=in_range(teacher_monitoring,1,5)
)

TINM_rules <- validator(
  acceptable_absent=in_range(acceptable_absent,1,5),
  students_deserve_attention=in_range(students_deserve_attention,1,5),
  growth_mindset=in_range(growth_mindset,1,5),
  motivation_teaching=in_range(motivation_teaching,0,1),
  reason_teaching=in_range(bin_var(m3sdq2_tmna,1),0,1),
  intrinsic_motivation=in_range(intrinsic_motivation,1,5)
)

# Input Standards
ISTD_rules <- validator(
  standards_monitoring_input=in_range(standards_monitoring_input,0,1),
  standards_monitoring_infrastructure=in_range(standards_monitoring_infrastructure,0,1),
  standards_monitoring=in_range(standards_monitoring,1,5)
)
# Input Monitoring
IMON_rules <- validator(
  monitoring_inputs=in_range(monitoring_inputs,0,1),
  monitoring_infrastructure=in_range(monitoring_infrastructure,0,1),
  system_in_place=in_range(system_in_place,0,1),
  parents_involved=in_range(parents_involved,0,1),  
  sch_monitoring=in_range(sch_monitoring,1,5)
)

#clarity of functions
SCFN_rules <- validator(
  infrastructure_scfn=in_range(infrastructure_scfn,0,1),
  materials_scfn=in_range(materials_scfn,0,1),
  hiring_scfn=in_range(hiring_scfn,0,1),
  supervision_scfn=in_range(supervision_scfn,0,1),  
  student_scfn=in_range(student_scfn,0,1),  
  principal_hiring_scfn=in_range(principal_hiring_scfn,0,1),  
  supervision_scfn=in_range(supervision_scfn,0,1),  
  sch_management_clarity=in_range(sch_management_clarity,1,5)
)

SATT_rules <- validator(
  principal_satisfaction=in_range(principal_satisfaction,1,5),
  principal_salary=principal_salary>0,
  principal_salary_score=in_range(principal_salary_score,1,5),
  sch_management_attraction=in_range(sch_management_attraction,1,5)
)

SSLD_rules <- validator(
  sch_selection_deployment=in_range(sch_selection_deployment,1,5)
)

SSUP_rules <- validator(
  prinicipal_trained=in_range(prinicipal_trained,0,1),
  principal_training=in_range(principal_training,0,1),
  principal_used_skills=in_range(principal_used_skills,0,1),
  principal_offered=in_range(principal_offered,0,1),
  sch_support=in_range(sch_support,1,5)
)

SEVL_rules <- validator(
  principal_formally_evaluated=in_range(principal_formally_evaluated,0,1),
  principal_evaluation_multiple=in_range(principal_evaluation_multiple,0,1),
  principal_negative_consequences=in_range(principal_negative_consequences,0,1),
  principal_positive_consequences=in_range(principal_positive_consequences,0,1),
  principal_evaluation=in_range(principal_evaluation,1,5)
)
```

## a) Teacher absence
```{r teacher absence, echo=FALSE}
#validate 
out <- confront(teacher_absence_dta, EFFT_rules)
summary(out)
plot(out)
```

## b) Student attendance
```{r student absence, echo=FALSE}
#validate
out <- confront(final_indicator_data_CONT, CONT_rules)
summary(out)
plot(out)
```

## c) Content knowledge teachers
```{r content knowledge teachers, echo=FALSE}
#validate
out <- confront(final_indicator_data_CONT, CONT_rules)
summary(out)
plot(out)
```

## d) Student assessment 4th grade
```{r student learning outcomes, echo=FALSE}
#validate 
out <- confront(assess_4th_grade_dta, LERN_rules)
summary(out)
plot(out)
```

## e) ECD assessment 1th grade
```{r ECD learning outcomes, echo=FALSE}
#validate 
out <- confront(ecd_dta_anon, LCAP_rules)
summary(out)
plot(out)
```




