---
title: "Analysis of Callbacks to Absent Teachers - Jordan 2019"
author: "Brian Stacy"
date: "2/26/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(haven)
library(DDIwR)
library(kableExtra)
library(skimr)
library(Hmisc)
```

# Introduction

In Jordan, a number of teachers that we selected to interview were absent, and as a result, we could not collect their information in the school.  In these cases, replacement teachers were selected and these replacement teachers were interviewed.  If a teacher was absent, we asked the enumerators to record their phone numbers, so that we could contact them with a follow up.  The survey firm then contacted randomly 35 teachers and asked them a set of questions.

In what follows, we will explore whether teachers that were absent systematically differ from teachers that were present to answer the survey by comparing their answers to the same set of questions.


```{r data, include=FALSE}

#set directory to bring in data

work_dir<- "//wbgfscifs01/GEDEDU/datalib-edu/Projects/GEPD-Confidential/CNT/JOR/JOR_2019_GEPD/JOR_2019_GEPD_v01_RAW/Data/"


#load follow up survey data
follow_up<-read_dta(paste(work_dir, "raw/Phone_Survey/CallTeacher.dta", sep=""))
follow_up_code<-  readxl::read_excel(paste(work_dir, "raw/Phone_Survey/[emis]Phone Survey Absent Teachers.xlsx", sep="")) %>% 
  mutate(emiscode=id,
         school_code=text)


#add school codes back into data
follow_up <- follow_up %>%
  left_join(follow_up_code) %>%
  select(-parentid, -text, -id, -m3seq7_tatt)

#load ddi
follow_up_ddi<-getMetadata(paste(work_dir, "raw/Phone_Survey/CallTeacher_1_DDI_All/fba968ae612b4c099443a8426f9a2d95$1_ddi.xml", sep=""))$dataDscr

# this converts each set of <record> columns to a data frame
# after first converting each row to numeric and assigning
# names to each column (making it easier to do the matrix to data frame conv)
  follow_up_ddi_df<-follow_up_ddi %>%
  map_df(~data.frame(unlist(.))[1,])
  
  follow_up_ddi_df<-data.frame(t(follow_up_ddi_df)) %>%
    rownames_to_column() %>%
    rename(variable=1,
           varlabel=2)




#load school data for comparisons
load(paste(work_dir, "confidential/School/school_survey_data.RData", sep=""))


teacher_questionnaire_present<- teacher_questionnaire %>%
  select(school_code, colnames(follow_up)[grep("m3s", colnames(follow_up))]) %>%
  select(-contains("_other")) %>%
    mutate_all( ~case_when(
      .x==900 ~ as.numeric(NA),              
      .x==998 ~ as.numeric(NA),
      .x==99 ~ as.numeric(NA),
      .x==98 ~ as.numeric(NA),
      is.na(.x) ~ as.numeric(NA),
      TRUE ~  as.numeric(.x)))

#Create a function which will generate new binary variable using case_when, but 
#if value is misisng it will generate binary variable to be missing
#This is done a lot so will create function for it.
#e.g. school_absent=case_when(
#         m2sbq6_efft==6  ~ 1,
#         m2sbq6_efft!=6   ~ 0,
#         is.na(m2sbq6_efft) ~ as.numeric(NA))
bin_var <- function(var, val) {
  case_when(
    var==val  ~ 1,
    var!=val   ~ 0,
    is.na(var) ~ as.numeric(NA))
}

#create function to wrap text
wrapper <- function(x, ...) 
{
  paste(strwrap(x, ...), collapse = "\n")
}

```


```{r sample_weights, include=FALSE}
#define function to create weights for summary statistics
project_folder <- "//wbgfscifs01/GEDEDU/datalib-edu/Projects/GEPD-Confidential/CNT"
country<-"JOR"
year<-"2019"
#Load original sample of schools
currentDate<-c("2019-10-11")
sample_folder <- file.path(paste(project_folder,country,paste(country,year,"GEPD", sep="_"),paste(country,year,"GEPD_v01_RAW", sep="_"),"Data/sampling/", sep="/"))
sample_frame_name <- paste(sample_folder,"/school_sample_",currentDate,".RData", sep="")

load(sample_frame_name)


df_weights_function <- function(dataset,scode, snumber, prov) {
  scode<-enquo(scode)  
  snumber<-enquo(snumber)
  prov<-enquo(prov)
  
  dataset %>%
    mutate(!! scode := as.numeric(.data$school_code)) %>%
    left_join(data_set_updated) %>%
    mutate(ipw=if_else(is.na(.data$weights), median(.data$weights, na.rm=T), .data$weights)*!! snumber ) %>%
    mutate(province=governorate) %>%
    select(-one_of(colnames(data_set_updated[, -which(names(data_set_updated) == "rural" | names(data_set_updated) == "governorate" | names(data_set_updated) == "province" |
                                                        names(data_set_updated) == "foundation_period" | names(data_set_updated) == "territory")])))
}

teacher_questionnaire_present<-df_weights_function(teacher_questionnaire_present, organization_code, total_students_grade_4, governorate)


follow_up<-follow_up %>%
  select(school_code, colnames(follow_up)[grep("m3s", colnames(follow_up))]) %>%
  select(-contains("_other")) %>%
      mutate_all( ~case_when(
      .x==900 ~ as.numeric(NA),              
      .x==998 ~ as.numeric(NA),
      .x==99 ~ as.numeric(NA),
      .x==98 ~ as.numeric(NA),
      is.na(.x) ~ as.numeric(NA),
      TRUE ~  as.numeric(.x))) %>%
  df_weights_function( organization_code, total_students_grade_4, governorate)

```


# Questions Asked in Follow Up

- Below are the questions asked to teachers by phone as part of the follow up.

```{r questions, echo=FALSE}

follow_up_ddi_df %>%
  kable(caption="Questions Asked to Teachers in Follow Up Survey",
        col.names=c("Question ID", "Question Text")) %>%
  kable_styling("striped")


```

# Comparison of Means for Teachers Sampled and Follow up Teachers


```{r summary_stats, include=FALSE}



    #add function to produce weighted summary stats
      my_skim<-    skim_with( numeric = sfl( mean = ~ wtd.mean(.,  w=sch_ipw, na.rm=TRUE),
                                             sd = ~ sqrt(wtd.var(.,  weights=sch_ipw, na.rm=TRUE)),
                                             p25 = ~ (wtd.quantile(., probs=c(0.25),  weights=sch_ipw, na.rm=TRUE)),
                                             p50 = ~ (wtd.quantile(., probs=c(0.5), weights=sch_ipw, na.rm=TRUE)),
                                             p75 = ~ (wtd.quantile(., probs=c(0.75), weights=sch_ipw, na.rm=TRUE)),
                                             complete = ~ sum(!is.na(.))))


    
    
    sch_ipw<-teacher_questionnaire_present$ipw 

    #add variable label
    sumstats_teacher_df <- my_skim(teacher_questionnaire_present) %>%
            yank("numeric") %>%
      mutate(variable=skim_variable) %>%
      select(variable, mean, sd, p0, p25, p50, p75, p100, complete,  hist) %>%
      filter(variable!="school_code") %>%
      left_join(follow_up_ddi_df) %>%
      mutate(ci_low=as.numeric(mean)-1.96*(as.numeric(sd)/sqrt(as.numeric(complete))),
             ci_high=as.numeric(mean)+1.96*(as.numeric(sd)/sqrt(as.numeric(complete)))) %>%
      mutate(ci=paste("[",round(ci_low,2),", ", round(ci_high,2),"]", sep="")) %>%
      select(varlabel, mean, ci, complete)
 
    
    
    #now get frame with teachers in same school as follow up teachers
    teacher_questionnaire_present_same <- teacher_questionnaire_present %>%
      filter(school_code %in% unique(follow_up$school_code))
    
        sch_ipw<-teacher_questionnaire_present_same$ipw 

        sumstats_teacher_same_df <- my_skim(teacher_questionnaire_present_same) %>%
            yank("numeric") %>%
      mutate(variable=skim_variable) %>%
      select(variable, mean, sd, p0, p25, p50, p75, p100, complete,  hist) %>%
      filter(variable!="school_code") %>%
      left_join(follow_up_ddi_df) %>%
      mutate(ci_low=as.numeric(mean)-1.96*(as.numeric(sd)/sqrt(as.numeric(complete))),
             ci_high=as.numeric(mean)+1.96*(as.numeric(sd)/sqrt(as.numeric(complete)))) %>%
      mutate(ci=paste("[",round(ci_low,2),", ", round(ci_high,2),"]", sep="")) %>%
      mutate(mean_same=mean,
             ci_same=ci, 
             complete_same=complete) %>%
      select(varlabel, mean_same, ci_same, complete_same)
    
    sch_ipw<-follow_up$ipw 
    
    #add variable label
    sumstats_follow_up_df <- my_skim(follow_up) %>%
            yank("numeric") %>%
      mutate(variable=skim_variable) %>%
      select(variable, mean, sd, p0, p25, p50, p75, p100, complete,  hist) %>%
      filter(variable!="school_code") %>%
      left_join(follow_up_ddi_df) %>%
      mutate(ci_low=as.numeric(mean)-1.96*(as.numeric(sd)/sqrt(as.numeric(complete))),
             ci_high=as.numeric(mean)+1.96*(as.numeric(sd)/sqrt(as.numeric(complete)))) %>%
      mutate(ci=paste("[",round(ci_low,2),", ", round(ci_high,2),"]", sep="")) %>%
      mutate(mean_follow=mean,
             ci_follow=ci, 
             complete_follow=complete) %>%
      select(varlabel, mean_follow, ci_follow, complete_follow)    
      
    sumstats<-sumstats_teacher_df %>%
            left_join(sumstats_teacher_same_df) %>%
      left_join(sumstats_follow_up_df)
    

```


```{r sumstats_table, echo=FALSE}

  sumstats %>%
    kable(caption = "Summary Statistics of Questions by Teacher Type (Sampled/Follow up)",
          col.names = c("Indicator", "Mean", "95% Confident Interval", "Count", "Mean", "95% Confident Interval", "Count", "Mean", "95% Confident Interval", "Count"),
          digits = 2, 
          escape=F) %>%
    kable_styling("striped") %>%
    add_header_above(c(" "=1, "Sampled Teachers"=3, "Sampled Teachers in Follow Up Schools"=3,"Follow Up Teachers"=3))


```

