---
title: "Dashboard Cut Score Meeting"
author: "Brian Stacy"
institute: "Global Education Policy Dashboard"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    fig_width: 5
    fig_height: 4
    fig_caption: true
---


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(tidyverse)
library(haven)
library(mirt)
library(equateIRT)
library(skimr)
library(DT)
library(knitr)
library(kableExtra)
library(captioner)
library(ggcorrplot)
library(plotly)
library(psych)
library(crosstalk)
library(RColorBrewer)
library(data.table)
library(ggridges)
library(Hmisc)
library(psych) # For Cronbach's alpha
library(lavaan) # For Confirmatory Factor Analysis
library(spatstat)
library(ggpubr)
library(crosstalk)
```



```{r include=FALSE}

#===============
# GET DATA
#===============

#set directory:
work_dir<-"C:/Users/wb469649/OneDrive - WBG/4th Grade Assessment - Dashboard - To Share/"

#Create function to save metadata for each question in each module
#The attr function retrieves metadata imported by haven. E.g. attr(school_dta$m1s0q2_code, "label")
makeVlist <- function(dta) { 
  varlabels <- sapply(dta, function(x) attr(x,"label"))
  vallabels <- sapply(dta, function(x) attr(x,"labels"))
  tibble(name = names(varlabels),
         varlabel = varlabels, vallabel = vallabels) 
}


#load data
########
#jordan
#######
load(file=paste(work_dir, 'Data/dashboard_4th_grade_assessment_data_jordan.RData', sep=""))
assess_4th_grade_anon_jordan <- assess_4th_grade_anon
#Load original sample of schools
currentDate<-c("2019-10-11")

sample_frame_name <- paste("C:/Users/WB469649/WBG/Ezequiel Molina - Dashboard (Team Folder)/Country_Work/Jordan/2019/Data/Sampling/school_sample_",currentDate,".RData", sep="")

load(sample_frame_name)
data_set_updated_jordan <- data_set_updated

########
# Peru
########
load(file=paste(work_dir, 'Data/dashboard_4th_grade_assessment_data_peru.RData', sep=""))

#Load original sample of schools
currentDate<-c("2019-07-22")
sample_frame_name <- paste("C:/Users/WB469649/WBG/Ezequiel Molina - Dashboard (Team Folder)/Country_Work/Peru/2019/Data/sampling/school_sample_",currentDate,".RData", sep="")

load(sample_frame_name)
#function to create zero/one variables  
bin_var <- function(var, val) {
  case_when(
    var==val  ~ 1,
    var!=val   ~ 0,
    is.na(var) ~ as.numeric(NA))
}

bin_var_NA0 <- function(var, val) {
  case_when(
    var==val  ~ 1,
    var!=val   ~ 0,
    is.na(var) ~ 0)
}

#create function to make titles in figures nice
wrapper <- function(x, ...) 
{
  paste(strwrap(x, ...), collapse = "\n")
}

#produce caption for tables/figures
  tab_num<-captioner(prefix="Table")
  fig_num<-captioner(prefix="Figure")

  
#get weights from original sample
assess_4th_grade_weights <- assess_4th_grade_anon %>%
  group_by(school_code) %>%
  mutate(total_sampled=n()) %>%
  ungroup() %>%
  mutate(codigo.modular=as.numeric(school_code)) %>%
  left_join(data_set_updated) %>%
  mutate( school_ipw=weights*total_4th/total_sampled)  %>%
  mutate(school_ipw=if_else(is.na(school_ipw), median(school_ipw, na.rm=T), school_ipw)) %>%
  select(colnames(assess_4th_grade_anon), school_ipw, total_sampled, departamento)
  
assess_4th_grade_weight_vec <- assess_4th_grade_weights$school_ipw


#get weights from original sample
assess_4th_grade_weights_jordan <- assess_4th_grade_anon_jordan %>%
  group_by(school_code) %>%
  mutate(total_sampled=n()) %>%
  ungroup() %>%
  mutate(organization_code=as.numeric(school_code)) %>%
  left_join(data_set_updated_jordan) %>%
  mutate( school_ipw=weights*total_students_grade_4/total_sampled)  %>%
  mutate(school_ipw=if_else(is.na(school_ipw), median(school_ipw, na.rm=T), school_ipw)) %>%
  select(colnames(assess_4th_grade_anon_jordan), school_ipw, total_sampled, governorate)
  
assess_4th_grade_weight_vec_jordan <- assess_4th_grade_weights_jordan$school_ipw 


#add function to produce weighted summary stats
skim_with( numeric = list( mean = ~ wtd.mean(.,  w=school_ipw, na.rm=TRUE),
                                     sd = ~ sqrt(wtd.var(.,  weights=school_ipw, na.rm=TRUE)),
                                     p25 = ~ (wtd.quantile(., probs=c(0.25),  weights=school_ipw, na.rm=TRUE)),
                                     p50 = ~ (wtd.quantile(., probs=c(0.5), weights=school_ipw, na.rm=TRUE)),
                                     p75 = ~ (wtd.quantile(., probs=c(0.75), weights=school_ipw, na.rm=TRUE)),
                                     complete_count= ~ sum(!is.na(.))))


#rename a few variables to be consistent with sub_domain tags
assess_4th_grade_weights <- assess_4th_grade_weights %>%
  mutate(m8saq2_letters=m8saq2_id,
         m8saq3_words=m8saq3_id,
         m8saq4_words=m8saq4_id,
         m8saq5_comprehension=m8saq5_story,
         m8saq6_comprehension=m8saq6_story,
         m8saq7_comprehension=m8saq7_word_choice
         )
#rename a few variables to be consistent with sub_domain tags
assess_4th_grade_weights_jordan <- assess_4th_grade_weights_jordan %>%
  mutate(m8saq2_letters=m8saq2_id,
         m8saq3_words=m8saq3_id,
         m8saq4_words=m8saq4_id,
         m8saq5_comprehension=m8saq5_story,
         m8saq6_comprehension=m8saq6_story,
         m8saq7_comprehension=m8saq7_word_choice
         )
#score each sub-domain
sub_domains <- c('letters','words','comprehension', 'gir',
                 'number_sense','arithmetic','word_problem', 'sequences')

#create function to score each sub-domain
sub_domain_scorer <- function(subdomain, df) {
     rowMeans(df[grep(x=colnames(df), 
                                              pattern=subdomain)], na.rm=TRUE)
}

assess_4th_grade_domains_jordan <- cbind(assess_4th_grade_weights_jordan, setNames(lapply(sub_domains, sub_domain_scorer, assess_4th_grade_weights_jordan),sub_domains))

assess_4th_grade_domains <- cbind(assess_4th_grade_weights, setNames(lapply(sub_domains, sub_domain_scorer, assess_4th_grade_weights),sub_domains))


```

# Introduction

- GEPD Data from Peru & Jordan
  - Full data collect in Peru
    -- 2,681 students assessed in 204 schools
  - Partial data collected in Jordan
    -- 3,298 students assessed in 130 schools 
    
- Goal:
  - Determine Cut-scores for proficient in 4th grade assessment

- Proposal:
  - Based on Standard Setting Exercise from Various Experts
  - Literacy cutscore: 
      - Student scores 19 correct/24 items
      - Student scores 8 correct/13 items without Lonely Giraffe items
  - Math cutscore: 
      - Student scores 14 correct/17 items
      
---
# Key Takeaways

- Under proposed cut score
- In Peru: 
    - 89% of students proficient in language
    - 26% of students proficient in math
    
- In Jordan:
    - 41% of students proficient in language (so far)
    - 3% of students proficient in math (so far)
---


# Overview of GEPD 4th Grade Assessment

13-24 Literacy Items: 
- Letter Identification (3 items)
-	Word Recognition (7 items)
-	Reading Comprehension Story (3 items)
- Giraffe Comprehension Story (only Jordan so far) (11 items) 
    - 5 items 4th grade appropriate

15 Math Items:
-	Number Sense (4 items)
-	Arithmetic (11 items) 
    - 4 items 4th grade appropriate
-	Word Problem (1 item)
    - 1 item 4th grade appropriate
-	Sequences (1 item)
    - 1 item 4th grade appropriate

---
class: inverse, middle, center

Summary Statistics from Peru and Jordan
---


# Literacy Domain Scores - Peru


```{r sumstats_domains_lit, echo=FALSE, message=FALSE, warning=FALSE}

assess_4th_grade_domains_lit <-assess_4th_grade_domains %>%
  select( student_knowledge,
          literacy_student_knowledge, letters,words,comprehension) %>%
  mutate(letters=100*letters,
         words=100*words,
         comprehension=100*comprehension)


name<-c('student_knowledge','literacy_student_knowledge',
        'letters','words','comprehension' )
varlabel<-c('Fraction correct overall',
            'Fraction correct Literacy', 'Letter Identification','Word Recognition','Reading Comprehension Story')

assess_4th_grade_domains_metadata <- cbind.data.frame(name, varlabel)


#language
  school_ipw <- assess_4th_grade_weight_vec
 sumstats_assess_4th_grade_domains_df<-skim(assess_4th_grade_domains_lit) %>%
     dplyr::select(-level, -type, -value) %>%
     spread(stat, formatted) %>%
     dplyr::select(variable, mean, sd, p0, p25, p50, p75, p100, complete, missing, hist) 

  #add variable label
  sumstats_assess_4th_grade_domains_df_lit <- sumstats_assess_4th_grade_domains_df %>%
      mutate(name=variable) %>%
      left_join(assess_4th_grade_domains_metadata) %>%
      dplyr::select(variable, varlabel, mean, sd, hist) %>%
      arrange(factor(variable, levels=name)) %>%
      dplyr::select( varlabel, mean, sd, hist) 
  
  
  #produce caption for table
  assess_4th_grade_sumstats_domain_cap_lit<-tab_num(name="assess_4th_grade_stats_domain_lit", caption="Summary Statistics of Percentage Correct on Literacy 4th Grade Assessment Domains - Peru")
  
  #Produce table
  sumstats_assess_4th_grade_domains_df_lit %>%
    kable(caption=assess_4th_grade_sumstats_domain_cap_lit,
          col.names =c( "Label", "Mean",  "Std Dev", "Histogram")
) %>%
    kable_styling(bootstrap_options = c("striped", "hover"),
                  fixed_thead = T,
                  ) %>%
  pack_rows("Overall", 1,1) %>%
  pack_rows("Literacy", 2,5) %>%
    footnote(general="Summary table shows weighted summary statistics from 4th Grade assessment.")
 

```


---
# Literacy Domain Scores - Jordan




```{r sumstats_domains_lit_jordan, echo=FALSE, message=FALSE, warning=FALSE}

assess_4th_grade_domains_lit <-assess_4th_grade_domains_jordan %>%
  select( student_knowledge,
          literacy_student_knowledge, letters,words,comprehension, gir) %>%
  mutate(letters=100*letters,
         words=100*words,
         comprehension=100*comprehension,
         gir=100*gir)


name<-c('student_knowledge','literacy_student_knowledge',
        'letters','words','comprehension', 'gir' )
varlabel<-c('Fraction correct overall',
            'Fraction correct Literacy', 'Letter Identification','Word Recognition','Reading Comprehension Story', 'Giraffe Story')

assess_4th_grade_domains_metadata <- cbind.data.frame(name, varlabel)


#language
  school_ipw <- assess_4th_grade_weight_vec_jordan
 sumstats_assess_4th_grade_domains_df<-skim(assess_4th_grade_domains_lit) %>%
     dplyr::select(-level, -type, -value) %>%
     spread(stat, formatted) %>%
     dplyr::select(variable, mean, sd, p0, p25, p50, p75, p100, complete, missing, hist) 

  #add variable label
  sumstats_assess_4th_grade_domains_df_lit <- sumstats_assess_4th_grade_domains_df %>%
      mutate(name=variable) %>%
      left_join(assess_4th_grade_domains_metadata) %>%
      dplyr::select(variable, varlabel, mean, sd, hist) %>%
      arrange(factor(variable, levels=name)) %>%
      dplyr::select( varlabel, mean, sd, hist) 

  
  
  #produce caption for table
  assess_4th_grade_sumstats_domain_cap_lit_jor<-tab_num(name="assess_4th_grade_stats_domain_lit_jor", caption="Summary Statistics of Percentage Correct on Literacy 4th Grade Assessment Domains - Jordan")
  
  #Produce table
  sumstats_assess_4th_grade_domains_df_lit %>%
    kable(caption=assess_4th_grade_sumstats_domain_cap_lit_jor,
          col.names =c( "Label", "Mean", "Std Dev", "Histogram")) %>%
    kable_styling(bootstrap_options = c("striped", "hover"),
                  fixed_thead = T,
                  ) %>%
  pack_rows("Overall", 1,1) %>%
  pack_rows("Literacy", 2,6) %>%
    footnote(general="Summary table shows weighted summary statistics from 4th Grade assessment.")
 

```
---
# Math Domain Scores - Peru



```{r sumstats_domains, echo=FALSE, message=FALSE, warning=FALSE}

assess_4th_grade_domains <-assess_4th_grade_domains %>%
  select( student_knowledge,
          math_student_knowledge, number_sense,arithmetic,word_problem, sequences) %>%
    mutate(number_sense=100*number_sense,
         arithmetic=100*arithmetic,
         word_problem=100*word_problem,
         sequences=100*sequences)


name<-c('student_knowledge',
        'math_student_knowledge', 'number_sense','arithmetic','word_problem', 'sequences')
varlabel<-c('Fraction correct overall',
            'Fraction correct Numeracy', 'Number Sense','Arithmetic','Word Problem', 'Sequences')

assess_4th_grade_domains_metadata <- cbind.data.frame(name, varlabel)


#language
  school_ipw <- assess_4th_grade_weight_vec
 sumstats_assess_4th_grade_domains_df<-skim(assess_4th_grade_domains) %>%
     dplyr::select(-level, -type, -value) %>%
     spread(stat, formatted) %>%
     dplyr::select(variable, mean, sd, p0, p25, p50, p75, p100, complete, missing, hist) 

  #add variable label
  sumstats_assess_4th_grade_domains_df <- sumstats_assess_4th_grade_domains_df %>%
      mutate(name=variable) %>%
      left_join(assess_4th_grade_domains_metadata) %>%
      dplyr::select(variable,  varlabel, mean, sd, hist) %>%
      arrange(factor(variable, levels=name)) %>%
      dplyr::select(varlabel, mean, sd, hist) 

  
  
  #produce caption for table
  assess_4th_grade_sumstats_domain_cap<-tab_num(name="assess_4th_grade_stats_domain", caption="Summary Statistics of Percentage Correct on Math 4th Grade Assessment Domains - Peru")
  
  #Produce table
  sumstats_assess_4th_grade_domains_df %>%
    kable(caption=assess_4th_grade_sumstats_domain_cap,
          col.names =c("Label", "Mean", "Std Dev", "Histogram")
) %>%
    kable_styling(bootstrap_options = c("striped", "hover"),
                  fixed_thead = T,
                  ) %>%
  pack_rows("Overall", 1,1) %>%
  pack_rows("Math", 2,6) %>%
    footnote(general="Summary table shows weighted summary statistics from 4th Grade assessment.")
 

```

---
# Math Domain Scores - Jordan

```{r sumstats_domains_jordan, echo=FALSE, message=FALSE, warning=FALSE}

assess_4th_grade_domains <-assess_4th_grade_domains_jordan %>%
  select( student_knowledge,
          math_student_knowledge, number_sense,arithmetic,word_problem, sequences) %>%
    mutate(number_sense=100*number_sense,
         arithmetic=100*arithmetic,
         word_problem=100*word_problem,
         sequences=100*sequences)


name<-c('student_knowledge',
        'math_student_knowledge', 'number_sense','arithmetic','word_problem', 'sequences')
varlabel<-c('Fraction correct overall',
            'Fraction correct Numeracy', 'Number Sense','Arithmetic','Word Problem', 'Sequences')

assess_4th_grade_domains_metadata <- cbind.data.frame(name, varlabel)


#language
  school_ipw <- assess_4th_grade_weight_vec_jordan
 sumstats_assess_4th_grade_domains_df<-skim(assess_4th_grade_domains) %>%
     dplyr::select(-level, -type, -value) %>%
     spread(stat, formatted) %>%
     dplyr::select(variable, mean, sd, p0, p25, p50, p75, p100, complete, missing, hist) 

  #add variable label
  sumstats_assess_4th_grade_domains_df <- sumstats_assess_4th_grade_domains_df %>%
      mutate(name=variable) %>%
      left_join(assess_4th_grade_domains_metadata) %>%
      dplyr::select(variable,  varlabel, mean, sd, hist) %>%
      arrange(factor(variable, levels=name)) %>%
      dplyr::select(varlabel, mean, sd, hist) 

  
  
  #produce caption for table
  assess_4th_grade_sumstats_domain_cap_jor<-tab_num(name="assess_4th_grade_stats_domain_jor", caption="Summary Statistics of Percentage Correct on Math 4th Grade Assessment Domains - Jordan")
  
  #Produce table
  sumstats_assess_4th_grade_domains_df %>%
    kable(caption=assess_4th_grade_sumstats_domain_cap_jor,
          col.names =c("Label", "Mean", "Std Dev", "Histogram")
) %>%
    kable_styling(bootstrap_options = c("striped", "hover"),
                  fixed_thead = T,
                  ) %>%
  pack_rows("Overall", 1,1) %>%
  pack_rows("Math", 2,6) %>%
    footnote(general="Summary table shows weighted summary statistics from 4th Grade assessment.")
 

```

---
class: inverse, middle, center

Proficiency Rates Based on Alternate Cutscores from Peru and Jordan
---



# Literacy Cut Scores - Peru



```{r lang_cutscore_sumstats_peru,fig.height=6, fig.width=8, echo=FALSE}

#create matrix with  just item responses
math <- assess_4th_grade_anon %>%
  select(contains('m8sb')) %>%
  mutate(m8sbq1_number_sense=as.numeric(m8sbq1_number_sense==1)) %>%
  mutate_all(~bin_var_NA0(.,1))

language <- assess_4th_grade_anon %>%
  select(contains('m8sa')) %>%
  mutate(m8saq2_id=as.numeric(m8saq2_id==1),
         m8saq3_id=as.numeric(m8saq3_id==1),
         m8saq4_id=as.numeric(m8saq4_id==1)) %>%
  mutate_all(~bin_var_NA0(.,1))

lang2_peru<-language %>%
  mutate(m8saq2_id=m8saq2_id*3,
         m8saq3_id=m8saq3_id*3,
         m8saq4_id=m8saq4_id*4)

num_correct <- rowSums(lang2_peru, na.rm=T)

lang_cutscores_peru <- data.frame(lang2_peru, num_correct, school_ipw)


  lang_cutscores_peru <- lang_cutscores_peru %>%
  transmute(
            cut_score_13=as.numeric(num_correct>=13),
            cut_score_12=as.numeric(num_correct>=12),
            cut_score_11=as.numeric(num_correct>=11),
            cut_score_10=as.numeric(num_correct>=10),
            cut_score_9=as.numeric(num_correct>=9),
            cut_score_8=as.numeric(num_correct>=8),
            cut_score_7=as.numeric(num_correct>=7),
            cut_score_6=as.numeric(num_correct>=6),
            cut_score_5=as.numeric(num_correct>=5),
            cut_score_4=as.numeric(num_correct>=4),
            cut_score_3=as.numeric(num_correct>=3),
            cut_score_2=as.numeric(num_correct>=2),
            cut_score_1=as.numeric(num_correct>=1)) %>%
  summarise_all(~wtd.mean(.,  w=school_ipw, na.rm=TRUE)) %>%
  pivot_longer(cols=starts_with('cut_score_'),
               names_to = 'cutscore',
               names_prefix = 'cut_score_',
               values_to = 'scores') %>%
  mutate(cutscore=as.numeric(cutscore))

  
prob_plot_proficient<- ggplot(data=lang_cutscores_peru, aes(x=cutscore, y=scores, label=round(scores,2))) +
  geom_point() +
  geom_text(hjust=1.6,vjust=0.6) +
  theme_light() +
  expand_limits(x = 0, y = 0) +
  geom_vline(xintercept=8, linetype="dashed", color = "red") +
  scale_x_continuous(name="Cutscore Threshold", breaks=c(1,3,5,7,9,11,13,15, 17))+
  theme(axis.title.y = element_blank()) +
  ggtitle(str_wrap("Literacy Fraction Proficient Based on Alternative Cutscore Thresholds - Peru", 60))
  
 prob_plot_proficient


```

---
# Literacy Cut Scores - Jordan



```{r lang_cutscore_sumstats_jordan,fig.height=6, fig.width=8, echo=FALSE}

#create matrix with  just item responses


language <- assess_4th_grade_anon_jordan %>%
  select(contains('m8sa')) %>%
  mutate(m8saq2_id=as.numeric(m8saq2_id==1),
         m8saq3_id=as.numeric(m8saq3_id==1),
         m8saq4_id=as.numeric(m8saq4_id==1)) %>%
  mutate_all(~bin_var_NA0(.,1))

lang2_jordan<-language %>%
  mutate(m8saq2_id=m8saq2_id*3,
         m8saq3_id=m8saq3_id*3,
         m8saq4_id=m8saq4_id*4)

num_correct <- rowSums(lang2_jordan, na.rm=T)

lang_cutscores_jordan <- data.frame(lang2_jordan, num_correct, school_ipw)


  lang_cutscores_jordan <- lang_cutscores_jordan %>%
  transmute(cut_score_24=as.numeric(num_correct>=24),
            cut_score_23=as.numeric(num_correct>=23),
            cut_score_22=as.numeric(num_correct>=22),
            cut_score_21=as.numeric(num_correct>=21),
            cut_score_20=as.numeric(num_correct>=20),
            cut_score_19=as.numeric(num_correct>=19),
            cut_score_18=as.numeric(num_correct>=18),
            cut_score_17=as.numeric(num_correct>=17),
            cut_score_16=as.numeric(num_correct>=16),
            cut_score_15=as.numeric(num_correct>=15),                        
            cut_score_14=as.numeric(num_correct>=14),
            cut_score_13=as.numeric(num_correct>=13),
            cut_score_12=as.numeric(num_correct>=12),
            cut_score_11=as.numeric(num_correct>=11),
            cut_score_10=as.numeric(num_correct>=10),
            cut_score_9=as.numeric(num_correct>=9),
            cut_score_8=as.numeric(num_correct>=8),
            cut_score_7=as.numeric(num_correct>=7),
            cut_score_6=as.numeric(num_correct>=6),
            cut_score_5=as.numeric(num_correct>=5),
            cut_score_4=as.numeric(num_correct>=4),
            cut_score_3=as.numeric(num_correct>=3),
            cut_score_2=as.numeric(num_correct>=2),
            cut_score_1=as.numeric(num_correct>=1)) %>%
  summarise_all(~wtd.mean(.,  w=school_ipw, na.rm=TRUE)) %>%
  pivot_longer(cols=starts_with('cut_score_'),
               names_to = 'cutscore',
               names_prefix = 'cut_score_',
               values_to = 'scores') %>%
  mutate(cutscore=as.numeric(cutscore))

  
prob_plot_proficient_jordan<- ggplot(data=lang_cutscores_jordan, aes(x=cutscore, y=scores, label=round(scores,2))) +
  geom_point() +
  geom_text(hjust=1.6,vjust=0.6) +
  theme_light() +
  expand_limits(x = 0, y = 0) +
  geom_vline(xintercept=19, linetype="dashed", color = "red") +
  scale_x_continuous(name="Cutscore Threshold", breaks=c(1,3,5,7,9,11,13,15,17,19,21,23, 25))+
  theme(axis.title.y = element_blank()) +
  ggtitle(str_wrap("Literacy Fraction Proficient Based on Alternative Cutscore Thresholds - Jordan", 60))
  
 prob_plot_proficient_jordan


```

---
# Math Cut Scores - Peru

```{r math_cutscore_sumstats_peru, fig.height=6, fig.width=8, echo=FALSE}

math <- assess_4th_grade_anon %>%
  select(contains('m8sb')) %>%
  mutate(m8sbq1_number_sense=as.numeric(m8sbq1_number_sense==1)) %>%
  mutate_all(~bin_var_NA0(.,1))

math2 <- math %>%
  mutate(m8sbq1_number_sense=m8sbq1_number_sense*3)
num_correct <- rowSums(math2, na.rm=T)

math_cutscores_peru <- data.frame(math2, num_correct, school_ipw)

#set math cutscore to 9, which is around where the students get average 4th grade level item at 50% rate
math_cutscores_peru <- math_cutscores_peru %>%
  transmute(cut_score_16=as.numeric(num_correct>=16),
            cut_score_15=as.numeric(num_correct>=15),                        
            cut_score_14=as.numeric(num_correct>=14),
            cut_score_13=as.numeric(num_correct>=13),
            cut_score_12=as.numeric(num_correct>=12),
            cut_score_11=as.numeric(num_correct>=11),
            cut_score_10=as.numeric(num_correct>=10),
            cut_score_9=as.numeric(num_correct>=9),
            cut_score_8=as.numeric(num_correct>=8),
            cut_score_7=as.numeric(num_correct>=7),
            cut_score_6=as.numeric(num_correct>=6),
            cut_score_5=as.numeric(num_correct>=5),
            cut_score_4=as.numeric(num_correct>=4),
            cut_score_3=as.numeric(num_correct>=3),
            cut_score_2=as.numeric(num_correct>=2),
            cut_score_1=as.numeric(num_correct>=1)) %>%
  summarise_all(~wtd.mean(.,  w=school_ipw, na.rm=TRUE)) %>%
  pivot_longer(cols=starts_with('cut_score_'),
               names_to = 'cutscore',
               names_prefix = 'cut_score_',
               values_to = 'scores') %>%
  mutate(cutscore=as.numeric(cutscore))

  
prob_plot_proficient_math<- ggplot(data=math_cutscores_peru, aes(x=cutscore, y=scores, label=round(scores,2))) +
  geom_point() +
  geom_text(hjust=1.6,vjust=0.6) +
  theme_light() +
  scale_x_continuous(name="Cutscore Threshold", breaks=c(1,3,5,7,9,11,13,15, 17))+
  geom_vline(xintercept=14, linetype="dashed", color = "red") +
  theme(axis.title.y = element_blank()) +
  expand_limits(x = 0, y = 0) +
  ggtitle(str_wrap("Math Fraction Proficient Based on Alternative Cutscore Thresholds - Peru", 60))
  
 prob_plot_proficient_math


```
---
# Math Cut Scores - Jordan

```{r math_cutscore_sumstats_jordan, fig.height=6, fig.width=8, echo=FALSE}

math <- assess_4th_grade_anon_jordan %>%
  select(contains('m8sb')) %>%
  mutate(m8sbq1_number_sense=as.numeric(m8sbq1_number_sense==1)) %>%
  mutate_all(~bin_var_NA0(.,1))

math2 <- math %>%
  mutate(m8sbq1_number_sense=m8sbq1_number_sense*3)
num_correct <- rowSums(math2, na.rm=T)

math_cutscores_jordan <- data.frame(math2, num_correct, school_ipw)

#set math cutscore to 9, which is around where the students get average 4th grade level item at 50% rate
math_cutscores_jordan <- math_cutscores_jordan %>%
  transmute(cut_score_16=as.numeric(num_correct>=16),
            cut_score_15=as.numeric(num_correct>=15),                        
            cut_score_14=as.numeric(num_correct>=14),
            cut_score_13=as.numeric(num_correct>=13),
            cut_score_12=as.numeric(num_correct>=12),
            cut_score_11=as.numeric(num_correct>=11),
            cut_score_10=as.numeric(num_correct>=10),
            cut_score_9=as.numeric(num_correct>=9),
            cut_score_8=as.numeric(num_correct>=8),
            cut_score_7=as.numeric(num_correct>=7),
            cut_score_6=as.numeric(num_correct>=6),
            cut_score_5=as.numeric(num_correct>=5),
            cut_score_4=as.numeric(num_correct>=4),
            cut_score_3=as.numeric(num_correct>=3),
            cut_score_2=as.numeric(num_correct>=2),
            cut_score_1=as.numeric(num_correct>=1)) %>%
  summarise_all(~wtd.mean(.,  w=school_ipw, na.rm=TRUE)) %>%
  pivot_longer(cols=starts_with('cut_score_'),
               names_to = 'cutscore',
               names_prefix = 'cut_score_',
               values_to = 'scores') %>%
  mutate(cutscore=as.numeric(cutscore))

  
prob_plot_proficient_jordan_math<- ggplot(data=math_cutscores_jordan, aes(x=cutscore, y=scores, label=round(scores,2))) +
  geom_point() +
  geom_text(hjust=1.6,vjust=0.6) +
  theme_light() +
  expand_limits(x = 0, y = 0) +
  scale_x_continuous(name="Cutscore Threshold", breaks=c(1,3,5,7,9,11,13,15, 17))+
  theme(axis.title.y = element_blank()) +
  geom_vline(xintercept=14, linetype="dashed", color = "red") +
  ggtitle(str_wrap("Math Fraction Proficient Based on Alternative Cutscore Thresholds - Jordan", 60))
  
 prob_plot_proficient_jordan_math


```
---








--- 
# Cut Score Approach Based on UIS 
- Set of experts from UIS reviewed the SDI 4th grade math test. 
- Items 3C, 3F, 3I, 5, and 6 are aligned with the skills expected in 4th grade for math. 
- Item 3G is aligned to the content of 5th grade. 
- The remaining items are either aligned with skills in earlier grades or are measuring skills not covered in the GPF.

In Literacy:
- Items 7b,7d, 73, 7f, and 7h aligned 4th grade. 
    - These items all come from the lonely giraffe set of questions.

We will take the following approach to assigning a cut score for our math assessment:

*	Estimate ability levels for all Peru/Jordan examinees using all math items in the SDI test.
*	Identify the ability level to the probability of correctly answering half of the aligned items.
* Translate that ability level to the closest score in the actual test (maybe through a linear scatterplot that shows the best fitting line).


---
#Literacy Cut-Score Plots - Jordan

```{r lang_cut_score_pre, include=FALSE}
#create matrix with  just item responses

language <- assess_4th_grade_anon_jordan %>%
  select(contains('m8sa')) %>%
  mutate(m8saq2_id=as.numeric(m8saq2_id==1),
         m8saq3_id=as.numeric(m8saq3_id==1),
         m8saq4_id=as.numeric(m8saq4_id==1)) %>%
  mutate_all(~bin_var_NA0(.,1))

#Estimate IRT parameters ignoring missing values
irt_lang_2PL_jordan <- mirt(language, 1, itemtype='2PL', optimizer='NR', SE=F, technical=list(removeEmptyRows=TRUE))

#estimate factor scores from models
lang_assess_scores<-data.frame(fscores(irt_lang_2PL_jordan, method='EAP', response.pattern = language, lausib))



lang2<-language %>%
  mutate(m8saq2_id=m8saq2_id*3,
         m8saq3_id=m8saq3_id*3,
         m8saq4_id=m8saq4_id*4)
# Get number correct and theta
Theta <- lang_assess_scores$F1
num_correct <- rowSums(lang2, na.rm=T)

```





```{r lang_cut_score, fig.height=6, fig.width=8, echo=FALSE, message=FALSE, warning=FALSE}


#####################################################
# get probabiliy of correct response for these items
#####################################################

#items 7b
extr.7b <- extract.item(irt_lang_2PL_jordan, 6)
traceline <- probtrace(extr.7b, Theta)

prob_7b <- data.frame(traceline, Theta, num_correct) %>%
  mutate(prob_correct=P.1,
         item='7b',
         id=row_number()) %>%
  select(-P.0, -P.1)


#items 7d
extr.7d <- extract.item(irt_lang_2PL_jordan, 8)
traceline <- probtrace(extr.7d, Theta)

prob_7d <- data.frame(traceline, Theta, num_correct) %>%
  mutate(prob_correct=P.1,
         item='7d',
         id=row_number()) %>%
  select(-P.0, -P.1)
#items 7e
extr.7e <- extract.item(irt_lang_2PL_jordan, 9)
traceline <- probtrace(extr.7e, Theta)

prob_7e <- data.frame(traceline, Theta, num_correct) %>%
  mutate(prob_correct=P.1,
         item='7e',
         id=row_number()) %>%
  select(-P.0, -P.1)
#items 7f
extr.7f <- extract.item(irt_lang_2PL_jordan, 10)
traceline <- probtrace(extr.7f, Theta)

prob_7f <- data.frame(traceline, Theta, num_correct) %>%
  mutate(prob_correct=P.1,
         item='7f',
         id=row_number()) %>%
  select(-P.0, -P.1)

#items 7h
extr.7h <- extract.item(irt_lang_2PL_jordan, 12)
traceline <- probtrace(extr.7h, Theta)

prob_7h <- data.frame(traceline, Theta, num_correct) %>%
  mutate(prob_correct=P.1,
         item='7h',
         id=row_number()) %>%
  select(-P.0, -P.1)



probs <- rbind( prob_7b ,prob_7d, prob_7e,
               prob_7f, prob_7h)

#calculate average
prob_avg <- probs %>%
  group_by(id) %>%
  summarise(prob_correct=mean(prob_correct),
            num_correct=mean(num_correct),
            Theta=mean(Theta)) %>%
  mutate(item='Average')

probs<-probs %>%
  bind_rows(prob_avg)

#test ggplot
prob_plot_theta<- ggplot(data=probs, aes(x=Theta, y=prob_correct, color=item)) +
  geom_line() +
  theme_light() +
  scale_x_continuous(name=expression(theta))+
  theme(axis.title.y = element_blank()) +
  ggtitle(expression(paste("Probability of Correct Response by ",theta," and Fraction Correct - Literacy")))

prob_plot_num_correct_lit<- ggplot(data=probs, aes(x=num_correct, y=prob_correct, color=item)) +
  geom_smooth() +
  theme_light() +
  geom_vline(xintercept=19, linetype="dashed", color = "red") +
  scale_x_continuous(name="Number Correct", breaks=c(1,3,5,7,9,11,13,15,17,19,21,23,25))+
  theme(axis.title.y = element_blank()) +
  ggtitle(str_wrap("Probability of Correct Response on Five 4th Grade Level Items by Fraction Correct on All Literacy Items - Jordan ", 60))

# prob_plot_theta
prob_plot_num_correct_lit
# ggarrange(prob_plot_theta, prob_plot_num_correct,
#           nrow=2)



```
---
# Math Cut Scores Plots - Peru
```{r math_cut_score_prep, include=FALSE}
#create matrix with  just item responses
math <- assess_4th_grade_anon %>%
  select(contains('m8sb')) %>%
  mutate(m8sbq1_number_sense=as.numeric(m8sbq1_number_sense==1)) %>%
  mutate_all(~bin_var_NA0(.,1))

language <- assess_4th_grade_anon %>%
  select(contains('m8sa')) %>%
  mutate(m8saq2_id=as.numeric(m8saq2_id==1),
         m8saq3_id=as.numeric(m8saq3_id==1),
         m8saq4_id=as.numeric(m8saq4_id==1)) %>%
  mutate_all(~bin_var_NA0(.,1))

#Estimate IRT parameters ignoring missing values
irt_math_2PL <- mirt(math, 1, itemtype='2PL', optimizer='NR', SE=F, technical=list(removeEmptyRows=TRUE))
irt_lang_2PL <- mirt(language, 1, itemtype='2PL', optimizer='NR', SE=F, technical=list(removeEmptyRows=TRUE))

#estimate factor scores from models
lang_assess_scores<-data.frame(fscores(irt_lang_2PL, method='EAP', response.pattern = language, lausib))

math_assess_scores<-data.frame(fscores(irt_math_2PL, method='EAP', response.pattern = math))

# Get number correct and theta
Theta <- math_assess_scores$F1

math2 <- math %>%
  mutate(m8sbq1_number_sense=m8sbq1_number_sense*3)
num_correct <- rowSums(math2, na.rm=T)
```


```{r math_cut_score, fig.height=6, fig.width=8, echo=FALSE, message=FALSE, warning=FALSE}



#####################################################
# get probabiliy of correct response for these items
#####################################################

#items 3C
extr.3c <- extract.item(irt_math_2PL, 4)
traceline <- probtrace(extr.3c, Theta)

prob_3c <- data.frame(traceline, Theta, num_correct) %>%
  mutate(prob_correct=P.1,
         item='3c',
         id=row_number()) %>%
  select(-P.0, -P.1)


#items 3F
extr.3f <- extract.item(irt_math_2PL, 7)
traceline <- probtrace(extr.3f, Theta)

prob_3f <- data.frame(traceline, Theta, num_correct) %>%
  mutate(prob_correct=P.1,
         item='3f',
         id=row_number()) %>%
  select(-P.0, -P.1)
#items 3I
extr.3i <- extract.item(irt_math_2PL, 10)
traceline <- probtrace(extr.3i, Theta)

prob_3i <- data.frame(traceline, Theta, num_correct) %>%
  mutate(prob_correct=P.1,
         item='3i',
         id=row_number()) %>%
  select(-P.0, -P.1)
#items 5
extr.5 <- extract.item(irt_math_2PL, 13)
traceline <- probtrace(extr.5, Theta)

prob_5 <- data.frame(traceline, Theta, num_correct) %>%
  mutate(prob_correct=P.1,
         item='5',
         id=row_number()) %>%
  select(-P.0, -P.1)

#items 6
extr.6 <- extract.item(irt_math_2PL, 14)
traceline <- probtrace(extr.6, Theta)

prob_6 <- data.frame(traceline, Theta, num_correct) %>%
  mutate(prob_correct=P.1,
         item='6',
         id=row_number()) %>%
  select(-P.0, -P.1)
#items 3G
extr.3g <- extract.item(irt_math_2PL, 8)
traceline <- probtrace(extr.3g, Theta)

prob_3g <- data.frame(traceline, Theta, num_correct) %>%
  mutate(prob_correct=P.1,
         item='3g',
         id=row_number()) %>%
  select(-P.0, -P.1)



probs <- rbind(prob_3c, prob_3f, prob_3i,
               prob_5, prob_6, prob_3g)

#calculate average
prob_avg <- probs %>%
  group_by(id) %>%
  summarise(prob_correct=mean(prob_correct),
            num_correct=mean(num_correct),
            Theta=mean(Theta)) %>%
  mutate(item='Average')

probs<-probs %>%
  bind_rows(prob_avg)

#test ggplot
prob_plot_theta<- ggplot(data=probs, aes(x=Theta, y=prob_correct, color=item)) +
  geom_line() +
  theme_light() +
  scale_x_continuous(name=expression(theta))+
  theme(axis.title.y = element_blank()) +
  ggtitle(expression(paste("Probability of Correct Response by ",theta," and Fraction Correct")))

prob_plot_num_correct<- ggplot(data=probs, aes(x=num_correct, y=prob_correct, color=item)) +
  geom_smooth() +
  theme_light() +
  geom_vline(xintercept=14, linetype="dashed", color = "red") +
  scale_x_continuous(name="Number Correct", breaks=c(1,3,5,7,9,11,13,15))+
  theme(axis.title.y = element_blank()) +
  ggtitle(str_wrap("Probability of Correct Response on Six 4th Grade Level Items by Fraction Correct on All Math Items - Peru", 60))

# prob_plot_theta
prob_plot_num_correct
# ggarrange(prob_plot_theta, prob_plot_num_correct,
#           nrow=2)



```

---

# Math Cut Scores Plots - Jordan
```{r math_cut_score_prep_jordan, include=FALSE}
#create matrix with  just item responses
math <- assess_4th_grade_anon_jordan %>%
  select(contains('m8sb')) %>%
  mutate(m8sbq1_number_sense=as.numeric(m8sbq1_number_sense==1)) %>%
  mutate_all(~bin_var_NA0(.,1))



#Estimate IRT parameters ignoring missing values
irt_math_2PL_jordan <- mirt(math, 1, itemtype='2PL', optimizer='NR', SE=F, technical=list(removeEmptyRows=TRUE))

#estimate factor scores from models

math_assess_scores<-data.frame(fscores(irt_math_2PL_jordan, method='EAP', response.pattern = math))

#estimate factor scores from models

math_assess_scores<-data.frame(fscores(irt_math_2PL, method='EAP', response.pattern = math))

# Get number correct and theta
Theta <- math_assess_scores$F1

math2 <- math %>%
  mutate(m8sbq1_number_sense=m8sbq1_number_sense*3)
num_correct <- rowSums(math2, na.rm=T)
```


```{r math_cut_score_jordan, fig.height=6, fig.width=8, echo=FALSE, message=FALSE, warning=FALSE}



#####################################################
# get probabiliy of correct response for these items
#####################################################

#items 3C
extr.3c <- extract.item(irt_math_2PL_jordan, 4)
traceline <- probtrace(extr.3c, Theta)

prob_3c <- data.frame(traceline, Theta, num_correct) %>%
  mutate(prob_correct=P.1,
         item='3c',
         id=row_number()) %>%
  select(-P.0, -P.1)


#items 3F
extr.3f <- extract.item(irt_math_2PL_jordan, 7)
traceline <- probtrace(extr.3f, Theta)

prob_3f <- data.frame(traceline, Theta, num_correct) %>%
  mutate(prob_correct=P.1,
         item='3f',
         id=row_number()) %>%
  select(-P.0, -P.1)
#items 3I
extr.3i <- extract.item(irt_math_2PL_jordan, 10)
traceline <- probtrace(extr.3i, Theta)

prob_3i <- data.frame(traceline, Theta, num_correct) %>%
  mutate(prob_correct=P.1,
         item='3i',
         id=row_number()) %>%
  select(-P.0, -P.1)
#items 5
extr.5 <- extract.item(irt_math_2PL_jordan, 13)
traceline <- probtrace(extr.5, Theta)

prob_5 <- data.frame(traceline, Theta, num_correct) %>%
  mutate(prob_correct=P.1,
         item='5',
         id=row_number()) %>%
  select(-P.0, -P.1)

#items 6
extr.6 <- extract.item(irt_math_2PL_jordan, 14)
traceline <- probtrace(extr.6, Theta)

prob_6 <- data.frame(traceline, Theta, num_correct) %>%
  mutate(prob_correct=P.1,
         item='6',
         id=row_number()) %>%
  select(-P.0, -P.1)
#items 3G
extr.3g <- extract.item(irt_math_2PL_jordan, 8)
traceline <- probtrace(extr.3g, Theta)

prob_3g <- data.frame(traceline, Theta, num_correct) %>%
  mutate(prob_correct=P.1,
         item='3g',
         id=row_number()) %>%
  select(-P.0, -P.1)



probs <- rbind(prob_3c, prob_3f, prob_3i,
               prob_5, prob_6, prob_3g)

#calculate average
prob_avg <- probs %>%
  group_by(id) %>%
  summarise(prob_correct=mean(prob_correct),
            num_correct=mean(num_correct),
            Theta=mean(Theta)) %>%
  mutate(item='Average')

probs<-probs %>%
  bind_rows(prob_avg)

#test ggplot
prob_plot_theta<- ggplot(data=probs, aes(x=Theta, y=prob_correct, color=item)) +
  geom_line() +
  theme_light() +
  scale_x_continuous(name=expression(theta))+
  theme(axis.title.y = element_blank()) +
  ggtitle(expression(paste("Probability of Correct Response by ",theta," and Fraction Correct")))

prob_plot_num_correct<- ggplot(data=probs, aes(x=num_correct, y=prob_correct, color=item)) +
  geom_smooth() +
  theme_light() +
  geom_vline(xintercept=14, linetype="dashed", color = "red") +
  scale_x_continuous(name="Number Correct", breaks=c(1,3,5,7,9,11,13,15))+
  theme(axis.title.y = element_blank()) +
  ggtitle(str_wrap("Probability of Correct Response on Six 4th Grade Level Items by Fraction Correct on All Math Items - Jordan", 60))

# prob_plot_theta
prob_plot_num_correct
# ggarrange(prob_plot_theta, prob_plot_num_correct,
#           nrow=2)



```
