---
title: "ETH Teacher Linkages"
format: html
---

# Introduction

This analysis will link the teacher modules  using teacher IDs and names and then do some basic analysis.

Teachers can be linked by a common ID.  The following are the column names in the various files

* Teacher pedagogy: m4saq1_number
* Teacher Content Knowledge: m5sb_tnum
* Teacher Questionnaire: m3sb_tnumber
* Teacher Roster: TEACHERS__id

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	fig.height = 6,
	fig.width = 8,
	message = FALSE,
	warning = FALSE
)
library(tidyverse)
library(haven)
library(vtable)
library(here)
library(readxl)
library(stringr)
library(Hmisc)
library(naniar)
library(lubridate)
library(skimr)
library(digest)
library(validate)
library(GGally)
library(Hmisc)
#Country name
country <-'ETH'
country_name <- "Ethiopia"
year <- '2020_2021'
school_file <-'EPDash.dta'
#########################
# File paths #
#########################
#The download_folder will be the location of where raw data is downloaded from the API
#The save_folder will be the location of where cleaned data is stored



if (str_to_lower(Sys.getenv("USERNAME")) == "wb469649" ){
  #project_folder  <- "//wbgfscifs01/GEDEDU/datalib-edu/projects/gepd"
  project_folder  <- "C:/Users/wb469649/WBG/HEDGE Files - HEDGE Documents/GEPD-Confidential/"
  download_folder <-file.path(paste(project_folder,"CNT",country,paste(country,year,"GEPD", sep="_"),paste(country,year,"GEPD_v01_RAW", sep="_"),"Data/raw/School/", sep="/"))
  sampling_folder <-file.path(paste(project_folder,"CNT",country,paste(country,year,"GEPD", sep="_"),paste(country,year,"GEPD_v01_RAW", sep="_"),"Data/sampling", sep="/"))
  confidential_folder <- file.path(paste(project_folder,"CNT",country,paste(country,year,"GEPD", sep="_"),paste(country,year,"GEPD_v01_RAW", sep="_"),"Data/confidential/School", sep="/"))
  save_input_folder <- file.path(paste0(project_folder,"General/LEGO_Teacher_Paper/3_input_data"))
  save_output_folder <- file.path(paste0(project_folder,"General/LEGO_Teacher_Paper/5_output_data"))

} else if  (str_to_lower(Sys.getenv("USERNAME")) == "wb577189" ){
  #project_folder  <- "//wbgfscifs01/GEDEDU/datalib-edu/projects/gepd"
  project_folder  <- "C:/Users/wb577189/OneDrive - WBG/GEPD-Confidential/CNT/"
  download_folder <-file.path(paste(project_folder,"/CNT/",country,paste(country,year,"GEPD", sep="_"),paste(country,year,"GEPD_v01_RAW", sep="_"),"Data/raw/School", sep="/"))
  sampling_folder <-file.path(paste(project_folder,"/CNT/",country,paste(country,year,"GEPD", sep="_"),paste(country,year,"GEPD_v01_RAW", sep="_"),"Data/sampling", sep="/"))
  confidential_folder <- file.path(paste(project_folder,"/CNT/",country,paste(country,year,"GEPD", sep="_"),paste(country,year,"GEPD_v01_RAW", sep="_"),"Data/confidential/School", sep="/"))
  save_input_folder <- file.path(paste0(project_folder,"General/LEGO_Teacher_Paper/3_input_data"))
  save_output_folder <- file.path(paste0(project_folder,"General/LEGO_Teacher_Paper/5_output_data"))

} else if  (str_to_lower(Sys.getenv("USERNAME")) == "wb631589" ){
  #project_folder  <- "//wbgfscifs01/GEDEDU/datalib-edu/projects/gepd"
  project_folder  <- "C:/Users/wb631589/OneDrive - WBG/GEPD-Confidential/"
  download_folder <-file.path(paste(project_folder,"/CNT/",country,paste(country,year,"GEPD", sep="_"),paste(country,year,"GEPD_v02_RAW", sep="_"),"Data/raw/School", sep="/"))
  sampling_folder <-file.path(paste(project_folder,"/CNT/",country,paste(country,year,"GEPD", sep="_"),paste(country,year,"GEPD_v02_RAW", sep="_"),"Data/sampling", sep="/"))
  confidential_folder <- file.path(paste(project_folder,"/CNT/",country,paste(country,year,"GEPD", sep="_"),paste(country,year,"GEPD_v02_RAW", sep="_"),"Data/confidential/School", sep="/"))
  save_input_folder <- file.path(paste0(project_folder,"General/LEGO_Teacher_Paper/3_input_data"))
  save_output_folder <- file.path(paste0(project_folder,"General/LEGO_Teacher_Paper/5_output_data"))

} else {
  download_folder <- choose.dir(default = "", caption = "Select folder to open data downloaded from API")
  save_folder <- choose.dir(default = "", caption = "Select folder to save final data")

}


```

```{r functions}



#function to attach weights

# df_weights_function <- function(dataset,scode, snumber, prov) {
#   scode<-enquo(scode)  
#   snumber<-enquo(snumber)
#   prov<-enquo(prov)
#   
#   dataset %>%
#     mutate(!! scode := as.numeric(.data$school_code)) %>%
#     left_join(weights_df %>% filter(Admin_Code %in% emis_list) %>% filter(Region %in% region_list)  %>% filter(Zone %in% zone_list)  %>% filter(Woreda %in% woreda_list)  %>% filter(Program==1)) %>%
#     left_join(data_set_updated %>% filter(Admin_Code %in% emis_list) %>% filter(Region %in% region_list) %>% filter(Zone %in% zone_list)   %>% filter(Woreda %in% woreda_list) %>% filter(Program==1))  %>%
#     mutate(
#            N_schools=N_sch,
#            N_schools_strata=N_sch_strata,
#            N_selected_strata=N_sel_strata,
#            school_weights=ipw,
#            ipw=ipw*!! snumber,
#            ipw=if_else(is.na(ipw),mean(ipw, na.rm=T), ipw)) %>%
#     mutate(province=Region,
#            urban_rural=Location
#            ) %>%
#     select(-one_of(colnames(data_set_updated[, -which(names(data_set_updated) == "Location" | names(data_set_updated) == "Region" | 
#                                                         names(data_set_updated) == "owner" )])))
# }

df_weights_function <- function(dataset,scode, snumber, prov) {
  scode<-enquo(scode)  
  snumber<-enquo(snumber)
  prov<-enquo(prov)
  
  dataset %>%
    left_join(data_set_updated)  %>%
    mutate(province=Region,
           urban_rural=Location, 
           school_weight = 1/(sample/count)) 
}


df_add_weights<- function(dataset) {
  temp<-get(dataset) 
    
    #add hashed school code if needed
    if ("school_code" %in% colnames(temp)) {
      temp <- temp %>%
        left_join(key) %>%
        select(hashed_school_code, hashed_school_province, hashed_school_district, everything())
    }
    
    
    #add on weights
    if ("school_code" %in% colnames(temp)) {
      temp <- df_weights_function(temp, Code_School, grd4_total, Region)
    }
    
}

```

```{r}
#list of key indicators

ind_list<-c('student_knowledge', 'math_student_knowledge', 'literacy_student_knowledge', 
            'student_proficient', 'student_proficient_70', 'student_proficient_75',
            'literacy_student_proficient', 'literacy_student_proficient_70', 'literacy_student_proficient_75',
            'math_student_proficient', 'math_student_proficient_70', 'math_student_proficient_75',
            'presence_rate','absence_rate', 'sch_absence_rate', 'student_attendance',
            'content_knowledge', 'math_content_knowledge', 'literacy_content_knowledge', 
            'content_proficiency',  'content_proficiency_70', 'content_proficiency_75',
            'literacy_content_proficiency',  'literacy_content_proficiency_70', 'literacy_content_proficiency_75',
            'math_content_proficiency',  'math_content_proficiency_70', 'math_content_proficiency_75',
            'teach_score','classroom_culture','instruction','socio_emotional_skills',
            'teach_prof','classroom_culture_prof','instruction_prof','socio_emotional_skills_prof',
            'ecd_student_proficiency', 'ecd_math_student_proficiency', 'ecd_literacy_student_proficiency', 'ecd_exec_student_proficiency', 'ecd_soc_student_proficiency',
            'ecd_student_knowledge', 'ecd_math_student_knowledge', 'ecd_literacy_student_knowledge', 'ecd_exec_student_knowledge', 'ecd_soc_student_knowledge',
            'inputs', 'blackboard_functional', 'pens_etc', 'textbooks', 'share_desk', 'used_ict', 'access_ict',
            'infrastructure','drinking_water', 'functioning_toilet', 'internet', 'class_electricity','disability_accessibility','disab_road_access', 'disab_school_ramp', 'disab_school_entr', 'disab_class_ramp', 'disab_class_entr', 'disab_screening',
            'operational_management', 'vignette_1', 'vignette_1_resp', 'vignette_1_finance', 'vignette_1_address', 'vignette_2', 'vignette_2_resp', 'vignette_2_finance', 'vignette_2_address', 
            'intrinsic_motivation', 'acceptable_absent', 'students_deserve_attention', 'growth_mindset', 'motivation_teaching',
            'instructional_leadership', 'classroom_observed', 'classroom_observed_recent', 'discussed_observation', 'feedback_observation', 'lesson_plan_w_feedback',
            'principal_knowledge_score', 'add_triple_digit_pknw', 'multiply_double_digit_pknw', 'complete_sentence_pknw', 'experience_pknw', 'textbooks_pknw', 'blackboard_pknw',
            'principal_management', 'sch_goals_exist','sch_goals_clear','sch_goals_relevant','sch_goals_measured',
            'teacher_attraction', 'teacher_satisfied_job', 'teacher_satisfied_status', 'better_teachers_promoted' ,'teacher_bonus', 'salary_delays',
            'teacher_selection_deployment', 'teacher_selection','teacher_deployment',
            'teacher_support', 'pre_service','practicum','in_service','opportunities_teachers_share',
            'teaching_evaluation', 'formally_evaluated', 'evaluation_content', 'negative_consequences','positive_consequences',
            'teacher_monitoring','attendance_evaluated' , 'attendance_rewarded' , 'attendence_sanctions', 'miss_class_admin',
            'sch_management_clarity', 'infrastructure_scfn','materials_scfn','hiring_scfn', 'supervision_scfn', 'student_scfn' , 'principal_hiring_scfn', 'principal_supervision_scfn',
            'standards_monitoring',
            'sch_monitoring', 'monitoring_inputs','monitoring_infrastructure','system_in_place','parents_involved',
            'sch_management_attraction', 'principal_satisfaction',
            'sch_selection_deployment', 
            'sch_support', 'prinicipal_trained','principal_training','principal_used_skills','principal_offered',
            'principal_evaluation', 'principal_formally_evaluated','principal_evaluation_multiple','principal_negative_consequences','principal_positive_consequences'
)

#attach derived indicators
load(paste0(confidential_folder,"/school_survey_data.RData"))

```


## Weights File

```{r}
#read in the file on school weights
#Load original sample of schools
currentDate<-c("2020-02-14")
sample_folder <- file.path(paste(project_folder,"CNT",country,paste(country,'2021',"GEPD", sep="_"),paste(country,'2021',"GEPD_v02_RAW", sep="_"),"Data/sampling/", sep="/"))
sample_frame_name <- paste(sample_folder,"/school_sample_",currentDate,".RData", sep="")
weights_df  <- read_csv(paste(sample_folder,"/Ethiopia_weights.csv", sep=""))
school_info <- read.csv(paste0("C:/Users/wb631589/OneDrive - WBG/Dashboard (Team Folder)/Country_Work/Ethiopia/2020/Data/Sampling/Primary_schools_STATA/Primary_schools_ETH.csv"))


data_set_updated <- weights_df %>%
  mutate(
    school_code = Code_School,
    strata_count = paste0(Woreda, Region, Zone, Location)
  )

data_set_updated <- data_set_updated %>%
  mutate(
    school_code = if_else(school_code == 500135 & School_Name == "Ruqi", 5001350, school_code))

#for sampled school that can potentially have more than 1 match, keep the relevant ones 
data_set_updated <- data_set_updated %>%
  filter(!(school_code == 100008 & School_Name == "Chaba"),
         !(school_code == 500033 & (School_Name == "Bonga")),
         !(school_code == 500069 & (School_Name == "Bejit" | School_Name == "Dhadhin")),
         !(school_code == 500077 & (School_Name == "Lucy Acadamy" | School_Name == "Setema" | School_Name == "Cali bakow")))


data_set_updated <- data_set_updated %>%
  filter(!(school_code == 100308 & School_Name == "Dukie"),
         !(school_code == 500135 & (School_Name == "Majeti" | School_Name == "Fejej")))

#get the grade 4 student count to know what schools to keep in case we have multiple programs
school_info <- school_info %>%
  filter(Grade == "Grade 4") %>%
  mutate(total_students = M+F) %>%
  group_by(Code_School, Region, Woreda, School_Name, Program) %>%
  summarise(grd4_total = sum(total_students)) %>%
  ungroup()


#for schools that have multiple programs, keep the program with the maximum student count
data_set_updated <- data_set_updated %>%
  left_join(school_info) %>%
  mutate(grd4_total = replace_na(grd4_total, 0L),
         tie_break = if_else(as.character(Program) == "1", 1L, 2L)) %>%
  group_by(Code_School, Region, Woreda, School_Name) %>%
  # keep the row with max grd4_total; if multiple, pick the one with smallest tie_break
  slice_max(grd4_total, with_ties = TRUE) %>%
  arrange(tie_break) %>%
  slice_head(n = 1) %>%
  ungroup() %>%
  select(-tie_break)

#there are still 5 schools 407814 550446 601254 601499 700084 with double listings due to program, just average the weight for them. Even though not ideal, 
#doing this to save time given that all other sampled schools are unique at the school code level
data_set_updated <- data_set_updated %>%
  group_by(school_code) %>%
  summarise(sample = mean(sample),
            count = mean(count),
            strata_count = first(strata_count),
            Region = first(Region),
            Location = first(Location))

# data_set_updated <- data_set_updated %>%
#   mutate(school_weight= 1/(sample/count))

# %>%
#   select(-sample) #variable name causes conflict
# load(sample_frame_name)
# 
# #get list of schools from interview data
# emis_list<-school_dta_short$school_emis_preload
# code_list<-school_dta_short$school_code
# region_list<-school_dta_short$school_address_preload
# zone_list<-school_dta_short$school_province_preload
# woreda_list<-school_dta_short$school_district_preload
# 
# #create weights for each school
# data_set_updated <- data_set_updated %>%
#   mutate(N_sch=n()) %>% #get total number of schools
#   #now calculate probability of selecting woreda
#   group_by(Region, Zone, Woreda) %>%
#   mutate(N_school_woreda=n(),
#          N_students_woreda=sum(grd4_total,na.rm=T)) %>%
#   group_by(Region) %>%
#   mutate(strat_total=sum(grd4_total, na.rm=T),
#          N_sel_strata=sum(as.numeric(sample=="Sampled School"),na.rm=T),
#          N_sch_strata=n()) #stratum weights (three schools selected)


key <- read_csv(file.path(confidential_folder, "EPDash_linkfile_hashed.csv"))

#remove two duplicates schools since the information is consistent for them both 
key <- key %>%
  group_by(school_code) %>%
  fill(everything(), .direction = "downup") %>%
  ungroup() %>%
  distinct(school_code, .keep_all = TRUE) 

```

## School File

```{r school}

###########################
#read in school level file
###########################

#in the raw data, there seems to be 2 schools were the data were collected in 2020 and 2021. okay to keep school 306356 because the one coming from 2020 seems to be fully empty. for the other school, for now let's assign two different school codes before the collapse
school_dta <- school_dta %>%
  mutate(
         school_code  = if_else(school_code == 409732 & date == 2020, 4097322020, school_code))

school_dta_short <- school_dta_short %>%
  mutate(
         school_code  = if_else(school_code == 409732 & date == 2020, 4097322020, school_code))

school_weights  <- school_weights %>%
  mutate(
         school_code  = if_else(school_code == 409732 & date == 2020, 4097322020, school_code))

module_cols <- paste0("modules__", 1:8)  # modules_1 to modules_8

for (i in 1:8) {
  module <- paste0("modules__", i)
  dupl_var <- paste0("dupl_", i)
  
  school_dta <- school_dta %>%
    group_by(school_code, .data[[module]]) %>%
    mutate(!!dupl_var := n() > 1) %>%
    ungroup()
}

school_micro_raw <- school_dta %>%
  group_by(school_code) %>%
  mutate(across(where(is.character), ~ na_if(.x, ""))) %>%  # turn "" into NA
  fill(everything(), .direction='downup') %>%
  slice(1) %>% 
  ungroup()

var.list <- sapply(school_dta, function(x) attr(x,"label"))
var.labels= unlist(var.list)


#merge on derived indicators
school_micro_comb <- school_micro_raw %>%
  left_join(
    school_dta_short %>%
      select(school_code, ind_list)
  ) %>%
  select(colnames(school_data_preamble), ind_list, everything())

#add weights and anonymize
school_micro <- df_add_weights('school_micro_comb')  

#now for the school that was repeated in both years, assign the same school weight and strata variables since this is our best guess
school_micro <- school_micro %>% 
  mutate(hashed_school_code = if_else(school_code == 4097322020, "55f7525b6c88fcbf", hashed_school_code),
         hashed_school_province = if_else(school_code == 4097322020, "d3e706fdb56e5000", hashed_school_province),
         hashed_school_district = if_else(school_code == 4097322020, "c5d330755961900a", hashed_school_district),
         sample = if_else(school_code == 4097322020, 12, sample), 
         count = if_else(school_code == 4097322020, 1703, count),
         strata_count = if_else(school_code == 4097322020, "Kindo DidayeSNNPWolaytaRural", strata_count),
         Region = if_else(school_code == 4097322020, "SNNP", Region),
         Location = if_else(school_code == 4097322020, "Rural", Location),
         province = if_else(school_code == 4097322020, "SNNP", province),
         urban_rural = if_else(school_code == 4097322020, "Rural", urban_rural),
         school_weight = if_else(school_code == 4097322020, 142, school_weight)
)

#school_micro <- Hmisc::upData(school_micro, labels = var.labels)

```


```{r}
#create a file for matching to tecaher and student files

#list additional info that will be useful to keep in each indicator dataframe
preamble_info <- c( 'interview__key', 'school_code',
                   'school_name_preload', 
                   'school_province_preload', 'school_district_preload', 'school_emis_preload', 'school_emis_preload',
                   'school_info_correct', 'm1s0q2_name', 'm1s0q2_code', 'm1s0q2_emis',
                   'survey_time', 'lat', 'lon' , 'total_enrolled' , 'm7saq10'
                   )

drop_school_info <- c(

)


#create school database with just preamble info.  This will be useful for merging on school level info to some databases
school_data_preamble_temp <- school_dta %>%
  group_by(school_code) %>%
  select( preamble_info) %>%
  select(-interview__key) %>%
  summarise_all( ~(if(is.numeric(.)) mean(., na.rm = TRUE) else first(.))) 
  
school_data_preamble <- school_dta %>%
  group_by(interview__key) %>%
  select(interview__key, school_code) %>%
  left_join(school_data_preamble_temp)
```


## Teacher Questionnaire File

```{r}

#for this one repeated school, change the school code 
teacher_questionnaire <- teacher_questionnaire %>%
  mutate(
         school_code  = if_else(school_code == 409732 & date == 2020, 4097322020, school_code))


#Add school preamble info
teacher_questionnaire <- teacher_questionnaire %>%
  left_join(school_data_preamble) %>%
  select(preamble_info, everything()) %>%
  #for those that are duplicated based on the teacher number, change the number to questionnaire id if it is possible
  mutate(m3sb_tnumber = if_else(school_code == 100008  & m3sb_tnumber == 7 & m3sb_troster == "Rebeka Tujar", 4, m3sb_tnumber),
         m3sb_tnumber = if_else(school_code == 104432  & m3sb_tnumber == 3 & m3sb_troster == "Asimarechi Bekalu", 2, m3sb_tnumber),
         m3sb_tnumber = if_else(school_code == 108797  & m3sb_tnumber == 6 & m3sb_troster == "Melese Bayih", 2, m3sb_tnumber),
         m3sb_tnumber = if_else(school_code == 108974  & m3sb_tnumber == 6 & m3sb_troster == "Maritu Belay", 5, m3sb_tnumber),
         m3sb_tnumber = if_else(school_code == 201295  & m3sb_tnumber == 3 & m3sb_troster == "Gudeta Aliy", 2, m3sb_tnumber),
         m3sb_tnumber = if_else(school_code == 201462  & m3sb_tnumber == 14 & m3sb_troster == "Mohammed  Abdulay", 4, m3sb_tnumber),
         m3sb_tnumber = if_else(school_code == 207363  & m3sb_tnumber == 3 & m3sb_troster == "ABDI UMER", 1, m3sb_tnumber),
         m3sb_tnumber = if_else(school_code == 208402  & m3sb_tnumber == 4 & m3sb_troster == "Umer Dereje", 3, m3sb_tnumber),
         m3sb_tnumber = if_else(school_code == 305813  & m3sb_tnumber == 2 & m3sb_troster == "Nasir Ahmed", 1, m3sb_tnumber),
         m3sb_tnumber = if_else(school_code == 305813  & m3sb_tnumber == 3 & m3sb_troster == "Abdi Umer", 7, m3sb_tnumber),
         m3sb_tnumber = if_else(school_code == 305973  & m3sb_tnumber == 3 & m3sb_troster == "Bashir Farah", 1, m3sb_tnumber),
         m3sb_tnumber = if_else(school_code == 400926  & m3sb_tnumber == 18 & m3sb_troster == "Habtamu Beyene", 1, m3sb_tnumber),
         m3sb_tnumber = if_else(school_code == 401185  & m3sb_tnumber == 6 & m3sb_troster == "Yakobe Handesa", 5, m3sb_tnumber),
         m3sb_tnumber = if_else(school_code == 407814  & m3sb_tnumber == 4 & m3sb_troster == "sewunet aserese", 3, m3sb_tnumber),
         m3sb_tnumber = if_else(school_code == 500135  & m3sb_tnumber == 2 & m3sb_troster == "ZINET EBRAHIME", 6, m3sb_tnumber),
         m3sb_tnumber = if_else(school_code == 550264  & m3sb_tnumber == 4 & m3sb_troster == "2.Aliyi Mehmad", 2, m3sb_tnumber),
         m3sb_tnumber = if_else(school_code == 550323  & m3sb_tnumber == 8 & m3sb_troster == "EDEMALEM ENEYEW", 3, m3sb_tnumber)) %>%
  group_by(school_code,m3sb_tnumber) %>%
  fill(everything(), .direction='downup') %>%
  slice(1) %>% 
  ungroup()


#add weights and anonymize
teacher_questionnaire_micro <- df_add_weights('teacher_questionnaire')      %>%
  select(-starts_with('interview__'), -c('lat','lon'))              


#now for the school that was repeated in both years, assign the same school weight and strata variables since this is our best guess
teacher_questionnaire_micro <- teacher_questionnaire_micro %>% 
  mutate(hashed_school_code = if_else(school_code == 4097322020, "55f7525b6c88fcbf", hashed_school_code),
         hashed_school_province = if_else(school_code == 4097322020, "d3e706fdb56e5000", hashed_school_province),
         hashed_school_district = if_else(school_code == 4097322020, "c5d330755961900a", hashed_school_district),
         sample = if_else(school_code == 4097322020, 12, sample), 
         count = if_else(school_code == 4097322020, 1703, count),
         strata_count = if_else(school_code == 4097322020, "Kindo DidayeSNNPWolaytaRural", strata_count),
         Region = if_else(school_code == 4097322020, "SNNP", Region),
         Location = if_else(school_code == 4097322020, "Rural", Location),
         province = if_else(school_code == 4097322020, "SNNP", province),
         urban_rural = if_else(school_code == 4097322020, "Rural", urban_rural),
         school_weight = if_else(school_code == 4097322020, 142, school_weight)
)

#merge in teacher weights
teacher_assessment_weights <- school_weights %>%
  select(school_code, teacher_weight_component)


teacher_questionnaire_micro <- teacher_questionnaire_micro %>%
  left_join(teacher_assessment_weights, by = "school_code")


```


## Teacher Absence File

```{r}
############################
#read in teacher roster file
############################


teacher_absence_dta <- teacher_absence_final 

teacher_absence_dta <- teacher_absence_dta %>%
  mutate(
         school_code  = if_else(school_code == 409732 & date == 2020, 4097322020, school_code))

#add weights and anonymize
teacher_absence_micro <- df_add_weights('teacher_absence_dta')       %>%
  select(-starts_with('interview__'), -c('lat','lon'))    

teacher_absence_micro <- teacher_absence_micro %>% 
  mutate(hashed_school_code = if_else(school_code == 4097322020, "55f7525b6c88fcbf", hashed_school_code),
         hashed_school_province = if_else(school_code == 4097322020, "d3e706fdb56e5000", hashed_school_province),
         hashed_school_district = if_else(school_code == 4097322020, "c5d330755961900a", hashed_school_district),
         sample = if_else(school_code == 4097322020, 12, sample), 
         count = if_else(school_code == 4097322020, 1703, count),
         strata_count = if_else(school_code == 4097322020, "Kindo DidayeSNNPWolaytaRural", strata_count),
         Region = if_else(school_code == 4097322020, "SNNP", Region),
         Location = if_else(school_code == 4097322020, "Rural", Location),
         province = if_else(school_code == 4097322020, "SNNP", province),
         urban_rural = if_else(school_code == 4097322020, "Rural", urban_rural),
         school_weight = if_else(school_code == 4097322020, 142, school_weight)
)

#merge in teacher weights
teacher_absence_weights <- school_weights %>%
  select(school_code, teacher_abs_weight)


teacher_absence_micro <- teacher_absence_micro %>%
  left_join(teacher_absence_weights, by = "school_code")


```


## Teacher Assessment File

```{r teacherassess}
#read in data from difference questionnaire.  This was done because the exams were graded back in the central office.

teacher_assessment_dta <- teacher_assessment_dta %>%
  mutate(
         school_code  = if_else(school_code == 409732 & date == 2020, 4097322020, school_code))

#add weights and anonymize
teacher_assessment_micro <- df_add_weights('teacher_assessment_dta')         %>%
  select(-starts_with('interview__'), -c('lat','lon'))          

teacher_assessment_micro <- teacher_assessment_micro %>% 
  mutate(hashed_school_code = if_else(school_code == 4097322020, "55f7525b6c88fcbf", hashed_school_code),
         hashed_school_province = if_else(school_code == 4097322020, "d3e706fdb56e5000", hashed_school_province),
         hashed_school_district = if_else(school_code == 4097322020, "c5d330755961900a", hashed_school_district),
         sample = if_else(school_code == 4097322020, 12, sample), 
         count = if_else(school_code == 4097322020, 1703, count),
         strata_count = if_else(school_code == 4097322020, "Kindo DidayeSNNPWolaytaRural", strata_count),
         Region = if_else(school_code == 4097322020, "SNNP", Region),
         Location = if_else(school_code == 4097322020, "Rural", Location),
         province = if_else(school_code == 4097322020, "SNNP", province),
         urban_rural = if_else(school_code == 4097322020, "Rural", urban_rural),
         school_weight = if_else(school_code == 4097322020, 142, school_weight)
)

#merge in teacher weights
teacher_assessment_weights <- school_weights %>%
  select(school_code, teacher_weight_component)


teacher_assessment_micro <- teacher_assessment_micro %>%
  left_join(teacher_assessment_weights, by = "school_code")


```



## Teacher Pedagogy File

```{r pedg}

teacher_pedagogy <- final_indicator_data_PEDG %>%
  left_join(school_data_preamble) %>%
  left_join(school_micro_comb %>% select(school_code, starts_with('m4saq1'))) %>%
  distinct(school_code,.keep_all = TRUE)

#add weights and anonymize
teacher_pedagogy_micro <- df_add_weights('teacher_pedagogy') 


```





```{r}
#join the assessment, pedagogy, and questionnaire info to the roster

#start with teacher questionnaire
teacher_combined_df <- teacher_absence_micro %>%
  left_join(teacher_questionnaire_micro %>% mutate(TEACHERS__id=m3sb_tnumber) %>% select(-grade), na_matches='never') %>%
  group_by(school_code,TEACHERS__id) %>%
  slice(1) 


sum(!is.na(teacher_combined_df$m3sb_tnumber))
pct <- round(100*sum(!is.na(teacher_combined_df$m3sb_tnumber))/nrow(teacher_questionnaire_micro))
print(paste0(pct,"% of teachers interviewed for questionnaire are successfully matched"))


# now teacher pedagogy
teacher_combined_df <- teacher_combined_df %>%
  left_join(teacher_pedagogy_micro %>% mutate(TEACHERS__id=m4saq1_number), na_matches='never') %>%
  group_by(school_code,TEACHERS__id) %>%
  slice(1) 


sum(!is.na(teacher_combined_df$m4saq1_number))
pct <- round(100*sum(!is.na(teacher_combined_df$m4saq1_number))/nrow(teacher_pedagogy_micro))
print(paste0(pct,"% of teachers assessed for pedagogy are successfully matched"))



# now teacher content
teacher_combined_df <- teacher_combined_df %>%
  left_join(teacher_assessment_micro %>% mutate(TEACHERS__id=m5sb_tnum), na_matches='never') %>%
  group_by(school_code,TEACHERS__id) %>%
  slice(1) 


sum(!is.na(teacher_combined_df$m5sb_tnum))
pct <- round(100*sum(!is.na(teacher_combined_df$m5sb_tnum))/nrow(teacher_assessment_micro))
print(paste0(pct,"% of teachers assessed for content knowledge are successfully matched"))



```

```{r}
matches <- teacher_combined_df %>%
  mutate(m2saq2=teacher_name) %>%
  select(school_code, TEACHERS__id, m2saq2, m5sb_tnum, m5sb_troster, m3sb_tnumber, m3sb_troster,m4saq1_number, m4saq1) 

```

```{r}

g4_weights <- school_weights %>%
  select(school_code, g4_stud_weight_component)

g1_weights <- school_weights %>%
  select(school_code, g1_stud_weight_component)


teacher_combined_df %>%
  janitor::clean_names() %>%
  write_dta(path=paste0(save_input_folder,"/",country,"/", country,"_teacher_combined_modules.dta"))


matches %>%
  janitor::clean_names() %>%
  write_dta(path=paste0(save_input_folder,"/",country,"/", country,"_teacher_modules_key.dta"))

#save input files
school_micro %>%
  janitor::clean_names() %>%
  write_dta(path=paste0(save_input_folder,"/",country,"/", country,"_school_modules.dta"))

teacher_absence_micro %>%
  mutate(m2saq2=teacher_name) %>%
  janitor::clean_names() %>%
  write_dta(path=paste0(save_input_folder,"/",country,"/", country,"_teacher_absence.dta"))

teacher_pedagogy_micro %>%
  janitor::clean_names() %>%
  write_dta(path=paste0(save_input_folder,"/",country,"/", country,"_teacher_pedagogy.dta"))

teacher_assessment_micro %>%
  janitor::clean_names() %>%
  write_dta(path=paste0(save_input_folder,"/",country,"/", country,"_teacher_assessment.dta"))

teacher_questionnaire_micro %>%
  janitor::clean_names() %>%
  write_dta(path=paste0(save_input_folder,"/",country,"/", country,"_teacher_questionnaire.dta"))

assess_4th_grade_anon <- df_add_weights('assess_4th_grade_anon') 

assess_4th_grade_anon <- assess_4th_grade_anon%>%
  left_join(g4_weights)

assess_4th_grade_anon <- assess_4th_grade_anon %>%
  mutate(
         school_code  = if_else(school_code == 409732 & date == 2020, 4097322020, school_code))
         
assess_4th_grade_anon <- assess_4th_grade_anon %>%
  select(-ends_with('nogiraffe')) %>%
  janitor::clean_names() %>%
  write_dta(path=paste0(save_input_folder,"/",country,"/", country,"_fourth_grade_assessment.dta"))

ecd_dta_anon <- df_add_weights('ecd_dta_anon') 

ecd_dta_anon <- ecd_dta_anon%>%
  left_join(g1_weights)

ecd_dta_anon <- ecd_dta_anon %>%
  mutate(
         school_code  = if_else(school_code == 409732 & date == 2020, 4097322020, school_code))

ecd_dta_anon <- ecd_dta_anon %>%
  janitor::clean_names() %>%
  write_dta(path=paste0(save_input_folder,"/",country,"/", country,"_first_grade_assessment.dta"))

```


