---
title: "Gabon Teacher Linkages"
format: html
---

# Introduction

This analysis will link the teacher modulese using teacher IDs and names and then do some basic analysis.

Teachers can be linked by a common ID.  The following are the column names in the various files

* Teacher pedagogy: m4saq1_number
* Teacher Content Knowledge: m5sb_tnum
* Teacher Questionnaire: m3sb_tnumber
* Teacher Roster: TEACHERS__id

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	fig.height = 6,
	fig.width = 8,
	message = FALSE,
	warning = FALSE
)
library(tidyverse)
library(haven)
library(vtable)
library(here)
library(readxl)
library(stringr)
library(Hmisc)
library(naniar)
library(lubridate)
library(skimr)
library(digest)
library(validate)
library(GGally)
library(Hmisc)
#Country name
country <-'GAB'
country_name <- "Gabon"
year <- '2023'
school_file <-'EPDash.dta'
#########################
# File paths #
#########################
#The download_folder will be the location of where raw data is downloaded from the API
#The save_folder will be the location of where cleaned data is stored



if (str_to_lower(Sys.getenv("USERNAME")) == "wb469649" ){
  #project_folder  <- "//wbgfscifs01/GEDEDU/datalib-edu/projects/gepd"
  project_folder  <- "C:/Users/wb469649/WBG/HEDGE Files - HEDGE Documents/GEPD-Confidential/"
  download_folder <-file.path(paste(project_folder,"CNT",country,paste(country,year,"GEPD", sep="_"),paste(country,year,"GEPD_v01_RAW", sep="_"),"Data/raw/School/", sep="/"))
  sampling_folder <-file.path(paste(project_folder,"CNT",country,paste(country,year,"GEPD", sep="_"),paste(country,year,"GEPD_v01_RAW", sep="_"),"Data/sampling", sep="/"))
  confidential_folder <- file.path(paste(project_folder,"CNT",country,paste(country,year,"GEPD", sep="_"),paste(country,year,"GEPD_v01_RAW", sep="_"),"Data/confidential/School", sep="/"))
  save_input_folder <- file.path(paste0(project_folder,"General/LEGO_Teacher_Paper/3_input_data"))
  save_output_folder <- file.path(paste0(project_folder,"General/LEGO_Teacher_Paper/5_output_data"))

} else if  (str_to_lower(Sys.getenv("USERNAME")) == "wb577189" ){
  #project_folder  <- "//wbgfscifs01/GEDEDU/datalib-edu/projects/gepd"
  project_folder  <- "C:/Users/wb577189/OneDrive - WBG/GEPD-Confidential/CNT/"
  download_folder <-file.path(paste(project_folder,"/CNT/",country,paste(country,year,"GEPD", sep="_"),paste(country,year,"GEPD_v01_RAW", sep="_"),"Data/raw/School", sep="/"))
  sampling_folder <-file.path(paste(project_folder,"/CNT/",country,paste(country,year,"GEPD", sep="_"),paste(country,year,"GEPD_v01_RAW", sep="_"),"Data/sampling", sep="/"))
  confidential_folder <- file.path(paste(project_folder,"/CNT/",country,paste(country,year,"GEPD", sep="_"),paste(country,year,"GEPD_v01_RAW", sep="_"),"Data/confidential/School", sep="/"))
  save_input_folder <- file.path(paste0(project_folder,"General/LEGO_Teacher_Paper/3_input_data"))
  save_output_folder <- file.path(paste0(project_folder,"General/LEGO_Teacher_Paper/5_output_data"))

} else {
  download_folder <- choose.dir(default = "", caption = "Select folder to open data downloaded from API")
  save_folder <- choose.dir(default = "", caption = "Select folder to save final data")

}


```

```{r functions}



#function to attach weights

#function to attach weights

df_weights_function <- function(dataset,scode, snumber, prov) {
  scode<-enquo(scode)  
  snumber<-enquo(snumber)
  prov<-enquo(prov)
  
  dataset %>%
    left_join(data_set_updated)  %>%
    mutate(province=Province,
           district=Département) %>%
    mutate(ipw=if_else(is.na(ipw), median(ipw, na.rm=T), ipw) ) 
    
}

df_add_weights<- function(dataset) {
  temp<-get(dataset) 
    
    #add hashed school code if needed
    if ("school_code" %in% colnames(temp)) {
      temp <- temp %>%
        left_join(key) %>%
        select(hashed_school_code, hashed_school_province, hashed_school_district, everything())
    }
    
    
    #add on weights
    if ("school_code" %in% colnames(temp)) {
      temp <- df_weights_function(temp, Inst_ID, totalstudents, District) 
    }
}

```

```{r}
#list of key indicators

ind_list<-c('student_knowledge', 'math_student_knowledge', 'literacy_student_knowledge', 
            'student_proficient', 'student_proficient_70', 'student_proficient_75',
            'literacy_student_proficient', 'literacy_student_proficient_70', 'literacy_student_proficient_75',
            'math_student_proficient', 'math_student_proficient_70', 'math_student_proficient_75',
            'presence_rate','absence_rate', 'sch_absence_rate', 'student_attendance',
            'content_knowledge', 'math_content_knowledge', 'literacy_content_knowledge', 
            'content_proficiency',  'content_proficiency_70', 'content_proficiency_75',
            'literacy_content_proficiency',  'literacy_content_proficiency_70', 'literacy_content_proficiency_75',
            'math_content_proficiency',  'math_content_proficiency_70', 'math_content_proficiency_75',
            'teach_score','classroom_culture','instruction','socio_emotional_skills',
            'teach_prof','classroom_culture_prof','instruction_prof','socio_emotional_skills_prof',
            'ecd_student_proficiency', 'ecd_math_student_proficiency', 'ecd_literacy_student_proficiency', 'ecd_exec_student_proficiency', 'ecd_soc_student_proficiency',
            'ecd_student_knowledge', 'ecd_math_student_knowledge', 'ecd_literacy_student_knowledge', 'ecd_exec_student_knowledge', 'ecd_soc_student_knowledge',
            'inputs', 'blackboard_functional', 'pens_etc', 'textbooks', 'share_desk', 'used_ict', 'access_ict',
            'infrastructure','drinking_water', 'functioning_toilet', 'internet', 'class_electricity','disability_accessibility','disab_road_access', 'disab_school_ramp', 'disab_school_entr', 'disab_class_ramp', 'disab_class_entr', 'disab_screening',
            'operational_management', 'vignette_1', 'vignette_1_resp', 'vignette_1_finance', 'vignette_1_address', 'vignette_2', 'vignette_2_resp', 'vignette_2_finance', 'vignette_2_address', 
            'intrinsic_motivation', 'acceptable_absent', 'students_deserve_attention', 'growth_mindset', 'motivation_teaching',
            'instructional_leadership', 'classroom_observed', 'classroom_observed_recent', 'discussed_observation', 'feedback_observation', 'lesson_plan_w_feedback',
            'principal_knowledge_score', 'add_triple_digit_pknw', 'multiply_double_digit_pknw', 'complete_sentence_pknw', 'experience_pknw', 'textbooks_pknw', 'blackboard_pknw',
            'principal_management', 'sch_goals_exist','sch_goals_clear','sch_goals_relevant','sch_goals_measured',
            'teacher_attraction', 'teacher_satisfied_job', 'teacher_satisfied_status', 'better_teachers_promoted' ,'teacher_bonus', 'salary_delays',
            'teacher_selection_deployment', 'teacher_selection','teacher_deployment',
            'teacher_support', 'pre_service','practicum','in_service','opportunities_teachers_share',
            'teaching_evaluation', 'formally_evaluated', 'evaluation_content', 'negative_consequences','positive_consequences',
            'teacher_monitoring','attendance_evaluated' , 'attendance_rewarded' , 'attendence_sanctions', 'miss_class_admin',
            'sch_management_clarity', 'infrastructure_scfn','materials_scfn','hiring_scfn', 'supervision_scfn', 'student_scfn' , 'principal_hiring_scfn', 'principal_supervision_scfn',
            'standards_monitoring',
            'sch_monitoring', 'monitoring_inputs','monitoring_infrastructure','system_in_place','parents_involved',
            'sch_management_attraction', 'principal_satisfaction',
            'sch_selection_deployment', 
            'sch_support', 'prinicipal_trained','principal_training','principal_used_skills','principal_offered',
            'principal_evaluation', 'principal_formally_evaluated','principal_evaluation_multiple','principal_negative_consequences','principal_positive_consequences'
)

#attach derived indicators
attach(paste0(confidential_folder,"/school_survey_data.RData"))

```


## Weights File

```{r}
#read in the file on school weights
#Load original sample of schools
currentDate<-c("2023-08-09")

#load school code file
school_codes <- read_csv(file.path(confidential_folder, "school_idfile_hashed.csv")) %>% 
  mutate(school_name_preload = gsub("[[:punct:]]", " ", school_name_preload),
         school_name_preload = str_squish(school_name_preload),
         school_name_preload = iconv(school_name_preload,to="ASCII//TRANSLIT")) %>% 
  rename(old_school_code = school_code) %>% 
  mutate(school_code = paste(school_name_preload, "_", temp_school_code))

sample_folder <- file.path(paste(project_folder,"/CNT/",country,paste(country,year,"GEPD", sep="_"),paste(country,year,"GEPD_v01_RAW", sep="_"),"Data/sampling/", sep="/"))
data_set_updated <- read_csv(paste(sample_folder, '/GEPD_GAB_weights_revised_', currentDate,  '.csv', sep="")
)  %>% 
  left_join(school_codes %>% select(-school_name_preload), by = c("school_code")) %>%
  select(school_code,school_name_preload, Province, Département, private, public, rural ,urban_rural,
         ipw) 





key <- read_csv(file.path(confidential_folder, "EPDash_linkfile_hashed.csv"))
```

## School File

```{r school}

###########################
#read in school level file
###########################

##School
school_dta<-read_dta(file.path(download_folder, "EPDash.dta"))
#rename a few key variables up front
school_dta<- school_dta %>%
  mutate(enumerator_name_other= m1s0q1_name_other  ,
         enumerator_number=m1s0q1_name ,
         survey_time=m1s0q8,
         lat=m1s0q9__Latitude,
         lon=m1s0q9__Longitude,
         school_emis_preload=if_else(school_name_preload=='ECOLE PUBLIQUE RURALE ASSOK MEDZENG' ,'0901103006X507',school_emis_preload),
         #temp_school_code=if_else(!is.na(school_emis_preload),as.character(school_emis_preload), as.character(m1s0q2_code)),
         m7_teach_count_pknw=m7_teach_count, #this variable was mistakenly not tagged as pknw
         total_enrolled=m1saq7) %>%
  
  mutate(school_name_preload = case_when(
    
    interview__key == "06-80-44-02" ~ "COMPLEXE SCOLAIRE PRIVE BILINGUE LE CEP",
    interview__key=="47-94-03-65" ~ "COMPLEXE SCOLAIRE PRIVE BILINGUE LE CEP",
    TRUE ~ school_name_preload

  )) %>% 
  
  ## Create new temp code that combined the EMIS code and the name
  mutate(temp_school_code = paste(school_name_preload, "_", school_emis_preload)) %>% 
  
  # ## Get names and code for all the blank interviews
  # mutate(
  #   
  #   temp_school_code= if_else(school_info_correct==1, as.character(temp_school_code), as.character(m1s0q2_emis)),
  #   school_name_preload = if_else(school_info_correct==1, as.character(school_name_preload), as.character(m1s0q2_name)),
  #   #fix some school names
  #   school_name_preload= str_remove_all(school_name_preload, '^"|"$'),
  #   school_name_preload= gsub('""', '"', school_name_preload),
  #   # clean up some manually entered values
  #   school_name_preload = case_when(
  #     school_emis_preload=='0302201009X502' ~ 'ECOLE PRIVEE CATHOLIQUE SAINT RUFFIN DE NZOGHE BANG',
  #     school_emis_preload=='0202402005X505' ~ 'COMPLEXE SCOLAIRE PRIVE SAINT BILL',
  #     school_emis_preload=='0101303165X513' ~ 'ECOLE PUBLIQUE COMMUNALE DE BAKELE',
  #     school_emis_preload=='0202402001X510' ~ 'COMPLEXE SCOLAIRE NANETTE',
  #     school_emis_preload=='0801402060X524' ~ 'ETABLISSEMENT SCOLAIRE PRIVE LE GUIDE',
  #     school_emis_preload=='0402201007X514' ~ 'SAINTE FAMILLE DE FOUGAMOU',
  #     school_emis_preload=='0106401054X506' ~ 'COMPLEXE SCOLAIRE BILINGUE LES THEOPHILES',
  #     TRUE ~ school_name_preload
  #   ),
  #   temp_school_code = case_when(
  #     school_emis_preload=='0302201009X502' ~ '0302201009X502',
  #     school_emis_preload=='0202402005X505' ~ '0202402001X510',
  #     school_emis_preload=='0101303165X513' ~ '0701401008X502',
  #     school_emis_preload=='0202402001X510' ~ '0202402005X505',
  #     school_emis_preload=='0801402060X524' ~ '0801402060X524',
  #     school_emis_preload=='0402201007X514' ~ '0402201007X514',
  #     school_emis_preload=='0106401054X506' ~ '0106401054X506',
  #     TRUE ~ temp_school_code
  #   )
  # ) %>%
  select(-starts_with("enumerators_preload")) %>% #bring in school codes that were created in separate stata program
  filter(!is.na(temp_school_code)) %>%
  ungroup() %>%
  left_join(key) %>%
  filter(!is.na(temp_school_code)) %>% 
  select(-school_code) %>% 
  mutate(school_code = school_emis_preload) %>% 
  
  ## VERY IMPORTANT FOR MATCHING LATER ON
  
 mutate(school_name_preload = gsub("[[:punct:]]", " ", school_name_preload),
         school_name_preload = str_squish(school_name_preload),
         school_name_preload = iconv(school_name_preload,to="ASCII//TRANSLIT")) %>% 
  
  ##Manual cleaning for the 12 schools that don't match on names
  mutate(school_name_preload = case_when(
    
    temp_school_code == "ECOLE MARTIN LUTHER KING _ 0101301088X506" ~ "ECOLE BILINGUE MARTIN LUTHER KING",
   temp_school_code == "COMPLEXE SCOLAIRE FRANCO-ARABE A OZANGUE _ 0101305188x524" ~ "ECOLE PUBLIQUE D OZANGUE",
   temp_school_code =="COMPLEXE SCOLAIRE LA MAISON DE DAVID 3 _ 0101301002X504" ~ "COMPLEXE SCOLAIRE MAISON DE DAVID 3",
   temp_school_code == "COMPLEXE SCOLAIRE LES OLIVIER VERDOYANT _ 0101306005X510" ~ "OLIVIERS VERDOYANTS",
   temp_school_code == "COMPLEXE SCOLAIRE REHMA _ " ~ "COMPLEXE SCOLAIRE LA PATIENCE RIMA",
   temp_school_code == "ECOLE PRIVEE LAÏC BILINGUE LES ECLAIREURS _ " ~ "COMPLEXE SCOLAIRE PRIVE BILINGUE LES LEADERS",
   temp_school_code == "ECOLE PRIVEE LAÏQUE  LA CONQUÊTE _ "~ "COMPLEXE SCOLAIRE PRIVE LA CONQUETE DU PETIT CHEMINOT",
   T ~ school_name_preload
    
  )) %>% 
  
  rename(old_school_code = school_code) %>% 
  mutate(school_code = paste(school_name_preload, "_", old_school_code))
  





school_micro_raw <- school_dta %>%
  group_by(school_code) %>%
  fill(everything(), .direction='downup') %>%
  slice(1) %>% 
  ungroup()


var.list <- sapply(school_dta, function(x) attr(x,"label"))
var.labels= unlist(var.list)


#merge on derived indicators
school_micro_comb <- school_micro_raw %>%
  left_join(
    school_dta_short %>%
      select(school_code, ind_list)
  ) %>%
  select(colnames(school_data_preamble), ind_list, everything())

#add weights and anonymize
school_micro <- df_add_weights('school_micro_comb')                   

#school_micro <- Hmisc::upData(school_micro, labels = var.labels)

```


```{r}
#create a file for matching to tecaher and student files

#list additional info that will be useful to keep in each indicator dataframe
preamble_info <- c( 'interview__key', 'school_code',
                   'school_name_preload', 
                   'school_province_preload', 'school_district_preload', 'school_emis_preload', 'school_emis_preload',
                   'school_info_correct', 'm1s0q2_name', 'm1s0q2_code', 'm1s0q2_emis',
                   'survey_time', 'lat', 'lon' , 'total_enrolled' , 'm7saq10'
                   )

drop_school_info <- c(

)


#create school database with just preamble info.  This will be useful for merging on school level info to some databases
school_data_preamble_temp <- school_dta %>%
  group_by(school_code) %>%
  select( preamble_info) %>%
  select(-interview__key) %>%
  summarise_all( ~(if(is.numeric(.)) mean(., na.rm = TRUE) else first(.))) 
  
school_data_preamble <- school_dta %>%
  group_by(interview__key) %>%
  select(interview__key, school_code) %>%
  left_join(school_data_preamble_temp)
```


## Teacher Questionnaire File

```{r}

teacher_questionnaire<-read_dta(file.path(download_folder, "questionnaire_roster.dta")) 
#Add school preamble info
teacher_questionnaire <- teacher_questionnaire %>%
  left_join(school_data_preamble) %>%
  select(preamble_info, everything())



#add weights and anonymize
teacher_questionnaire_micro <- df_add_weights('teacher_questionnaire')      %>%
  select(-starts_with('interview__'), -c('lat','lon'))              

```


## Teacher Absence File

```{r}
############################
#read in teacher roster file
############################

teacher_absence_dta<-read_dta(file.path(download_folder, "TEACHERS.dta")) 
#Add school preamble info
teacher_absence_dta <- teacher_absence_dta %>%
  left_join(school_data_preamble) %>%
  select(preamble_info, everything()) 

#merge on derived indicators
teacher_absence_dta_comb <- teacher_absence_dta %>%
  left_join(
    teacher_absence_final %>%
      select(school_code, TEACHERS__id, contains(ind_list))
  ) %>%
  distinct(school_code, TEACHERS__id, .keep_all = TRUE)

#add weights and anonymize
teacher_absence_micro <- df_add_weights('teacher_absence_dta_comb')       %>%
  select(-starts_with('interview__'), -c('lat','lon'))             


```


## Teacher Assessment File

```{r teacherassess}
#read in data from difference questionnaire.  This was done because the exams were graded back in the central office.
teacher_assessment_dta_raw <- read_dta(file.path(download_folder, "teacher_assessment_answers.dta")) %>%
  left_join(school_data_preamble) %>%
  select(preamble_info, everything()) 

#merge on derived indicators
teacher_assessment_dta_comb <- teacher_assessment_dta_raw %>%
  left_join(
    teacher_assessment_dta %>%
      select(school_code, teacher_assessment_answers__id, contains(ind_list))
  ) %>%
  distinct(school_code, teacher_assessment_answers__id, .keep_all = TRUE)


#add weights and anonymize
teacher_assessment_micro <- df_add_weights('teacher_assessment_dta_comb')         %>%
  select(-starts_with('interview__'), -c('lat','lon'))          


```



## Teacher Pedagogy File

```{r pedg}




teacher_pedagogy <- school_micro_raw %>%
  select(preamble_info, starts_with('m4saq1'), starts_with('s1'), starts_with('s2'),starts_with('m4s') )

  
#add weights and anonymize
teacher_pedagogy_micro <- df_add_weights('teacher_pedagogy') %>%
  select(-starts_with('interview__')) 


```



```{r}
#join the assessment, pedagogy, and questionnaire info to the roster

#start with teacher questionnaire
teacher_combined_df <- teacher_absence_micro %>%
  left_join(teacher_questionnaire_micro %>% mutate(TEACHERS__id=m3sb_tnumber), na_matches='never') %>%
  group_by(school_code,TEACHERS__id) %>%
  slice(1) 


sum(!is.na(teacher_combined_df$m3sb_tnumber))
pct <- round(100*sum(!is.na(teacher_combined_df$m3sb_tnumber))/nrow(teacher_questionnaire_micro))
print(paste0(pct,"% of teachers interviewed for questionnaire are successfully matched"))


# now teacher pedagogy
teacher_combined_df <- teacher_combined_df %>%
  left_join(teacher_pedagogy_micro %>% mutate(TEACHERS__id=m4saq1_number), na_matches='never') %>%
  group_by(school_code,TEACHERS__id) %>%
  slice(1) 


sum(!is.na(teacher_combined_df$m4saq1_number))
pct <- round(100*sum(!is.na(teacher_combined_df$m4saq1_number))/nrow(teacher_pedagogy_micro))
print(paste0(pct,"% of teachers assessed for pedagogy are successfully matched"))





# now teacher content
teacher_combined_df <- teacher_combined_df %>%
  left_join(teacher_assessment_micro %>% mutate(TEACHERS__id=m5sb_tnum), na_matches='never') %>%
  group_by(school_code,TEACHERS__id) %>%
  slice(1) 


sum(!is.na(teacher_combined_df$m5sb_tnum))
pct <- round(100*sum(!is.na(teacher_combined_df$m5sb_tnum))/nrow(teacher_assessment_micro))
print(paste0(pct,"% of teachers assessed for content knowledge are successfully matched"))



```

```{r}
matches <- teacher_combined_df %>%
  select(school_code, grade_joined, TEACHERS__id, m2saq2, m5sb_tnum, m5sb_troster, m3sb_tnumber, m3sb_troster,m4saq1_number, m4saq1)


```

```{r}

teacher_combined_df %>%
  janitor::clean_names() %>%
  write_dta(path=paste0(save_input_folder,"/",country,"/", country,"_teacher_combined_modules.dta"))


matches %>%
  janitor::clean_names() %>%
  write_dta(path=paste0(save_input_folder,"/",country,"/", country,"_teacher_modules_key.dta"))

#save input files
school_micro %>%
  janitor::clean_names() %>%
  write_dta(path=paste0(save_input_folder,"/",country,"/", country,"_school_modules.dta"))

teacher_absence_micro %>%
  janitor::clean_names() %>%
  write_dta(path=paste0(save_input_folder,"/",country,"/", country,"_teacher_absence.dta"))

teacher_pedagogy_micro %>%
  janitor::clean_names() %>%
  write_dta(path=paste0(save_input_folder,"/",country,"/", country,"_teacher_pedagogy.dta"))

teacher_assessment_micro %>%
  janitor::clean_names() %>%
  write_dta(path=paste0(save_input_folder,"/",country,"/", country,"_teacher_assessment.dta"))

teacher_questionnaire_micro %>%
  janitor::clean_names() %>%
  write_dta(path=paste0(save_input_folder,"/",country,"/", country,"_teacher_questionnaire.dta"))

assess_4th_grade_anon %>%
  select(-ends_with('nogiraffe')) %>%
  janitor::clean_names() %>%
  write_dta(path=paste0(save_input_folder,"/",country,"/", country,"_fourth_grade_assessment.dta"))

ecd_dta_anon %>%
  janitor::clean_names() %>%
  write_dta(path=paste0(save_input_folder,"/",country,"/", country,"_first_grade_assessment.dta"))
```


