---
title: "Ethiopia Weights"
author: "Brian Stacy"
date: "2/24/2021"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#load relevant libraries
library(rgdal)
library(tidyverse)
library(readxl)
library(leaflet)
library(kableExtra)
library(DT)
library(skimr)
library(haven)
library(crosstalk)
library(purrr)
library(dtplyr)
set.seed(54351324)

#################################
#Specify Directories, etc
#################################

#Specify directory where sampling frame located
#Specify directory where sampling frame located
dir_frame<-"C:/Users/wb469649/WBG/Ezequiel Molina - Dashboard (Team Folder)/Country_Work/Ethiopia/2020/Data/Sampling/Primary_schools_STATA/"

#specify name of sampling frame file.  This needs to be a csv file
file_frame<-"ETH_sampling_data.dta"
#specify name of sampling frame file.  This needs to be a csv file
public_file_frame<-"Primary_schools_ETH.csv"
#specify date that sample was created.  This may be useful if you want to access stored results
#date_frame<-c("2019-07-22")

date_frame<-c("2020-02-07")

#################################
#read in sampling frame from [XXX]
#################################


dat=read_csv(paste(dir_frame, public_file_frame, sep="/"))


#reshape frame to be one observation per row
# do some prep work first



#drop some observations that are coded Lang==2
df <- dat %>%
  filter(Lang=='includes all')

#keep just Grade 4 and Grade 1
df <- df %>%
  filter(Grade=="Grade 1" | Grade=="Grade 4")


#Database is at the schoolXclass level.  Aggregate to schoolXgrade
df<- df %>%
  group_by(Region, Zone, Woreda, School_Name, Sector, owner, Location, Program, Admin_Code, Code_School,  Grade) %>%
  summarise(
            M=sum(M),
            F=sum(F)
            ) %>%
  arrange(Admin_Code, Grade) %>%
  group_by(Admin_Code) %>%
  mutate(grd4_male=M,
         grd4_female=F,
         grd1_male=first(M),
         grd1_female=first(F)) %>%
  mutate(grd4_total=grd4_male+grd4_female,
         grd1_total=grd1_male+grd1_female) %>%
  filter(Grade=="Grade 4") %>%
  select(-M, -F)
  


```

# Introduction

This file outlines the sampling strategy in Ethiopia for the Global Education Policy Dashboard.

## General Notes on Sampling

Overall, we draw a sample of 300 public schools from each of the regions of Ethiopia.  As a comparison to the total number of schools in Ethiopia, this consistutes an approximately 1% sample.  Because of the large size of the country, and because there can be very large distances between Woredas within the same region, we chose a cluster sampling approach.  In this approach, 100 Woredas were chosen with probability proportional to 4th grade size.  Then within each Woreda two rural and one urban school were chosen with probability proportional to 4th grade size.

## Particular Notes


In order to deal with potential refusals and closed schools, a set of replacement schools was also drawn.  Because it is important to match the language of instruction with the replacement school, we select replacement schools from within the same Woreda.  




## Sampling Frame

Our school database consists of primarily public schools, with a mix of other ownership types.  We will restrict our sample frame to only public and private schools in Ethiopia, omitting religious schools.  Our school sampling frame contains information on region, zone, Woreda, along with ownership, urban/rural status, and the number of students in each grade.  Information on the number of students is based on the 2011 E.C.

Our sampling frame will be restricted also to schools with at least three 1st grade and at least 3 4th grade students.


There was a concern that some zones posed a security risk for the enumerators.  As a result this list of Zones were excluded.


|    region     |    zone                         |           
|---------------|---------------------------------|
|    Oromiya    |    Wallagaa   Lixaa             |          
|    Oromiya    |    Wallagaa   Bahaa             |          
|    Oromiya    |    Horroo   Guduru Wallaggaa    |                   
|    Oromiya    |    Qellam   Wallaggaa           |           
|    Oromiya    |    Wallagaa   Lixaa             |       



```{r ownership, echo=FALSE}

zone_list<-c('Wallagaa Lixaa', 'Wallagaa Bahaa', 'Horroo Guduru Wallaggaa', 'Qellam Wallaggaa')


#keep just private and government schools, omitting religious schools
df <- df %>%
  filter(owner=="Government" | owner=="Private") %>%
  filter(grd4_total>=3 & grd1_total>=3) %>%
  filter(!(Zone %in% zone_list)) 

#keep Woredas with at least three schools
df <- df %>%
  group_by(Region, Woreda) %>%
  filter(n()>=3) %>%
  ungroup()

#Some summary stats and descriptives
ggplot(data=df, aes(owner)) +
  geom_histogram(stat='count') +
  stat_count(aes(y=..count..,label=..count..),geom="text",hjust=-.5) +
  coord_flip() +
  expand_limits(y=40000) +
  theme_bw() +
  ggtitle(str_wrap("Counts of the Number of Schools by Ownership Type in Sampling Frame",55))

#Some summary stats and descriptives
ggplot(data=df, aes(Location)) +
  geom_histogram(stat='count') +
  stat_count(aes(y=..count..,label=..count..),geom="text",hjust=-.5) +
  coord_flip() +
  expand_limits(y=40000) +
  theme_bw() +
  ggtitle(str_wrap("Counts of the Number of Schools by Urban/Rural Type in Sampling Frame",55))


#Some summary stats and descriptives
ggplot(data=df, aes(Region)) +
  geom_histogram(stat='count') +
  stat_count(aes(y=..count..,label=..count..),geom="text",hjust=-.5) +
  coord_flip() +
  expand_limits(y=40000) +
  theme_bw() +
  ggtitle(str_wrap("Counts of the Number of Schools by Region in Sampling Frame",55))


#Some summary stats and descriptives
ggplot(data=df, aes(Region, grd4_total)) +
  geom_histogram(stat='identity') +
  stat_summary(fun.y = sum, aes(label = ..y..), geom = "text",hjust=-.5) +
  coord_flip() +
  expand_limits(y=1250000) +
  theme_bw() +
  ggtitle(str_wrap("Counts of the Number of Students by Region in Sampling Frame",55))

domains<-df %>% group_by(Region) %>% summarise(n=n())
```


# Sampling of Schools in Woredas


Schools will be selected using stratified, cluster random sampling.  The sample is stratified by Region and the urban/rural status of the school.  100 Woredas will be selected at random with probability proportional to the 4th grade student population of the Woreda.   Once the Woredas are chosen a sample of 3 schools in each Woreda will be selected, with two of those schools rural and one urban.

# weights

Weights are produced by resampling 10,000 times. Each school's weight is the proportion of times the school is selected using our procedure across the 10,000 repetitions.

```{r weights_calc, echo=FALSE}

sampling_proc <-  function(number) {
  
  set.seed(number)
  
  tryCatch({
    
    
    #create frame with the number of students per woreda
    sample_woredas <- df %>%
      group_by(Region, Woreda) %>%
      summarise(n_stud_woreda=sum(grd4_total)) %>%
      sample_n(size=if_else(0.115*n()>2,0.115*n(),2), weight=n_stud_woreda) %>%  #choose at least 2 woredas per region
      ungroup() %>%
      sample_n(size=100, weight=n_stud_woreda) %>% #slightly over sampled so get down to 100 randomly
      arrange(Region, Woreda) %>%
      mutate(sampled_woreda="Sampled Woreda")
    
    
    school_sample_df <- df %>%
      left_join(sample_woredas) %>%
      filter(!is.na(sampled_woreda)) %>%
      group_by(Region, Woreda) %>%
      mutate(num_urban=sum(Location=="Urban"),
             num_schools=n() )%>%
      ungroup()
    
    school_sample_urban <- school_sample_df %>%
      filter(Location=="Urban") %>%
      group_by(Region, Woreda) %>%
      mutate(size_samp=case_when(
        num_schools-num_urban==0 ~ 3,
        num_schools-num_urban==1 ~ 2,
        num_schools-num_urban>=2 ~ 1,
        num_urban==0 | is.na(num_urban) ~ 0
      )) %>% #select 1 urban if there are 2 rural, but more if there are less than two rural
      sample_n(size=size_samp, weight=grd4_total)
    
    school_sample_rural <- school_sample_df %>%
      filter(Location=="Rural") %>%
      group_by(Region, Woreda) %>%
      mutate(size_samp=case_when(
        (num_urban==0 | is.na(num_urban))   ~ 3,
        num_schools-num_urban==1 ~ 1,
        num_schools-num_urban==0 ~ 0,
        TRUE ~ 2
      )) %>% #select 2 rural if there is 1 urban, but more if there are less than one urban
      sample_n(size=size_samp)
    
    #append rural and urban samples together
    
    bind_rows(school_sample_rural, school_sample_urban) %>%
      arrange(Region, Woreda) %>%
      mutate(sample=1) %>%
      right_join(df) %>%
      mutate(sample=if_else(sample==1,1,0)) %>%
      select(Region, Zone, Woreda, School_Name, Sector, owner, Location, Program, Admin_Code, Code_School, sample)
  }, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
}

#now sample 10000 times
weights_df <- data.frame(num = c(1:10000)) %>%
  mutate(numbers=num) %>%
  nest(numbers)  %>%
  mutate(
    trial_data=map(
      data,
      ~sampling_proc(.x$numbers)
    )
  ) %>%
  unnest(trial_data) %>%
  select(-data) %>%
  dtplyr::lazy_dt()

weights_df <- weights_df %>%
  group_by(Region, Zone, Woreda, School_Name, Sector, owner, Location, Program, Admin_Code, Code_School ) %>%
  summarise( sample=sum(sample, na.rm=T),
             count=n()) %>%
  mutate(ipw=sample/count) %>%
  as_tibble()

write_excel_csv(weights_df, file="C:/Users/wb469649/WBG/Ezequiel Molina - Dashboard (Team Folder)/Country_Work/Ethiopia/2020/Data/Sampling/Ethiopia_weights.csv")
```

