---
title: "Ethiopia Global Education Policy Dashboard Survey Sampling"
author: "Brian Stacy"
date: "12/23/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#load relevant libraries
library(rgdal)
library(tidyverse)
library(readxl)
library(leaflet)
library(kableExtra)
library(DT)
library(skimr)
library(haven)
library(crosstalk)
library(purrr)
set.seed(54351324)

#################################
#Specify Directories, etc
#################################

#Specify directory where sampling frame located
#Specify directory where sampling frame located
dir_frame<-"C:/Users/wb469649/WBG/Ezequiel Molina - Dashboard (Team Folder)/Country_Work/Ethiopia/2019/Data/Sampling/"

#specify name of sampling frame file.  This needs to be a csv file
file_frame<-"ETH_sampling_data.dta"
#specify name of sampling frame file.  This needs to be a csv file
public_file_frame<-"ETH_sampling_data.dta"
old_file_frame<-"Sampling_Frame_2009.dta"
#specify date that sample was created.  This may be useful if you want to access stored results
#date_frame<-c("2019-07-22")

date_frame<-c("2019-12-23")

#################################
#read in sampling frame from [XXX]
#################################


df=read_stata(paste(dir_frame, public_file_frame, sep="/"))
alt_df=read_stata(paste(dir_frame, old_file_frame, sep="/"))

#change names to lowercase
colnames(alt_df) <-  tolower(colnames(alt_df))
#convert to common names
alt_df<-alt_df %>%
  mutate(school=school_name,
         school_code = seq.int(nrow(alt_df))
)

```

# Introduction

This file outlines the sampling strategy in Ethiopia for the Global Education Policy Dashboard.

## General Notes on Sampling

Overall, we draw a sample of 300 public schools from each region of Ethiopia.  As a comparison to the total number of schools in Ethiopia, this consistutes an approximately 1% sample.  

Our sampling frame contains no school information beyond the ownership, Region, Zone, and Woreda.  Because of this, we take a simple 1% random sample within each region.  See discussion below for how sample weights are constructed.


## Particular Notes


In order to deal with potential refusals and closed schools, a set of replacement schools was also drawn.  Because it is important to match the language of instruction with the replacement school, we select replacement schools from within the same Woreda.  

Detailed information on the number of students from schools is missing from our sampling frame, so we match to an older school census from 2009 for counts of the number of students. This process led to an imperfect number of matches at the school level. For survey weight purposes, we first calculate the number of students at the region level based on the 2009 census.  Then we hand match, when necessary, the list of 300 schools chosen in our sampling frame to the 2009 census to merge the student counts.  The survey weights are then based on the number of 4th grade students in the school from the 2009 census.  If the government provides updated information on the number of students per school, the weights will be updated with this information.  






## Sampling Frame

Our school database consists of primarily public schools, with a mix of other ownership types.  We will restrict our sample frame to only public schools in Ethiopia.  The frame includes only school labelled as Primary Education schools.

Finally, we compare the 2009 census of schools to our current list of schools, which contains no information on the number of students per school.  Overall, the number of schools in our sampling frame exceed the number in the 2009 census by around 3,000 schools (36,466 compared to 33,462).  We then display the number of schools in our current sampling frame by region, the number of schools in the 2009 census by region, and finally the number of 4th grade students by region according to the 2009 census.





```{r ownership, echo=FALSE}


#change names to lowercase
colnames(df) <-  tolower(colnames(df))

#fix a typo in government ownership
df<- df %>%
  mutate(ownership=if_else(ownership=="Goverment", "Government", ownership))


#Some summary stats and descriptives
ggplot(data=df, aes(ownership)) +
  geom_histogram(stat='count') +
  stat_count(aes(y=..count..,label=..count..),geom="text",hjust=-.5) +
  coord_flip() +
  expand_limits(y=40000) +
  theme_bw() +
  ggtitle(str_wrap("Counts of the Number of Schools by Ownership Type in Sampling Frame",55))

#Some summary stats and descriptives
ggplot(data=df, aes(sector)) +
  geom_histogram(stat='count') +
  stat_count(aes(y=..count..,label=..count..),geom="text",hjust=-.5) +
  coord_flip() +
  expand_limits(y=40000) +
  theme_bw() +
  ggtitle(str_wrap("Counts of the Number of Schools by Primary Type in Sampling Frame",55))

#Some summary stats and descriptives
ggplot(data=df, aes(region)) +
  geom_histogram(stat='count') +
  stat_count(aes(y=..count..,label=..count..),geom="text",hjust=-.5) +
  coord_flip() +
  expand_limits(y=40000) +
  theme_bw() +
  ggtitle(str_wrap("Counts of the Number of Schools by Region in Sampling Frame",55))

#Some summary stats and descriptives
ggplot(data=alt_df, aes(region)) +
  geom_histogram(stat='count') +
  stat_count(aes(y=..count..,label=..count..),geom="text",hjust=-.5) +
  coord_flip() +
  expand_limits(y=40000) +
  theme_bw() +
  ggtitle(str_wrap("Counts of the Number of Schools by Region using 2009 Data",55))


#Some summary stats and descriptives

alt_df %>%
  group_by(region) %>%
  summarise(enrollment_g4=sum(enrollment_total4, na.rm=T)) %>%
  ggplot(aes(x=region, y=enrollment_g4)) +
  geom_bar(stat='identity') +
  geom_text(aes(label=enrollment_g4),hjust=-.5) +
  scale_y_continuous(name='4th Grade Enrollment') +
  coord_flip() +
  expand_limits(y=1100000) +
  theme_bw() +
  ggtitle(str_wrap("Counts of the Number of 4th Grade Students by Region using 2009 Data",55))

domains<-df %>% group_by(region_code) %>% summarise(n=n())
```


# Sampling of Schools in Districts


Schools (PSUs) will be selected using simple random sampling, where in each region a 0.82% sample is taken.  Simple random sampling is done, rather than probability proportional to size, because no reliable numbers on the number of students per school are available.  The latest information comes from a 2009 census, and we are unable to accurately match all the schools in our current frame to the 2009 census.  

```{r school sampling}

sample_random <- df %>%
  group_by(region) %>%
  sample_frac(size=0.0082) %>%
  ungroup() %>%
  sample_n(size=300) %>%
  mutate(sample='Sampled School')

#Some summary stats and descriptives
ggplot(data=sample_random, aes(region)) +
  geom_histogram(stat='count') +
  stat_count(aes(y=..count..,label=..count..),geom="text",hjust=-.5) +
  coord_flip() +
  expand_limits(y=400) +
  theme_bw() +
  ggtitle(str_wrap("Counts of the Number of Schools by Region in Selected Sample of 300 Schools",55))


datatable(sample_random, caption = 'List of Public Schools Chosen for Sample') 

write_excel_csv(sample_random, paste(dir_frame, '/sample_public_schools_', Sys.Date(),  '.csv', sep=""))

```


# Replacement Schools

Below is a list of replacement schools for each sampled school. Replacement schools were randomly selected among the set of schools in the Woreda, not including the orginally sampled schools. Each row contains the school name, location, and other information for each replacement school.  In the final 5 columns of the database is the school code, school name, region, zone, and woreda of the originally sampled school for which this school serves as a replacement. 

```{r update_dataset, echo=FALSE}
#add sample schools back to original database
data_set_updated <- df %>%
  left_join(sample_random)

#get list of woredas
sampled_woredas <- sample_random %>%
  group_by(region, zone, woreda) %>% 
  summarise(sampled_woreda=n()
            )


# select one replacement per woreda
sample_replace <- data_set_updated %>%
  left_join(sampled_woredas) %>%
  filter(!is.na(sampled_woreda)) %>%
  filter(is.na(sample)) %>%
  group_by(region, zone, woreda) %>% 
  sample_n(sampled_woreda) %>%
  mutate(sample='Replacement School') %>%
  arrange(region, zone, woreda) 

sample_random <- sample_random %>%
    arrange(region, zone, woreda) 


#add in school info for school that will be replaced
sample_replace$replaced_school_code=sample_random$admincode
sample_replace$replaced_school_name=sample_random$school
sample_replace$replaced_region=sample_random$region
sample_replace$replaced_zone=sample_random$zone
sample_replace$replaced_woreda=sample_random$woreda

datatable(sample_replace, caption = 'List of Replacement Schools Chosen for Sample') 


write_excel_csv(sample_replace, paste(dir_frame, '/sample_replacement_schools_', Sys.Date(),  '.csv', sep=""))

sample_updated<-sample_random
#save sample
sample_file_name <- paste(dir_frame,"school_sample_",Sys.Date(),".Rdata", sep="")

save(sample_updated, data_set_updated, sample_replace,
    file=sample_file_name)   


```

Update 2/3/2020:  
There was a concern that some zones posed a security risk for the enumerators.  As a result this list of originally sampled schools was dropped.


|    region     |    zone                         |    woreda                |    admincode      |    School                 |
|---------------|---------------------------------|--------------------------|-------------------|---------------------------|
|    Oromiya    |    Wallagaa   Lixaa             |    Laaloo   Assaabii     |    S0417150342    |    Seenaa   Jaarsoo       |
|    Oromiya    |    Wallagaa   Bahaa             |    Ibaantuu              |    S0416080032    |    Agaa   Guddinaa        |
|    Oromiya    |    Wallagaa   Lixaa             |    Lataa   Sibuu         |    S0417160032    |    Hawaasii   Gittan      |
|    Oromiya    |    Horroo   Guduru Wallaggaa    |    Horroo   Bulluq       |    S0408070412    |    Saqalaa                |
|    Oromiya    |    Qellam   Wallaggaa           |    Gawoo   Qebee         |    S0411050282    |    Jogee   Cabal          |
|    Oromiya    |    Qellam   Wallaggaa           |    Anfilloo              |    S0411010342    |    Dallaa   Shoor         |
|    Oromiya    |    Wallagaa   Lixaa             |    Boojjii   Coqorsaa    |    S0417070202    |    Manajaartee   Biqir    |
|    Oromiya    |    Wallagaa   Lixaa             |    Mana   Sibuu          |    S0417170712    |    BAREEDAA   FIRAA       |
|    Oromiya    |    Wallagaa   Lixaa             |    Najjoo                |    S0417180142    |    Yambal   Guduruu       |

In order to replace these schools, we sample another 9 schools from within the Oromiya region, but from different zones.

```{r security_schools, echo=FALSE}

zone_list<-c('Wallagaa Lixaa', 'Wallagaa Bahaa', 'Horroo Guduru Wallaggaa', 'Qellam Wallaggaa')

security_schools <- data_set_updated %>%
  filter(is.na(sample)) %>%
  filter(region=='Oromiya') %>%
  filter(!(zone %in% zone_list)) %>%
  sample_n(9) %>%
  mutate(sampled_security=1)

datatable(security_schools, caption = 'List of New Schools Chosen for Sample Because of Security Reasons') 

#add sample schools back to original database
data_set_updated <- data_set_updated %>%
  left_join(security_schools)

#get list of woredas
sampled_woredas_security <- security_schools %>%
  group_by(region, zone, woreda) %>% 
  summarise(sampled_woreda_security=n()
            )


# select one replacement per woreda
sample_replace_security <- data_set_updated %>%
  left_join(sampled_woredas_security) %>%
  filter(!is.na(sampled_woreda_security)) %>%
  filter(is.na(sample)) %>%
  filter(is.na(sampled_security)) %>%
  group_by(region, zone, woreda) %>% 
  sample_n(sampled_woreda_security) %>%
  mutate(sample='Replacement School') %>%
  arrange(region, zone, woreda) 

security_schools <- security_schools %>%
    arrange(region, zone, woreda) 


#add in school info for school that will be replaced
sample_replace_security$replaced_school_code=security_schools$admincode
sample_replace_security$replaced_school_name=security_schools$school
sample_replace_security$replaced_region=security_schools$region
sample_replace_security$replaced_zone=security_schools$zone
sample_replace_security$replaced_woreda=security_schools$woreda


datatable(sample_replace_security, caption = 'List of Replacement Schools Chosen for Sample Because of Security Reasons') 


write_excel_csv(sample_replace_security, paste(dir_frame, '/sample_replacement_schools_for_security', Sys.Date(),  '.csv', sep=""))

sample_updated<-sample_random %>%
  filter(!(zone %in% zone_list)) %>%
  bind_rows(security_schools)

write_excel_csv(sample_updated, paste(dir_frame, '/sample_public_schools_', Sys.Date(),  '.csv', sep=""))

sample_replace<-sample_replace %>%
  filter(!(zone %in% zone_list)) %>%
  bind_rows(sample_replace_security)

write_excel_csv(sample_replace, paste(dir_frame, '/sample_replacement_schools_', Sys.Date(),  '.csv', sep=""))

#save sample
sample_file_name <- paste(dir_frame,"school_sample_",Sys.Date(),".Rdata", sep="")

save(sample_updated, data_set_updated, sample_replace, sample_replace_security,
    file=sample_file_name)   

```
