---
title: "Ethiopia Global Education Policy Dashboard Survey - Public Officials"
author: "Brian Stacy"
date: "1/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#load relevant libraries
#library(rgdal)
library(tidyverse)
library(readxl)
library(leaflet)
library(kableExtra)
library(DT)
library(skimr)
library(haven)
library(crosstalk)
library(purrr)
set.seed(54351324)

#################################
#Specify Directories, etc
#################################

#Specify directory where sampling frame located
#Specify directory where sampling frame located
dir_frame<-"C:/Users/wb469649/WBG/Ezequiel Molina - Dashboard (Team Folder)/Country_Work/Ethiopia/2019/Data/Sampling/"
dir_frame<-"C:/Users/wb577189/OneDrive - WBG/My files/Dashboard (Team Folder)/Country_Work/Ethiopia/2020/Data/Sampling/"

date_frame<-c("2020-02-14")

```

## Introduction

This file outlines the sampling strategy for Ethiopia for the Survey of Public Officials.  For sampling notes on the School Survey, please see the markdown report produced using:

https://github.com/worldbank/GEPD/blob/master/Data/Ethiopia/2019/Data/Sampling/Sampling_Notes_Ethiopia.Rmd

## General Notes on Sampling
The aim of the Global Education Policy Dashboard school survey is to produce nationally representative estimates, which will be able to detect changes in the indicators over time at a minimum power of 80% and with a 0.05 significance level.  We also wish to detect differences by urban/rural location. 


For our Survey of Public Officials, we will sample a total of 200 public officials.  Roughly 40 officials will be surveyed at the central level, while 60 officials will be surveyed at the regional level and 100 at the district (Woreda) level.  For selection of officials at the regional and district level, we will employ a cluster sampling strategy, where 6 Regional offices are chosen at random from among the regions in which schools were sampled.  Then among these 6 Regions, we also select at random 20 Woreda offices from among the Woredas in which schools werer sampled.  The result of this sampling approach is that for 6 clusters we will have links from the school to the Woreda office to the Regional office to the central office.  Within the Regional office 10 public officials will be interviewed.  Within the Woreda offices 5 officials will be interviewed.  

In other countries we interviewed the following profiles: head of organization, head of school monitoring, head of finance, head of planning, head of HR, and, if needed, some randomly chosen officials. The number of public officials to randomize varies according to the type of office (regional or district) and if the above positions are combined.

For the randomly chosen officials, the randomization has to be done with Survey Solutions following these steps:

  1.	Get (or write down on paper) the full list of public officials 
  2.	Count and assign a number to each public official in the list (exclude those that were directly selected, for example the head of HR)
  3.	Count the public officials in the list and put the total number of public officials into Survey Solutions 
  4.	Interview the public officials according to the order given by Survey Solutions (if a public official who was randomly chosen is not available, go with the next one in the list)
  5.	Take a picture of the full list and upload it to Survey Solutions for quality control

```{r load, echo=FALSE, warning=FALSE}
#load the school level data

sample_file_name <- paste(dir_frame,"school_sample_",date_frame,".Rdata", sep="")

load(file=sample_file_name)   

#Some summary stats and descriptives
ggplot(data=sample_updated, aes(Region)) +
  geom_histogram(stat='count') +
  stat_count(aes(y=..count..,label=..count..),geom="text",hjust=-.5) +
  coord_flip() +
  expand_limits(y=400) +
  theme_bw() +
  ggtitle(str_wrap("Counts of the Number of Schools by Region in Selected Sample of 300 Schools",55))

```

We will make sure all regions have the possibility of being selected, but we will give greater weight to regions with more schools (for example Amhara).  In the next code snippet, we will create the weights.

```{r regional_weights, echo=TRUE}

 #form regional weights, based on the number of schools.
  region_weights<- data_set_updated %>% #read in school sample frame as basis for forming weights
    group_by(Region) %>%
    summarise(n_stud=sum(grd4_total) )  #count number of students per region

  #select six regions
  regions_list <- region_weights %>%
    sample_n(6, weight=n_stud)

  region_frame_name <- paste(dir_frame,"/region_sample_",Sys.Date(),".csv", sep="")
  datatable(regions_list,
            caption="Regions selected for Public Officials Survey")

  write_excel_csv(regions_list,region_frame_name) 

```
The regions selected are: `r paste(regions_list$region, sep=",")`

Now we will select the Woredas.

```{r woredas}

  #From within regions, assign how many woredas to visit
  regions_list <- regions_list %>%
  ungroup() %>%
  mutate(N_woredas_to_sample=(20*n_stud/sum(n_stud))) #get number of woredas based on number of students in 4th grade


  
  regions_list <- regions_list %>% 
    mutate(N_woredas_to_sample=case_when(
      Region=="Oromia" ~8,
      Region=="Amhara" ~6,
      Region=="SNNP" ~4,
      TRUE ~ 1
    )) #do some reallocation to ensure at least one school from each region

    
  woreda_list<- sample_updated %>%
    group_by(Region, Woreda) %>%
    mutate(n_schools_woreda=n()) %>%
    summarise_all(first) %>%
    group_by(Region) %>%
    left_join(regions_list) %>%
    filter(!is.na(n_stud)) %>% #drop woredas in regions not selected
    sample_n(N_woredas_to_sample) %>%
    dplyr::select(Region, Zone, Woreda)
  
  #Change Addis Ababa "woreda" values, because the chosen isn't a woreda it is a sub-city admin unit
  woreda_list <- woreda_list %>%
    mutate(
      Zone=if_else(Region=="Addis Ababa","NA",Zone),
      Woreda=if_else(Region=="Addis Ababa","NA",Woreda)
    )
  
  #save as csv
  dist_frame_name <- paste(dir_frame,"/woreda_sample_",Sys.Date(),".csv", sep="")
  datatable(woreda_list,
            options = list(pageLength = 21),
            caption="Woredas selected for Public Officials Survey")

  write_excel_csv(woreda_list,dist_frame_name) 
  write_excel_csv(woreda_list,dist_frame_name) 

```

 
